\documentclass[twoside,letterpaper,12pt]{memoir}
\usepackage[no-math]{fontspec}
\usepackage{xunicode}
\usepackage{hyperref}
\usepackage{microtype}

\semiisopage

\setcounter{tocdepth}{3}

\setmainfont[Ligatures=TeX]{Garamond Premier Pro}

\title{Caretaker}
\author{Matthew Lineberger}

\date

\begin{document}

\setmainfont[Ligatures=TeX, Numbers=Lowercase]{Garamond Premier Pro}

\begin{titlingpage}
	\calccentering{\unitlength}
	\begin{adjustwidth*}{\unitlength}{-\unitlength}
	\maketitle 
	\end{adjustwidth*}
\end{titlingpage}

\pagestyle{simple}

\chapter*{Prologue}
\noindent Red Alert.Red lights were flashing up and down the passageway. Panels had fallen off the walls. She smelled ozone and the telltale stink of burning plastic; up the hall a small fire was glowing inside a broken \textsc{eps} conduit, slowly strangling behind a fire-suppression force field. The siren still wailed; nobody on the bridge had turned it off yet. It set her teeth on edge, disrupting her already loose thoughts.Janeway caught her reflection in a dead control panel, cracked horizontally along its entire length. Her right arm appeared to be hanging backwards. She needed to get to sickbay.Red Alert. They still hadn't turned the alarm off.There was a turbolift thirty meters down the corridor. She remembered that was where she was going when...when what? \textsc{uss} \textit{Voyager} had suffered some kind of serious problem, an accident or an attack, and she had been injured. That much she could infer on her own. She had no more information than that. The intercom was silent. That by itself was ominous, because in the few previous Red Alerts she'd experienced in her heretofore uneventful career, the bridge had issued an uninterrupted stream of instructions and status updates over the intercom.The bridge. The memory crystallized in her head. That's where she had been going. She had been called to the bridge. \textit{Voyager} was in the Badlands, looking for Maquis, and they had called her to the bridge because the captain wanted advice from her science officer in that weird, dangerous patch of space. And then what? Bright light, the ship shaking…And that sound. Of course, the sound. That earsplitting whine, like amplifier feedback powered by an exploding sun. How could she have forgotten it? And then the ship threw her to the deck, and then nothing.She remembered her commbadge. I must have hit my head hard, she thought, if she'd forgotten that. It chirped when she tapped it; at least that was still working. ``Science officer to bridge,'' she said.No reply. She tried again and got the same response. Sour adrenaline began pooling in her stomach. The silent intercoms, the howling klaxon grating away at her nerves, and now this. She hailed the bridge a third time and still got no result.Finally: ``Computer,'' she said. ``Status of the bridge."``\textsc{structural integrity failure on deck one}'' it said, its voice expressionless and mechanical. ``\textsc{explosive decompression in all compartments}.''She slumped against the wall, just barely able to keep standing. ``Survivors?" she said.``\textsc{none}.''She took a deep breath before asking the next question. ``Status of Captain Bujold."``\textsc{captain bujold is dead}.''``Status of First Officer Cavit."``\textsc{commander cavit is dead}."``Status of Chief Engineer Patel." He shouldn't have been on the bridge.``\textsc{lieutenant commander patel is dead}."``What? How?"``\textsc{lieutenant commander patel was killed by a fall from the main engineering upper catwalk}."Oh God, she thought. \textit{Voyager} was decapitated. Captain, first, and second officers…third and fourth, too, the ops officer Dvorska and the tactical officer Henglaav, they would have been on the bridge. She had no idea who was in command of the ship, who she had to report to, or even where she was supposed to go, with the bridge destroyed.And then, Lieutenant Kathryn Janeway suddenly froze in horror. Because the list of surviving department heads was getting shorter, and there couldn't be many left besides\ldots``Computer," she said. "Who is the commanding officer of \textsc{uss} \textit{Voyager}?''``\textsc{the commanding officer of uss} \textsi{voyager} \textsc{is lieutenant kathryn janeway}.''``Oh God,'' said Janeway. Then she vomited.The ship shuddered hard. The warp core went offline with a sound like distant thunder, felt as much as heard. Then main power failed, and all the lights went out.

\chapter*{Part I}
\textbf{Three Days Earlier }\noindent\textbf{Federation-Cardassian frontier}\\\noindent It hadn't been Chakotay's week.
``The Cardassian vessel is closing," said Tuvok. The Maquis raider shook under another phaser volley. Something important behind the captain's chair failed with a shower of sparks; they rained on the back of his neck, each one stinging like a mote of fire.``B'Elana!" shouted Chakotay.``I know, God damn it!" Behind them, the engineer yanked a panel off the wall and tore into the mess of jerry-rigged machinery that kept \textit{Val Jean} alive, cursing in Klingon and English.\textit{Val Jean} banked hard, faster than the inertial dampers could compensate. A'shadieeyah Mohammad, Chakotay's crackerjack pilot, was doing her best, trying to dodge the cruiser's weapons fire. Mohammad had gotten them out of more than her share of impossible jams, but this time the spoon-heads were hanging tight.``Weapons?" said Chakotay. It was more of a prayer than an order.``Weapons would be nice," said Seska, Chakotay's Bajoran second-in-command.``I'm really not in the mood for jokes," said Chakotay.``Weapons inoperative," said Tuvok.``B'Elana, is there anything---"``How about I stick a broom up my ass and sweep the floor while I'm at it?" said Torres.``B'Eleana, I need phasers!"``How much do you need a warp core breach?"``The Cardassians are going to give me one anyway if you don't get those phasers online."``They won't need to bother in a minute!"``They don't need to wait that long!"Seska leapt out of her seat and dove into an open access hatch and started working on the weapons herself. Mohammad turned the ship again, but not in time to avoid a phaser hit amidships. Every alarm on the bridge wailed to life at once.``Shields collapsed," said Tuvok.``One more hit and we're done!" said B'Elana. ``Chakotay, the phasers don't matter! We can't fight our way out of this.''``Can you give me warp speed?"``Are you crazy?" said B'Elana.``Can you!?"``I can give you one second. \textit{Maybe}."``Do it. A'sha, how far are we from the Badlands?"``Ten light years from the outer boundary,'' said Mohammad.``The Cardassians will be anticipating such a move," said Tuvok.``I can't get us ten light years on a one-second burst," said B'Elana.``There's another ship out there between us and the Badlands," said Kurt Bendera, \textit{Val Jean}'s sensor operator and a Starfleet defector like Chakotay and Tuvok. ``They're trying to lay low, but I caught their warp signature a couple of times. If we go to warp, they'll intercept."Chakotay made a snap decision. ``A'sha, come about, prepare for warp on my mark."``What?!" said Mohammad and B'Elana together.``Kurt's right, there's another cruiser out there. We need to draw him out of position before we make a run for the Badlands.''``If we even can make a run for it,'' said B'Elana.``That's your responsibility.''``The Cardassians are powering up their tractor beam,'' said Tuvok.``A'sha, now!''\textit{Val Jean} banked around as hard as it would go, then leaped into warp like a spurred thoroughbred. The tractor beam missed them by meters.Seska returned to her seat, smeared with grease and grime, sheened with sweat, and bleeding from a cut on her forehead. With a motion so subtle nobody else on the bridge could have possibly seen it, she placed a hand on his.``This had better work," she said.``It will. Any luck with the phasers?''``I got them back, for now.''``Good work,'' said Chakotay. ``Hopefully we won't need them.''B'Elana had done better than she'd promised. They stayed at warp for five seconds, and momentarily hit warp six before the warp drive gave out.``Brilliant, B'Elana," said Chakotay.``We don't have much time," said Seska. ``We need to get the warp drive back in working order before the Cardassians figure out where we went."No sooner had she said that than an alarm went off at Bendera's station. ``Cardassian \textit{Galor}-class cruiser warping in sixty astronomical units from our position." Pause. ``Correction, two of them just warped in.''``How long until they spot us?"``Three minutes to perform a full sky scan," said Bendera. ``If we're very very lucky."``B'Elana get your ass in gear."``You don't need to tell me twice." She started banging and cursing on machinery.Two minutes later, the Galors went to warp. They were on top of them before Chakotay could even shout the alarm.``We have warp!" said B'Elana.``Helm, engage!" \textit{Val Jean} warped away again just seconds before the Galor fired. The plasma clouds of the Badlands swelled to fill the entire viewscreen.They had to drop out of warp again at the edge of the Badlands, not even Mohammad daring to run through the dangerous patch of disturbed space faster than light until she got her bearings. The Maquis had mapped the whole area (at no small cost in blood) and a skilled navigator like Mohammad could warp through safely, but not quickly.And the Cardassians were starting to map the place, too.``Let's move," said Chakotay. ``I don't want to hang around here all day."``I'm working as fast as I can, boss," said Mohammad.And then the hunters were on top of them again.``Go!" shouted Chakotay, watching the two cruisers approach on the viewscreen like orcas bearing down on a wounded seal. \textit{Val Jean} leapt to warp again, with the Cardassians baying at their heels. One followed at a distance while the other closed in---so when Mohommad dropped \textit{Val Jean} out of warp to turn, one would overshoot, but the other wouldn't.``They're going to wait until we're in open space and then they're going to attack," said Chakotay.``Trying to shake them,'' said Mohommad.The ship dropped out of warp, turned with thrusters, then bounced into warp again. Mohammad had free reign with the ship, taking them through the twisting warren of safe passages through the Badlands without asking Chakotay or anyone else for instructions.``They are still pursuing," said Tuvok.``I'm taking us into the Rat's Nest," said Mohommad. ``If the spoon-heads have that charted, I'll eat my scarf."They turned again, and then Mohommad opened up the warp drive to full power. Something went \textit{bang} and caught fire; B'Elana cursed and screamed and hammered on machinery with a wrench (B'Elana referred to such outbursts as an ancient Klingon mechanics' ritual).Ahead of them was a vortex of raging plasma storms. The Rat's Nest was a network of passages interlaced through one of the most violent regions of the Badlands; the storms had been particularly bad that whole year. From a distance of a few light years, the tendrils of hot gas seemed motionless; Chakotay knew that was only because they were so enormous and so far away. The tips were flailing at half the speed of light and could burn away entire planets. Mohommad and the Cardassians could avoid those, but the smaller bursts that popped up at random outside the safe areas could incinerate a passing starship. Sometimes they popped up inside the safe areas, too. Especially in the Rat's Nest.\textit{Val Jean} began rattling. ``What the hell is that?" said Chakotay.``Subspace is very disturbed around here, boss," said Mohommad. The rattle became violent shaking.``We're going to have to drop out of warp if this keeps up," said Torres. ``The engines don't like this at all."``I see a spot," said Mohommad. ``Dropping out of warp."They fell below superluminal speed in a bubble of calm a few million kilometers across, surrounded by vast clouds of hot gas.``The Cardassians overshot us," said Bendera. ``They're in the middle of a cloud."``On screen!"The two Galors were being buffeted by plasma and repeatedly slashed by energy discharges. One took a shot right across the bow that penetrated the shields and tore away part of the hull.``Let's move," said Chakotay. \textit{Val Jean} warped away, leaving the Cardassians behind. A few minutes later, when Mohommad had to turn again, Bendera checked their long range scan.``Are they following us?" said Chakotay.``Negative. They're leaving the Badlands."``They had enough for one day," said Seska. She shook her head. The Bajoran earring she wore jingled. ``There's no way we should have survived that.''``But we did,'' said Chakotay. He leaned back in his chair and smiled for the first time all day. The adrenaline of combat was draining away, leaving him in a euphoric haze that was nearly post-orgasmic.Speaking of...``A'sha, take us through the Rat's Nest and out the other side of the Badlands. Make sure there aren't any spoon-heads on the other side waiting for us."``That's Federation territory, sir."``Same difference. Just keep us out of trouble."``Will do, boss."Chakotay went back to his cabin. Seska followed discretely about five minutes later.Afterwards, they were both dozing when a single bright flash woke them both up.``What the hell was that?" said Chakotay.Some tremendous force like a collision shook the whole ship, tossing them both out of Chakotay's bunk onto the cabin deck. ``Kurt, what the hell is happening?'' he shouted into the intercom. A piercing ringing noise, like amplifier feedback, was building in the background.``\textit{Something's happening with the storms. There's some kind of phased---}'' The intercom cut out.``Kurt! Kurt!''``To the bridge!'' shouted Seska, pulling on her shirt.Chakotay lunged for the door. \textit{Val Jean} shook, and suddenly there was pain and blinding white light. The ringing noise was deafening, louder than the end of the world. ``Seska!'' he shouted.\textit{Val Jean} fell down a hole in the world.\begin{center}\rule{3cm}{0.4 pt}\end{center}
\noindent\textbf{New Senegal Penal Colony}\\Tom Paris was digging a hole when two guards came to him and told him he had a visitor. In his early days on New Senegal, he would have had a remark for them; ``I told your mother I'm not interested in any more conjugal visits" perhaps. There was a series of mile-long, zigzagging ditches through the desert north of camp, each one dug by him and a few other insubordinate prisoners, reminders of the price of a smart mouth here. Mostly these days, he didn't say anything to the guards besides ``yes sir" and ``no sir".They escorted Paris across a kilometer of scrub desert to a plain white concrete bunker on the outskirts of a cluster of other concrete buildings, the administration center for the camp. Inside, the bunker was dim, so he couldn't see right away who was waiting for him inside. Slowly, as his eyes adjusted, a short, trim, dark-haired woman in a Starfleet uniform materialized out of the gloom. Her tunic was red, in the newest cut, with four rank pips: a starship captain. Behind her were two other Starfleet types, wearing gold and looking like miserable pricks. Cops, he guessed. Or maybe spooks. Starfleet Intelligence.``Good morning, Mr. Paris," she said. Her accent was French. ``My name is Captain Nicole Bujold, of the Federation starship \textit{Voyager}."``Hi," he said.``Please," she said, ``sit down." She waved her hand at a hard metal chair on one side of a steel desk. He did so. She sat across from him. The two spooks remained standing.``What's this all about, Captain?" said Paris.``We have a little situation on our hands, Mr. Paris. We were hoping you could help us.''``Who's ‘we'?''``Starfleet,'' she said. ``Would you like a drink?''``A what?''``A drink, Mr. Paris.'' She showed him a bottle of brown liquor. ``It's not a trick, Mr. Paris. I thought you'd appreciate a little hospitality.''``Sure,'' he said. ``I'll have a drink.''``Excellent. Now I have an excuse to drink as well.'' She smiled. It didn't quite reach her eyes. After she poured both glasses, Paris knocked his back. Synthehol.``What situation do you have?'' said Paris.``Three days ago, a Maquis raider named \textit{Val Jean} disappeared in the Badlands."Paris's eyes widened. A second later, he realized that had been a mistake. Never show Starfleet you know anything about anything. He sighed internally. Mistakes had marked his entire tenure as a freedom fighter, which was one reason why he was digging holes on New Senegal.``I take it you know the name."``I've heard it," said Paris.``You picked it, from what I understand." Another one of those cool, cheerless smiles.``If they disappeared in the Badlands, they were probably destroyed,'' said Paris.``Perhaps," said Bujold. ``That is what the Cardassians are claiming. But there are enough holes in their story to make us believe they aren't telling the whole truth."``So she'll turn up somewhere else. I can't help you with that. They abandoned all the hiding places I knew about as soon as I got captured.''``We have reason to believe the ship is still in the Badlands somewhere. It's...important to us that we find \textit{Val Jean}.''``Because of Chakotay?''``Yes, because of Chakotay. Other than Cal Hudson himself, Chakotay might be the most capable and dangerous leader the Maquis have. If he's still alive, we must make certain he does not fall into Cardassian hands.''``I thought you and the Cardassians were cooperating against the Maquis.''``Against the Maquis, yes, but Chakotay is not an ordinary Maquis. He's a defected Starfleet line officer and Academy instructor, with advanced knowledge of our capabilities and tactics. If the Cardassians capture him, they will almost certainly learn what he knows, one way or another.''``What do you want from me?" said Paris.``I intend to search the Badlands for \textit{Val Jean} and her crew. I'll need a guide."``Forget it," said Paris.``You know as much about the Badlands as anyone. There's even a prominent feature named after you. Paris's Ring, I believe.''```Paris's Asshole','' said Paris. ``I said forget about it. I'm not leading you to them.''``Think of it as a rescue mission. Your friends could be in serious trouble."``They probably slipped past the Cardassians and the spoon-heads are just too embarrassed to admit it. Chakotay and friends are probably still laughing about it on some asteroid somewhere."``Our sources indicate the Maquis are concerned as well. No one seems to know where \textit{Val Jean} is.''``Don't kid yourself. Your operatives don't know a single thing the Maquis don't want you to know,'' said Paris.``Mr. Paris, I don't have much time to waste. If you're not going to help me---''``I'm not selling out the Maquis," said Paris. ``If I lead you through the Badlands, you'll be recording every kilometer of the flight. You'll learn more about it from me in a day than you could have learned on your own in a year---and so will the Cardassians, as soon as you turn over your charts to them."``It is curious you speak of `selling out'. Because if I remember correctly, you were `sold out' yourself by Chakotay."Paris ground his knuckles into the hard steel tabletop. A part of him admired Bujold for doing her homework. She knew exactly where to poke him.``Other than ruining Chakotay's day, what are you offering me for helping you?"``A reduced overall sentence, and a transfer to a minimum security facility."Paris didn't respond. It was a better offer than he'd expected.Bujold leaned in. ``We're interested in one person, Mr. Paris: Chakotay. The rest of the crew, your old friends, they'll get token sentences. I'll even arrange so that the ones you care about the most stay out of jail.''He swore he saw her wink.She continued: ``And if they are in trouble, you'll be saving their lives." She paused to fold her hands in front of her. ``Or, you can rot here until the proper authorities declare you rehabilitated. Who knows how long it will take to rehabilitate a hardened terrorist?''``What if you don't find them?"``If \textit{Val Jean} cannot be found despite your sincere best efforts, then so be it,'' said Bujold.Paris said nothing.Bujold leaned in. ``You owe them nothing, Tom. Chakotay stole \textit{Val Jean} from you and dumped you in Starfleet's lap. Why are you still protecting him?"``I want a parole," said Paris. ``To Earth. If I help you, I want to go home.''``Betazed,'' said Bujold.``So someone can keep an eye on what I'm thinking,'' said Paris.Bujold shrugged. ``Best and final offer, Tom. Betazed is a lovely world, with lovely people. And when your sentence is up, you'll be free to travel wherever you please. The more helpful you are to Starfleet today, the sooner that day will come.''Paris sat and thought it over. The two spooks shifted impatiently.``\textit{Voyager} departs for Deep Space Nine in ten minutes, Mr. Paris,'' said Bujold. ``And so does this opportunity.''``Is this offer in writing?" said Paris.She took out a \textsc{padd} and laid it on the desk in front of him. ``Take as much time as you need to read it."He scrolled past the Starfleet legalese and thumprinted the signature box on the bottom. ``I'm in."``Excellent," said Bujold. She lifted her glass. ``\textit{Salut}``\begin{center}\rule{3cm}{0.4 pt}\end{center}
\noindent\textbf{Deep Space Nine}\\Ensign Harry Kim stood by one of the Promenade's huge windows, watching \textit{Voyager}'s final approach. His heart raced when he first read the name and registry number---\textit{his} ship, his first assignment. His hand drifted up and brushed the single rank pip on his collar, and then down to his communicator badge. He was three weeks out of the Academy, but he'd spent all of those three weeks a passenger \textit{en route} to Deep Space Nine.He watched the ship until it passed out of view, docking high overhead. Then he wandered back onto the Promenade. He still had three hours before he had to board \textit{Voyager}---a ludicrously fast turnaround for a starship making the trip from final evaluations at Utopia Planitia to Deep Space Nine, but still a long time for him to stare out the window in dreamy excitement, watching starships pass through the Bajoran Wormhole. After a while, traffic through the wormhole slowed and he decided to find something else to do. He'd be seeing the wormhole up close in a few hours anyway.The Promenade was crowded with people moving in all directions, but there were a few discrete streams, and one of them was flowing into Quark's Bar. The place was crowded with Starfleet, many of them waiting, like Harry, to board \textit{Voyager}. He felt like he should be mingling in the crowd and making friends, but his shyness presented an insurmountable wall. He found a seat at the bar instead.The Ferengi bartender (Quark, presumably) had no problems with shyness and seemed to sense Harry was looking for someone to talk to. Or maybe just that Harry wanted a drink.``Good afternoon, friend," said the Ferengi. He struck a classic bartender's pose, leaning on the bar with one elbow while polishing a glass. ``What can I get for you today?"Harry glanced at the forest of bottles behind Quark. His brain promptly locked up. He had no idea what ninety-nine percent of them even were. ``I'll have...a rootbeer," he finally said.``A rootbeer? A rootbeer?!''``What? What's wrong with rootbeer?''``My good sir, where are you from?"``Uh, Earth?"``Earth! And have you ever left Earth before?"``Well, we took a family vacation to Mars once."Quark gave Harry a look of pity and astonishment. ``Do you mean to tell that this is your very first voyage beyond your home sun, and you've come here, to this magnificent entertainment establishment---'' he waved around at the bad ``---famed across a thousand worlds, with your choice of beverages from across the galaxy to delight your senses and expand your horizons, and what you want is a \textit{root beer}?"``Well, I---"``Never mind. Starfleet has obviously already beaten the adventure out of you. Rom, one root beer!"``Now wait. What else do you have?"``That you'd like? Oh, tap water, tap water with ice, tap water with bubbles---"``I'm serious. What else do you have?"``Are you sure you don't want a root beer? It's safe and bor---I mean, predictable."``I'm serious. I'm sure I don't want the root beer."``Well, okay then. Rom, hold the root beer!" The Ferengi at the other end of the bar made a hand gesture that might have meant ``OK!". If Harry had been paying closer attention, he might have noticed that Rom hadn't been doing anything that could have been construed as pouring a root beer in the first place.Quark leaned in close to Harry. Harry could count the points of his teeth. ``So what do you have in mind?"``Um...you pick. What's good?"``Well, everything I have is \textit{good}. But I thought we were having an adventure. You don't want something \textit{good}, you want something \textit{great}. And I have just the thing for you."``What's that?"``Romulan Ale."Harry's eyes widened. ``That's illegal!"``It's illegal in the Federation, my boy. This station is \textit{Bajoran} territory!"Harry pondered, remembering his third grade production of the epic drama, \textit{Romulan Ale Is Uncool}, where he had played ``Incurably Insane Romulan Ale Addict \#3".Except, of course, that Romulan Ale \textit{was} cool. If it wasn't, they wouldn't have put on a stupid play to make kids not want to drink it. ``Okay," he said. ``I'll have some."Quark smiled in a way that made Harry want to flinch a little. He retrieved a decanter of blue liquid from under the bar, and with great ceremony, poured some into a small glass, which he pushed across the bar to Harry. Harry took one sip; it was smooth and cool, and very sweet, unlike how he had imagined.``That will be one strip of latinum," said Harry.Harry fished in his pockets for his FedBank chit, which let him carry Federation credits with him in areas where money was necessary. Quark held a chit reader over the bartop. Harry gave Quark one credit, plus another half-credit as a tip. He smiled at Quark.``Where are the other hundred ninety-three and a half credits?" said Quark.``The other what?"``The other hundred ninety-three and a half credits you owe me."``But you said it was only one."``One strip of gold-press latinum. You're paying in Federation credits, and the current exchange rate is 194 to 1."``But the exchange rate is 1 to 1!"``The \textit{official} exchange rate is 1 to 1. Only an idiot actually accepts one credit for one strip of latinum. Try it; go down to the currency exchange and buy one strip for one credit. They'll laugh you right out the door."``But you have to take credits at the official exchange rate. That's the law."``I have to take credits at the official exchange rate in the \textit{Federation}. And while we all recognize that the issue of Bajoran sovereignty vis-a-vis the Federation is complicated on this station, we've already established that this bar \textit{ain't} a Federation establishment, and therefore, I don't have to take Federation funny money at the official exchange rate. You owe me one hundred ninety-seven credits.""197? I just paid you one and a half."Quark put his hands on his hips. ``The credit just fell to 198 and a half to the strip."Harry sighed and paid. He didn't try to tip the Ferengi this time. He even bought a second Romulan Ale, and a third, and a fourth, the last costing him 352 credits, Harry reasoning that once back on the ship, he wouldn't have much to spend his money on anyway (Harry listened as Quark told a long tale of woe about the pitfalls of fiat money and his own misadventures in Orion currency speculation, Harry the whole time thinking that he thought it was the customer who was supposed to tell the bartender a sad story). He had been at the bar for an hour when a civilian took the stool next to him (a stool Harry didn't remember being there, but he'd been drinking for an hour).``Romulan Ale," said the civilian, a man in his early thirties.Quark poured him a glass. ``One strip of latinum,'' he said.The man thought for a moment, then entered a number on Quark's chit reader. Quark entered a different one; they haggled for a few minutes until they had settled on a price. Then he moved down the bar, leaving Harry and the stranger alone.The man took a sip of his drink. ``Damn," he said. ``This is a lousy vintage." He squinted down after Quark.``Mine's okay," said Harry.The man eyed Harry. ``Mind if I take a sip?"``Sure," said Harry.The man took Harry's glass and had a small sip. He started laughing.``What?" said Harry.``This isn't Romulan Ale," said the stranger. ``This is Wild Berry Tasty-Ade and synthehol. And I thought I got snookered. Next time make sure he hasn't switched bottles on you."Harry stared at him. ``I paid 352 credits for that!"The stranger laughed again. ``The exchange rate isn't that bad. I paid 83 for mine. Always stop by the currency exchange first to check the rates."``Oh," said Harry. He stared into his glass, having intense flashbacks to high school.The stranger seemed to take pity on him. ``What's your name?" he said.``Ensign Harry Kim," said Harry.``You with \textit{Voyager}?" said the stranger.``Yeah."``Me too." He held out his hand. ``Tom Paris."Harry took it. ``Nice to meet you. What are you, a civilian expert?"``Something like that."``Have you worked in the Gamma Quadrant before?''``We're not going to the Gamma Quadrant,'' he said.``Huh?''A call came over the station intercom: ``\textit{All} Voyager \textit{crew, report to Pylon Three.}"``That's us," said Paris, finishing off his drink. When he saw Harry abandoning his, he finished that, too.``Should I try to get my money back?" said Harry.``From him? You're kidding, right? Come on."They walked out of the bar, joining the crowd flowing towards Pylon 3.``Hey," said Harry, ``was it my imagination, or did your stool wink at me when you got up?"Paris shrugged. ``You never know in this place.

\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textbf{USS \textit{Voyager}}\noindent\textbf{Federation-Cardassian Frontier}\\Lieutenant Kathryn Janeway was still getting settled in her office when the door chimed. ``Come," she said.The doors hissed open and Captain Bujold walked in. Janeway sprang to her feet.``As you were," said Bujold. ``I just came down to see how you were settling in."``Just fine, ma'am," said Janeway.``What do you think of the facilities here?"``They're very nice," she said. ``Not as much space as we had on \textit{Atlantis}, but all of the equipment is top of the line."``Alas, we don’t have a \textit{Nebula}’s lab space," said Bujold. ``Our mission profile is geared more towards observation than analysis.''``It seems like a missed opportunity,'' said Janeway. ``This ship would be perfect for long-term science missions.''``That’s an interesting opinion. Most people would say a ship this small isn't really suited to long-duration missions "Janeway smiled. ``We have more volume than a \textit{Constitution}, and Jim Kirk seemed to do okay for himself."Bujold heaved a theatrical sigh and gave Janeway a wry smile. ``I agree with you. But since Wolf..." She shrugged. She was right. Since Wolf 359, science had gotten the short end of the funding stick. New general-purpose ships designs like the \textit{Intrepid }class had less and less space devoted to science facilities, older ships were seeing their science labs left off of refit lists , and most of the new designs in the pipeline were strict combat ships with no science facilities at all. Even the giant \textit{Galaxy} and \textit{Nebula} class explorers were seeing their science capacity shrink. Janeway understood the rationale, but she didn't have to like it.``Have you gone over your inventory yet?" said Bujold.``Eh? Yes, I have. I was going to mention--"``You are short several items."``It's a lot more than several, ma'am. I'm not sure I understand the rush. The Gamma Quadrant isn't going anywhere."``Our mission to the Gamma Quadrant has been postponed. I'm sorry I didn't inform you before now, but the situation is unfolding rapidly. A Maquis ship has disappeared in the Badlands; Chakotay is on board, and we have been tasked with finding him. Time is of the essence for us."``I understand," said Janeway. She pretended to be distracted by a blinking figure on her \textsc{padd}, to hide her irritation.``I have an assignment for you," said Bujold. ``We will be in the Badlands in a few hours. I would like you to send someone to work with Mr. Paris and Lieutenant Stadi to plot a course and plan our search."Janeway went through her mental list of officers and crewmen in her department. The trouble was, she'd been on board \textit{Voyager} less than a day, and couldn't even remember all her people's names, let alone their qualifications. She'd had all her assignments drawn up for a star mapping mission to the Gamma Quadrant, and now she had to completely redraw them on no notice. Bujold waited, tapping her foot. Janeway, pressed, decided on the one person she knew she could trust.``I can do it," said Janeway.Bujold gave her a curious look. ``You, Lieutenant?"``Yes ma'am."``What is your specialty again?"There was a long pause. ``Meteorology, ma'am."``Meteorology."``Yes. Specifically, meteorology of class J and T planets."``Gas giants," said Bujold.``Yes," said Janeway. Her ears were starting to turn hot. ``The fluid dynamics of the Badlands plasma systems are very similar...'' She trailed off.Bujold stared at the overhead for a moment, as if she had just spotted an interesting bug or somesuch thing. She said ``Hmm" several times. Finally, she said to Janeway, ``Well, if you feel it is best, by all means, please join Lieutenant Stadi and Mr. Paris on the bridge."``Yes ma'am." After Bujold left, she pulled up her department's personnel records and flipped through them, looking for someone else to send to the bridge.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textbf{USS \textit{Voyager}}\noindent\textbf{The Badlands}\\Lieutenant Stadi didn't like the way Tom Paris was leaning over her shoulder, watching the helm station's readouts. For one thing, he was making noises: small ``hmms" and ``uh-huhs" like an Academy instructor, making it clear he was critiquing her performance, as if a failed terrorist had any business judging a Starfleet officer. For another, he was looking at her breasts. She was sure of this because she was Betazed. She tried not to read minds unless she had a good reason, but \textit{Damn. Nice cans. I'd hit that}, was hard to ignore, especially when he thought it two or three times in the first hour.``Set course 285 mark 13, warp 3, four minutes," said Paris.``That's a little slow," said Commander Cavit, Voyager's first officer.``If you want to blow your nacelles off in a subspace pothole field, be my guest," said Paris.``This is ridiculous," said Cavit. ``The Cardassians told us where \textit{Val Jean} disappeared. Why don't we just go straight there and start looking?"``Because the Cardassians couldn't find their own asses in the Badlands," said Paris. ``All we know is that Val Jean went into the Rat's Nest. We're looking where she would have gone if she came out."``That's an unorthodox search pattern, Mr. Paris," said Bujold.``Look," said Paris, ``One of two things happened. They went into the Rat's Nest and they never came out, meaning the ship was wrecked, meaning it's not going anywhere; or they did leave, and they're hiding somewhere else in the Badlands. If that's the case, you want to catch them now, because the Maquis watch both sides of the border and someone saw us go in. If Chakotay is still in here, and he's alive, it's a race to find him before he finds out we're looking."Bujold and Cavitt seemed to accept that explanation, though Stadi glanced back over her shoulder once and saw Cavitt sitting in his chair cracking his knuckles, a sure sign he was unhappy, even to someone who wasn’t telepathic. Stadi felt the same.That unhappiness deepened as the search dragged on for another hour, and then another, and then another after that. Paris tried several times to make small talk with her. She brushed off each attempt with clipped, one-word answers. She tried to ignore her disgust when he started having sexual fantasies about her. When that failed, she started deliberately making small mistakes for him to correct, under the assumption that if he was micromanaging her, he wouldn't have time to wonder if she took ``it"\textit{there}.Bujold stood. ``Are we in a safe location, Mr. Paris?''``Relatively speaking, yes,'' he said.``Let’s pause here for a few minutes. I believe we could use a break.''Stadi stood up, noticing for the first time how her eyes were burning and her back was complaining. She’d been in that chair for a long time.``May I speak to you in my ready room, Lieutenant?" said Bujold.``Of course, sir.''Bujold asked the question as soon as they were in her office: ``Is he leading us on a wild-goose chase, lieutenant?"``I don't...if he is, he is hiding it well. Better than he's hiding his other thoughts."``Does he know you're a Betazed?"``I think so," said Stadi.``Hmm," said Bujold. ``Lieutenant, if I order you to do so, can you pilot us into the ‘Rat’s Nest’ without his help?"She nodded. She was getting used to the Badlands, now, and more than that, getting used to \textit{Voyager}. ``This ship can do it,'' said Stadi, patting the wall.``If Mr. Paris gives you any indication he's not making a good-faith effort, signal me."``How?"``Tap your commbadge twice."``Understood, ma'am."\begin{center}\rule{3cm}{0.4 pt}\end{center}``Nothing," said Dvorska, the ops officer. ``No debris, no warp trail."Paris nodded. It had been an hour since they'd last stopped. He looked over Stadi's shoulder at the helm console, wondering for the hundredth time what she looked like under the form-fitting Starfleet tunic. It had occurred to him, vaguely, that she was a Betazed and could probably hear his thoughts, but other than occasional encounters with the dog-faced guards of New Senegal women's camp, this was as close as he'd been to a woman in years.``Set course 636 mark 49," he said. ``Warp 2."He heard whispering behind him. He turned to see Cavitt and Bujold conferring. Cavitt looked angry; Bujold looked tired. They'd been searching the Badlands for most of the day.Bujold noticed him watching them. ``Mr. Paris," she said, ``how much longer do you expect this to take?"``I don't know, ma'am," he said, truthfully. ``The Badlands are as riled as I've ever seen them. We have to go slow."``Like hell we do," said Cavitt. ``We could use our own sensors to navigate and be at \textit{Val Jean}'s last reported location in half an hour." He pointed at Paris. ``I think he’s stalling so his friends have time to escape."``That's bullshit!" said Paris. ``You think I actually care if Chakotay goes to jail? Hell, I'd be happy to help put him there."``We're all tired, Mr. Paris," said Bujold.``I don't have to stand here and take that," said Paris.``Mr. Paris, can you truthfully tell me you aren't trying to buy time for your friends?"He hesitated. Just a hitch, not enough that most people would even notice. But it was enough for a single word to flutter up from his subconscious: \textit{No}. ``Yes," he said.He heard a communicator tweet twice. He looked back. Stadi was glaring right at him.``Mr. Paris, perhaps we should discuss this further in my ready room," said Bujold.``Fine," said Paris. He followed the captain to her lavish office just off the bridge. She didn't waste any time.``Mr. Paris, I believe my first officer is correct. I think you have been leading us on a wild goose chase in order to protect the Maquis."``Why would I do that?" said Paris. ``You know I hate Chakotay's guts."``Yes, I do," said Bujold. ``But perhaps not his pilot's, no?"Paris's ears and neck started to burn. ``Fuck her. She screwed me, too."``Mr. Paris, I offered you a deal in good faith, and in return you lied to me."``I'm not lying!" he said. \textit{Am I? What the hell am I doing?}``I will give you one last chance, Mr. Paris. Tell me the fastest way to the Rat's Nest right now, or I will have you escorted to the brig."Paris told her.``Thank you, Mr. Paris," she said. She tapped her communicator. ``You may come in now," she said.The ready room doors slid open and two big security goons walked in. ``Take him to the brig," said Bujold.``What!" said Paris. ``You said you wouldn't send me to the brig if I told you!"``I lied," said Bujold. ``Now we're even." The goons seized him by both arms and half-led, half-drag him across the bridge, to the turbolift.``Ensign Donaldson, take Mr. Paris's position," said Bujold as she strode onto the bridge. ``Lieutenant Stadi, set course 383 mark 54. Mr. Cavitt, take the ship to Yellow Alert." She planted herself in the captain's chair. Without turning to look at him, she said, ``Enjoy your next thirty years, Mr. Paris."\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textbf{USS \textit{Voyager}}\noindent\textbf{The Badlands}\\They had given Harry Kim had the overnight shift at ops. Because of this, he was off-duty when \textit{Voyager} entered the Badlands, and did not have to report to his general quarters station when they sounded yellow alert. The price for this was that he was supposed to be asleep, but between the excitement of a first mission and his own body clock insisting it was only early in the evening, he couldn't sleep. At 1900 hours, only an hour before he was supposed to wake up anyway, he gave up. He slipped out of the quarters he shared with three other junior officers and, his clarinet in hand, went to the deserted forward observation lounge, to play Benny Goodman and watch the red and yellow plasma clouds outside shift to blue and violet as they repeatedly jumped to warp.About thirty minutes after he arrived, he noticed that the warp hops no longer seemed random. Instead, they were closing in on some huge, gnarled blister of violent storms. It was beautiful, and thrilling, and more than a little scary, because it just kept getting bigger and bigger and \textit{bigger}, each hop bringing out finer details. He had no sense of scale, but the blister had to be at least a light-year across.Then came another hop and it was gone, replaced by a hellscape of storms and flares that looked close enough to touch. He gasped and realized they were inside it. Then they hopped again, and again, and again, in quick warp bursts, like they were trying to find a path through it. He forced himself to keep playing his clarinet, knowing that the people on the bridge knew what they were doing.His faith was rewarded when \textit{Voyager} hopped into a clear bubble of space and stayed there. He checked the time; 1948, enough to try a new arrangement of Glenn Miller he had found.There was a single, bright flash of light.Outside, the color of the sky changed from orange-red to yellow.Captain Bujold's voice came over the intercom: \textit{``Lieutenant Janeway, report to the bridge." }The yellow brightened to white. Harry’s clarinet playing trailed off. There was a ringing sound building in Harry's ears.The warp engines started building up power again as \textit{Voyager }banked hard to port.The Red Alert siren managed a single whoop.The white light outside became blinding, like the surface of the Sun. Harry looked away, shielded his face, felt his arms burn. The light felt like it was everywhere, inside and outside. The ringing had built to an earsplitting volume. There was a terrible roar, and \textit{Voyager} was smashed by some great force. Harry was hurled out of his seat into the side of the bar, where falling bottles from the shelf behind rained down on him.And then one of the big windows shattered, thirty centimeters of transparent aluminum giving way with a scream like a damned soul, and Harry was being sucked out to space, saved at the last second by a force field snapping to life. The ship shook more, and he dove for cover under a table.It stopped like a guillotine blade hitting a chopping block. There was a final thud, and then silence. Gradually he became aware of the red alert siren, the howls of alarm and pain outside, noises from the ship, and a low moan he was making himself as he cradled his burned forearms. When he was finally sure the shaking was done, he crawled out from under the table.He stood up and looked out the window.The Badlands were gone. Outside the windows hung a planet, an orb of banded yellow clouds. Beyond it were stars. Between it and \textit{Voyager} was an object, a central sphere larger than \textit{Voyager} surrounded by mile-long panels, like giant knives welded together blades-out.``Oh, shit," said Harry.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Val Jean}}\noindent\textbf{Ocampa system Kuiper belt}\\``You were right," said Seska. ``It’s pulling another ship through.''Chakotay snapped around to face the viewscreen. A brilliant white bloom of light was boiling in orbit of Ocampa, resolving into the shape of a starship.``I am getting a reading," said Bendera. ``It's a Federation starship."That got everyone's attention.``A rescue mission?" said Mohommad.``Capture is more like it," said Chakotay.``They are badly damaged," said Tuvok. ``They did not weather the trip well."``The Kazons have spotted them," said Seska.``How badly damaged are they?" said Chakotay. ``Can they fight?"``Their warp drive is unstable and going into shutdown," said Bendera. ``No discernible shield readings. Their main phaser batteries appear to have suffered emitter damage."``So they're helpless."``Not necessarily," said Tuvok. ``They may still have photon torpedoes."``Interesting," said Chakotay.``Should we hail them?" said Bendera.``Not yet," said Chakotay. ``Let's just watch for now."\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textbf{USS \textit{Voyager}}\noindent\textbf{Location unknown}\\Harry Kim staggered into sickbay and immediately tripped over a body lying by the door. ``Ah shit," he said. The dead man had a blue uniform, two and a half pips, and had been in sickbay: Kim was pretty sure he'd just tripped over \textit{Voyager}'s former chief medical officer. His head was cocked at an unnatural angle, neck snapped. He looked around and saw a younger officer, most likely the nurse, laying prone beside a blown-out plasma conduit, with half her face burned off.``Ah shit," he said again. ``Computer! Activate emergency medical hologram!" \textit{I hope this works}, he thought.A bald, middle-aged simulacrum in a blue Starfleet uniform shimmered to life in the middle of sickbay. ``Please state the nature of the medical emergency," it said, as if it couldn't see two bloody bodies lying on the floor.``There's been some kind of accident; there are casualties all over the ship," said Kim. ``Including them."The \textsc{emh} wasted no time, grabbing a medical tricorder from a cabinet and scanning both bodies. ``They're dead," it said. ``Are you injured?"Kim showed him his blistered hands. ``Second-degree burns," the \textsc{emh} said immediately. It picked up a dermal regenerator. ``Hold still." It gave Kim a few waves of the device, enough to shrink the blisters. As he worked, the doors hissed open and more people staggered in, a security rating with bad burns and, leaning on him, a petty officer with a grotesque compound fracture.``Move," said the \textsc{emh} to Harry.``But I'm not done!" said Kim.``This is a triage situation," said the \textsc{emh}. Its voice never changed from a clipped, professional monotone. \textit{Some bedside manner}, thought Kim.``\textit{Attention all crew, attention all crew}," said the intercom. ``\textit{This is Acting Captain Janeway. Anyone who is not hurt must report to his or her red alert station immediately. All section chiefs, please report your status to the auxiliary bridge immediately.}"\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textbf{\textit{Voyager} Main Engineering}\\The clamor of the alarms in Engineering was deafening. Lieutenant Joseph Carey stared at the master control board and tried to decide which crisis to tackle first. ``Vorick, we're still losing pressure in the primary impulse cooling circuit; get the emergency injectors restarted before the starboard reactors melt! Beltran, find out where it's leaking. Damage control, we're venting atmosphere on deck nine through the \textsc{hvac} system; seal those intakes on the double. Rodriguez! What's the story with main power?"``Sir, the starboard plasma injector fused shut and the blowdown valves stuck closed; we came a cunt-hair from blowing the whole fucking core. The warp plasma vented into the \textsc{eps} system; that saved the core, but we've got plasma blowouts all over the ship and the electrical system is fried. I can get you auxiliary power off the impulse reactors, and that's if you're lucky."``How are the antimatter pods holding?"``They're solid, sir. About the only thing on this fucking boat that isn't broke right now."``\textit{Attention all crew, attention all crew}," said the intercom. ``\textit{This is acting captain Janeway. Anyone who is not hurt must report to his or her red alert station immediately. All section chiefs, please report your status to the auxiliary bridge immediately}."Carey glanced up from the control board. ``Are you kidding me?" he said. \textit{How is the fucking science officer the acting captain?} He had known Janeway for about six hours and she hadn't impressed him; career blueshirt tag-alongs never did.``Computer," said Carey, ``Who is the legal commanding officer of \textsc{uss} \textit{Voyager}?"``\textsc{the commanding officer of uss} \textsi{voyager} \textsc{is lieutenant kathryn janeway}."\textit{Shit}, though Carey.``\textit{Bridge to engineering}," said the intercom.``Here we go," muttered Carey. ``Engineering; Lieutenant Carey reporting."``\textit{What's your status down there?}"``Bridge, we have a total warp core shutdown. We're bringing up the impulse reactors for power generation right now."Pause. "\textit{Lieutenant Carey, this is Commander Janeway. When can we expect warp power to be back online?}"``Commander, the starboard plasma injector has fused shut. That's what caused the plasma backflash throughout the ship. At this point, I have no idea what state the rest of the warp core is in. We might not be able to bring it back up at all; at the very least, it's going to take days to properly inspect it all."Another pause. Carey made a show of twiddling his thumbs; Rodriguez caught the gesture and sniggered. ``\textit{Engineering, we need warp power back as soon as possible}," said Janeway.``I understand, ma'am," said Carey. ``But the backflash hit the reaction chamber. I could have spalling on the chamber wall, I could have microfractures in the pressure vessel, I could have a cracked dilithium crystal for all I know right now. It's going to take some time."``\textit{What about the port nacelle? Can we use that?}"\textit{I cannot believe this is happening to me}, thought Carey. ``Ma'am, the reaction chamber feeds both nacelles. Even if the port nacelle worked perfectly, there's no way to power it."There was yet another long silence. ``Ma'am, maybe we should just call for a tow," said Carey. ``It's pretty long odds we can fix this girl outside of a drydock."``\textit{That's impossible}," said Janeway.\textit{What? Why?} ``Ma'am, the subspace comms should be operational."``\textit{Mr. Carey, come to the auxiliary bridge. I think you should brief me in person}."\textit{With crayons, no doubt}, thought Carey. He was about to argue when a thought occurred to him: \textit{She's out of her depth and she knows it. I might be the highest ranked officer left alive after her.} The thought of taking command of \textit{Voyager} in this state didn't exactly make his heart leap, but at the same time, he realized he trusted himself more than some dweeb who'd taken the bridge officer's exam on a lark--and maybe Janeway did, too.``I'll be right up, Lieutenant." \textit{Whoops. Should have said ``ma'am". Oh well.}``What was that about?" said Rodriguez.``They need me on the backup bridge. Ensign Vorick’s in command, but you’re in charge down here, understood?"``Yes sir."``Oh, and Rodriguez?"``Yes?"``I’m the chief engineer now. I might be the captain of this ship in ten minutes. From now on, when you make a report, stow the colorful language and stick with the numbers."``Undersood, sir. Sorry sir."Carey pointed to a crumpled figure at the foot of the ladder to the upper catwalk. ``And have someone take care of Commander Patel’s body.''``Aye sir."\begin{center}\rule{3cm}{0.4 pt}\end{center}Janeway had never been in so much pain in her entire life. The initial shock of her injuries was fading, along with her brain's natural pain suppressors. Her shoulder felt like someone had taken a welder to it and her headache was getting worse.``Navigation, do you have a fix on our location yet?" she said.``No ma'am, not yet. The best I can tell you is that we're somewhere in the Delta Quadrant, ten thousand light years from the galactic rim. I've found Sagittarius A, but there aren't a lot of other landmarks out here."``Keep looking," said Janeway, knowing it was a tall order. They were on almost the exact opposite side of the Milky Way from the Federation, exactly the area most thoroughly obscured by the giant molecular clouds and the galactic core. They couldn't have gotten much further from Earth if they'd tried.Janeway took another dose of painkiller from the first aid kit and injected it directly into her shoulder, where it did almost nothing. She gritted her teeth. She would hang on until the pain became too distracting to ignore. Then, she promised herself, she'd go to sickbay. \textit{Why hasn't Sickbay reported in yet?} she thought.In front of her, on the viewscreen, was an image of the yellow planet they'd found themselves orbiting, and an alien space station. The star and the planet weren't on any charts in the database, and the space station refused to respond to their hails. They hadn't bothered hailing the planet; there wasn't any point. The surface temperature was over 400 degrees.\textit{Big fat zeroes}, she thought bitterly. She was positive the space station was somehow responsible for their being there, but whoever was on board wasn't talking.The doors hissed open and Lieutenant Carey walked into the cramped auxiliary bridge. He spotted her sitting in the central chair, said ``Lieutenant Carey reporting, ma'am," and then seemed to take a half-step back as soon as he got a good look at her. \textit{I must be some sight}, she thought.``Report, Lieutenant," said Janeway.Carey looked confused. ``Wouldn't you prefer to do this in the briefing room?"``I can't hold my breath for that long," said Janeway. When Carey didn't seem to get it, she said, ``The briefing room blew out along with the rest of Deck One. So just talk to me here."``All right," said Carey. ``The starboard plasma injector fused shut when we tried to go to warp. When that happens, the plasma in the conduit is supposed to be shunted through an escape valve out into space. It didn't. The high pressure plasma stayed trapped in the line until it found an outlet into the low pressure \textsc{eps} system, and then all hell broke loose. Right now, I don't know what kind of damage it did to the reaction chamber, the dilithium matrix, the portside injector, the portside nacelle, the antimatter injectors...nothing, really. Thanks to the \textsc{eps} overload, there's serious damage all over the ship. Electrical power is unreliable, replicators are out, transporters are out, shields are out, \textsc{sif} is out, phasers are out. Like I said already, I don't think the ship can be repaired here. We need a tow back to a starbase. We've probably got more sick and injured than sickbay can handle; those people can't wait until we get propulsion back online."``Mr. Carey," said Janeway.``Ma'am?"``Right now, we are approximately 70,000 light years from the nearest starbase. Whatever force wrecked the ship also pulled us out here. So for the time being, you're on your own."Carey stared, unbelieving, looking back and forth between Janeway and the viewscreen.``We should hail that station," he finally said.``I already did, Mr. Carey."``We should hail them again."Janeway snapped. ``What do you think we've been doing up here, Lieutenant?"\textit{Fucking around}, said Carey's face. ``Sorry, ma'am. I got---"``We need main power back on line as soon as you can get it."``Yes ma'am. What are my secondary priorities?"Janeway reflected on that. ``That's your call," she said.``Yes, ma'am." A long pause, and then, ``Ma'am, where am I in the chain of command?"Janeway tapped the key panel on her armrest. ``First in line behind me," she said.``Was I...was I always behind you?"``How should I know?" said Janeway. The pain was getting worse.``Captain, we're being hailed! Audio only."\textit{Maybe they're friendly}, thought Janeway. ``Put it on speaker."A deep, scratchy, arrogant male voice boomed over the speakers. "\textit{Unidentified ship, this is Jal Jabin of the Kazon-Ogla. Heave to and prepare to be boarded. If you surrender without a fight, everybody lives. If you don't, I'll space every last one of you.}"\textit{Nope}. ``Mr. Gombe, show me the source of that transmission."A massive brown ship, shaped vaguely like the head of a squid, appeared on the viewscreen, approaching them at relatively low speed. It had snuck on them undetected at warp--another bad sign for \textit{Voyager}'s readiness, but not one that Janeway could afford to worry about at the moment.``Red alert," said Janeway.``Shields and phasers are out," said Carey, in case she’d forgotten in the last minute and a half.``Get down to engineering right now," said Janeway. ``Get me whatever shields you can get."``Yes ma'am." He took off running, off the auxiliary bridge.\textit{I'd better stall them, }she thought.``This is Lieutenant Kathryn Janeway of the Federation starship--"Janeway was interrupted by a flash from the Kazon vessel and a sudden explosion on \textit{Voyager}.\begin{center}\rule{3cm}{0.4 pt}\end{center}Voyager shook with the impact of the Kazon weapon. Alarms started howling around the auxiliary bridge.``Damage report!" said Janeway.``Electromagnetically propelled kinetic impactor," said Lieutenant (j.g.) Obayana Gombe, the former backup tactical officer. ``It penetrated the saucer, deck four portside, just aft of the forward turboshaft. Sections 408 and 409 are venting atmosphere."``\textit{I'm waiting, }Voyager\textit{. You have thirty seconds to reply.}"For a moment, Janeway was frozen. Everyone on the bridge was looking at her.``I have photon torpedoes," said Gombe, breaking the silence.``How many?" said Janeway.``Only the ready two in the tubes. The loading system isn't responding."``That should penetrate their shields" she said.He grimaced. ``They should, but they won't," he said. ``There's only enough antimatter in the ready reserve for one one-tenth yield shot, and I can't get the antimatter pumps to respond, either."She wanted to cry. \textit{Now what do I do?} she thought. ``Does anybody have any ideas?"Nobody said anything.``Comms, try to stall them," said Janeway.``How?"``I don't know. Ask them for instructions."There was a flutter of chatter between the comms operator and the Kazon on the other end. ``Ma'am, I asked them about transporting over, but they didn't seem to know what I was talking about." More chatter. ``Ma'am, we're running out of time."``They are charging their weapons," said Gombe.\textit{I can't let this ship fall into their hands}, she thought."\textit{Janeway, this is your last chance. Surrender or be destroyed.}" For emphasis, the Kazon ship fired another slug into \textit{Voyager}'s saucer, smashing open more compartments on Deck 4.``Captain," said the comms operator, ``we're being hailed by another ship. It encrypted with...an old Federation code."``Do we have the key?"``Yes ma'am."``Put it on speaker."\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Val Jean}}\\``I have \textit{Voyager}," said Tuvok.``Are we sure about this?" said Torres. ``Chakotay, you know why they were in the Badlands."``You just keep the warp drive working," he said. He didn't trust three days' worth of jerry-rigged repairs, even B'elana's. It gave him a legitimate reason to shut Torres up before she could reinforce his own doubts."\textit{Unknown ship, this is }Voyager\textit{. Who are you}?"``This is the Liberation Front starship \textit{Val Jean}, and we're coming to save your ass," said Chakotay. ``I can help you, but only if you do exactly as I say."\begin{center}\rule{3cm}{0.4 pt}\end{center}Janeway looked around at her officers. On the one hand, the idea of accepting help from terrorists was repugnant. On the other hand...``Captain, the Kazon say if we don't surrender, they're going to open fire."``Signal our surrender," said Janeway to comms. To Chakotay, she said, ``All right, I'm listening, Chakotay.""\textit{Do you have any photon torpedoes?}" said Chakotay.``Two. But they can't penetrate the Kazons' shields.""\textit{What about your transporters?}"``They're out," said Janeway.``Ma'am, the aeroshuttle has a transporter," said Gombe. ``It still works. I can't operate it from here, though."``Correction, Chakotay: I've found a working pad. Mr. Gombe, send a crew down there to operate the transporters right away."``Yes, ma'am," said Gombe."\textit{Listen to me very carefully}," said Chakotay. "\textit{In two minutes, I'm going to drop out of warp in phaser range of the Kazons. The Kazosn don't have subspace sensors, so they don't see me coming. Once I drop out, I'll need to remote operate your transporters. I’ll need one photon torpedo, armed and ready to fire, waiting on the pad.}"``There's no way we can get the torpedo hauled to the aeroshuttle in time," said Gombe.``Do a site-to-site transport, then," said Janeway.``Ma'am, transporting antimatter once is risky enough---"``Do you have a better plan?" said Janeway.``No ma'am. Readying the torpedo."``All right, Chakotay. I'm sending the remote access code for the aeroshuttle's transporter systems. They'll be online by the time you get here.""\textit{Acknowledged, Voyager. Chakotay out.}"``How do we know he's not just trying to steal a photon torpedo?" said Gombe.``It's not like it's doing us any good."``I suppose not, ma'am." He glanced down at his station. ``Captain, the Kazons are launching boarding shuttles."\begin{center}\rule{3cm}{0.4 pt}\end{center}Harry Kim ran like he never had in his entire life, his feet pounding on the deck as he approached the aeroshuttle airlock. With his normal Red Alert station---backing up the ops officer on the main bridge---destroyed, he had run around looking for the auxiliary command center until some damage control officer corralled him and sent him down to Deck 9 forward to supervise a gang of ratings on firewatch. He'd had to come by emergency ladderway, and his heart had been hammering by the time he'd scrambled down nine flights. He hadn't even found the ratings when another officer, a j.g. lieutenant named Nozawa, grabbed him.``Do you know how to power up a runabout?" he'd said.``Yes, sir," said Kim, who'd done particularly well on that unit.``Good. We need to get the aeroshuttle's transporters online in the next ninety seconds."Kim gulped and followed Nozawa at a dead run through three hundred meters of half-lit, smoke-filled, debris-clogged lower-deck passageways to the aeroshuttle docking port. Fortunately, the airlock doors still worked. Inside, to Kim's right, were the cabins and cargo spaces and a passageway to engineering. To his left was the standard forward cabin of a \textit{Danube}-class runabout, modified to dock semi-permanently with \textit{Voyager}.Nozawa pointed to the cockpit. ``You start up the ships's systems from there. I'll go operate the transporter. You've got about one minute."``What are we transporting?" said Kim.``A live photon torpedo, so make sure the voltage is steady." Kim nodded, swallowed hard, and bolted for the pilot's chair.As soon as he sat down, the Okudagram control panel lit up, instantly filling Kim with paralyzing terror. For six, seven heartbeats, he couldn't even read the labels.``I'm ready when you are!" shouted Nozawa.That broke Kim out of his trance. His training rushed back and his fingers danced across the panel. Unfortunately, as the startup procedure unfolded, he realized he was never going to get the impulse reactors started in time, let alone the warp drive. He checked the umbillical connection from \textit{Voyager}. It was stone dead; Engineering had cut the aeroshuttle off to conserve power. ``Oh, shit," he said.Then the lights on the panel reminded him. If the panel was on, then the aeroshuttle had a battery, which meant...``You've got power!" he shouted at Nozawa as he flipped open the circuits.\begin{center}\rule{3cm}{0.4 pt}\end{center}``Thirty seconds to impulse," said Mohommad.``Are you sure about this?" said Seska.``You think we can get home without Starfleet's help?" said Chakotay.``Do we want Starfleet's help?" said Bendera. ``They'll arrest us the minute we get back."``Look at them," said Chakotay. ``They're a wreck. Once we're back in the Badlands, we'll leave them in our dust. But we need to get back to the Badlands first. Tuvok, ready phasers. Bendera, stand by; they're going to hand over transporters to you the second we drop to impulse." He turned to Seska. ``Are you sure you have the timing down?"``Yes," she said.``All right," he said. ``Tuvok, make sure you only fire on the mothership. If we wipe out their boarding parties, there's no reason for them not to shoot \textit{Voyager}."``Ten seconds," said Mohommad.\begin{center}\rule{3cm}{0.4 pt}\end{center}On the aeroshuttle, Nozawa activated the transporter and held his breath while the sleek black torpedo materialized on the pad.Outside, the Kazon boarding shuttles drifted in, a few hundred meters from \textit{Voyager}'s hull. The first group of them had started slowing to contact speed.On the Kazon battleship \textit{Predator}, Maje Jal Jabin watched with growing excitement as his boarding parties approached the crippled alien starship. The Caretaker had provided many victims for the Kazon-Ogla, but he sensed that he had one of the great prizes of his career at his fingertips. There was something about the streamlined, white, alien hull which suggested great power and sophisticated technology. Ships like it had come here before, but they'd outrun or outfought him or destroyed themselves.He didn't notice how his boarding shuttles were blocking most of his best firing lines to \textit{Voyager}.On the auxiliary bridge, Janeway called Carey on the intercom. ``Mr. Carey, if this doesn't work, we'll fight the boarding parties for as long as we can. But this ship can't fall into the hands of these aliens. If Engineering falls, you blow the antimatter pods. Do you understand?"Down in engineering, Carey and Rodriguez looked at each other for a long moment. Then Carey, his voice shaking, said ``Yes, ma'am," and dialed up the controls for the antimatter containment fields.\textit{Val Jean} screamed towards the Caretaker array at many times the speed of light.\begin{center}\rule{3cm}{0.4 pt}\end{center}``Captain, another ship is approaching," said Gombe. ``Maquis raider. They just dropped out of warp and they're closing fast."``On screen," said Janeway.Janeway's heart sank when she saw the condition of the little raider. Its hull was covered in hasty patches and fresh burn marks; it could scarcely be in much better condition than \textit{Voyager}. She spotted a hole in the hull just a few meters from the flickering port warp nacelle; the ship's engineer had to be both incredibly good and incredibly reckless to keep the ship operating at warp speed in that condition."\textit{Bridge, this is the aeroshuttle}," said Nozawa. "\textit{Val Jean} \textit{has taken control of the transporter}."``The Kazons are firing on \textit{Val Jean}," said Gombe. On the screen, the computer highlighted depleted uranium shells streaking within a few kilometers of the Maquis ship.Janeway could do nothing but cover her mouth with her hands and wait.\begin{center}\rule{3cm}{0.4 pt}\end{center}``They've got us bracketed!" said Seska.``Mohommad, give them whatever you've got left!" said Chakotay.``They're recharging their forward coilguns," said Tuvok.``Bendera, now!" said Chakotay.\begin{center}\rule{3cm}{0.4 pt}\end{center}Harry Kim could hear the whine of the transporter as the torpedo vanished.\begin{center}\rule{3cm}{0.4 pt}\end{center}Gombe's eyes went wide. ``Captain, I know what he's doing! The Kazon have to open a hole in their shields to fire their weapons!"\begin{center}\rule{3cm}{0.4 pt}\end{center}Deep in the bowels of \textit{Predator}, near a critical three-way power junction, a Kazon crewman named Mierna was startled by a high-pitched whine. He turned around to see a black, lozenge-shaped device shimmer into existence. He reached out to touch it.The world exploded.\begin{center}\rule{3cm}{0.4 pt}\end{center}The explosion ripped through the port side of \textit{Predator}, disintegrating steel and flesh alike in a blaze of gamma rays, creating a blast wave of metal vapor that piled up against armored bulkheads and broke them down one after another after another. Spikes of death and fire radiated along corridors, ladderways, and conduits, killing and destroying in every part of the ship. One such spike reached the port warp nacelle, turning twenty-five thousand tons of irreplaceable warp coil into scrap. Another cracked open the deeply armored central core, just a few compartments away from where Jal Jabin was in the process of being hurled through the air by the shockwaves reverberating back and forth through Predator. Out on the ship's surface, armor spalled away and the hull cracked open, spilling living Kazons into the vacuum.Janeway stared, gape-mouthed, at the slowly spinning wreck Predator had become. And yet, there still was a ship to stare at. Her engines, unbelievably, were still working. A few shield panels still flickered. There was power to her guns. \textit{Val Jean} wasted no time, blasting the wounded Kazon battleship with phasers.Suddenly, \textit{Predator} heaved, like a wounded animal trying to shake off a pair of grasping predators. Subspace bent, and \textit{Predator} was gone, warping away at barely more than the speed of light, with all her boarding shuttles abandoned to Chakotay's tender mercies.``Kazon boarding parties, this is---" said Janeway. That's all she got out before each and every shuttle popped, like a string of firecrackers, self-destructing, leaving them no prisoners and no answers to the ten thousand questions Janeway had.\textit{Voyager} floated in the sudden calm over the hothouse world. The alien space station sat, implacable, unperturbed."\textit{Val Jean} \textit{to} \textit{Voyager}", said Chakotay. "\textit{We need to talk.}"\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Voyager}}\\It had taken forty minutes of negotiation just to agree on a meeting place. All the while, Janeway's headache and shoulder kept getting worse. Janeway finally gave up and agreed to beam over to \textit{Val Jean} in an hour's time, then went to sickbay to have her shoulder repaired.The sickbay was bedlam, with patients slumped in the passageway outside, bleeding on the deck and smearing more blood on the walls. When the wounded parted to let her pass, she felt intense guilt.Inside, the carpet was drenched in blood and a single doctor, assisted only by a handful of goldshirts performing basic first aid, was working on patients virtually stacked one on top of another. He worked on a patient lying on the stasis bed, his hands moving faster than Janeway could follow, and she realized he was an artificial human---either an android (which seemed unlikely, since she only knew of one in Starfleet) or a hologram. The \textsc{emh}.He was working frantically on a gold-shirted crewman second class. He had opened her chest cavity without even bothering to remove her uniform or set up a partition---only the sterile force field separated them from the rest of sickbay. As Janeway approached the operating table, he suddenly looked over at her and said, ``Please stand back, captain." His voice and face were flat, neutral. His hands never stopped moving.Alarms started piling up. The woman's vital signs were collapsing. Her heartrate and breathing zeroed. The sickbay went quiet. The doctor kept working, even reaching under her sternum to manually stimulate her heart. No matter what he did, though, it refused to beat anymore.Finally, he gave up. He withdrew his hands and, still showing no emotion, shimmered briefly. The blood coating his arms hung in midair for the briefest instant, like a pair of gloves. Then it splashed to the deck.``She's dead," said the doctor. He pointed at two goldshirts, who were injured themselves with burn blisters on their faces. ``Take the body." They hustled through the sterile field, grabbed the dead woman from either end, and hauled her off. As they passed, Janeway reached out with her good hand and stroked the woman's face, once.The doctor turned to Janeway. ``Please step through the sterile field," he said. She did, feeling numb. The field burned, like rubbing alcohol, as she walked through.``What was her name?" said Janeway.``Crewman Second Class Pullman," said the doctor. ``I have noted her death in the medical log." He scanned Janeway with a medical tricorder. ``You have a dislocated shoulder and a concussion," he said, as he guided her to sit on the edge of the table on which Crewman Pullman had just died (the self-cleaning bed and deck had already dissolved and absorbed her blood). ``You should have come to me immediately. Hold still."``How many other dead?" said Janeway.``Forty-six," he said, as he injected something into her neck via hypospray. Janeway blanched. That was nearly a third of the ship's crew.``Where's Dr. Fitzgerald?" said Janeway.``Dr. Fitzgerald is dead," said the hologram.Janeway jumped off the table, too angry to notice her headache was gone. ``Why the hell didn't anybody tell me?" she said. All the conversation in sickbay died as every conscious patient turned their heads to look at her. Even the doctor didn't respond.Janeway's ears started burning and she was about to slip back onto the operating table. Yelling at sick people wasn't going to make it better. She tapped her commbadge. ``Attention all hands: this is Acting Captain Janeway. Listen carefully: I am ordering everyone to report his or her status and location to the computer. I need to know where everybody is and what they're capable of now. Computer, collate the data the crew sends you," said Janeway. ``I want a map of where everyone is and an organizational chart of who's still alive." She tapped her commbadge off. ``Are you sapient?" she said to the doctor.``I am capable of independent initiative," said the Doctor. ``And I am aware of myself as an object distinct from my surroundings." He poked his index finger though the surface of the table. ``For a given value of `object'."``Close enough for government work," she said. ``Until further notice, you're the acting \textsc{cmo}."``Captain, I must point out that I do not have a Starfleet rank and thus I am legally unable to serve as \textsc{cmo}."\textit{Shit}, thought Janeway.``However," continued the Doctor. ``I should also note that as commanding officer of \textit{Voyager}, you have the authority to issue brevet commissions."``Even to holograms?"``The regulations do not specifically exclude holograms."``Fine. I hereby issue you the brevet rank of Lieutenant and appoint you \textsc{cmo} of \textit{Voyager}," she said. The Doctor nodded. A pair of rank pips appeared on his collar.``Captain, I need to reset your shoulder," he said.Janeway took a deep breath, held it, let it out. She knew what was coming. ``All right. Let's just do it."``Relax your arm," he said. He gave her a hypospray of painkiller, which wasn't enough, and started carefully manipulating her arm.``It's the twenty-fourth century," she said. ``You'd think they'd have a better way to do this."``Please hold still," he said. A muscle spasmed and she cried out. The Doctor was unrelenting, continuing to rotate her arm. It took everything she had not to beg him to stop.And then, suddenly, there was a *pop* and her arm was back in place. Instantly the pain...well, it didn't exactly disappear, but it changed to something more tolerable, and it got more tolerable still when the Doctor gave her another hypospray. He bound her arm in a sling. ``I gave you medication to speed up your body's natural healing process," he said, ``but you will still need to keep your shoulder immobile for the rest of the day. I have also given you something for your concussion; however, you are still at risk for dangerous brain swelling if you suffer another head injury, so take special care to avoid them."Janeway nodded, grateful that the intense, distracting pain was gone. She barely even noticed her concussion headache was gone, too.``Is there anything you need, Doctor?" said Janeway.``More assistance," he said.``I'll see what I can do," said Janeway.``Captain," he said. ``You should be aware: I was only designed to operate temporarily, as emergency relief. It would be in your best interest to find a replacement doctor as soon as possible. I cannot predict what will happen to my program if I am left running in the long term."``I know that," she said. ``Right now, your closest replacement is 70,000 light years away, so we're going to have to get by with you."``I understand," he said.``Can you spare a \textsc{padd}?"``On the desk."Satisfied, she took the \textsc{padd} and left sickbay.Her next stop was engineering. The turbolifts still weren't working and there were depressurized compartments all over the ship, forcing her to take a roundabout path. She made use of her time by going over the \textsc{padd}, where the computer had already downloaded data on the surviving crew. She grimaced once at the numbers---not only was a third of the crew dead, but a disproportionate number had been high-ranked officers, most of whom died in the bridge blowout. She grimaced again when she saw the map. People were scattered at random, with no regard for chain-of-command or actual expertise, leaving her with such absurdities as the ship's only surviving \textsc{ops} officer supervising a firewatch on Deck 9 while she tried to run the auxiliary bridge with an able crewman on the \textsc{ops} station. Damage control and Engineering seemed to know what it was doing, but everyone else was lost.She was still pondering this when she arrived in Engineering. Carey was standing in the control room, giving instructions to what seemed like three different people at once."...look, don't worry about the starboard engine," said Carey. ``Just get the portside running so we'll have impulse power again. We can always vector the thrust." He looked up and noticed Janeway. ``Captain," he said. ``What can I do for you?" He was plainly annoyed she was there.``What's your status?" she said.``I could have told you that by commbadge."``I was in the neighborhood," said Janeway.``Fine," said Carey. ``We're trying to get the impulse engines back online so we have mobility."``What about power?" said Janeway.``We're drawing auxiliary power off the fusion reactors. Those still work; we're just having trouble with the reactant pumps."She pointed at the dead warp core. ``What about main power?"``We're still inspecting it," said Carey, ``Technically, after that, we could probably start the warp core. The thing is, though, after a violent shutdown, regulations say we need to conduct a level-1 diagnostic on the entire system. That could take days."``Then shouldn't you be getting started?" said Janeway.``I could, but it would occupy practically my entire department. I think it would be better to use my people to get the rest of the ship in working order."``And when were you going to tell me about it?" said Janeway.``I was going to get to it," he said. ``Are you going to order me to restart the core?"\textit{You are a presumptuous little shit}, thought Janeway. But she hesitated before upbraiding him. He might have been right about the warp engine; it was very uncomfortable, she realized, giving orders to technical specialists which contradicted their technical judgment. ``Mr. Carey, I'm going to follow your recommendation," said Janeway. ``But in the future, I expect to be consulted before you make decisions like this."``Yes, ma'am," he said.``All right, I'm going over to talk to the Maquis. Do the transporters work yet?"``Not yet. You'll have to use the aeroshuttle's transporters."``What about one of the regular shuttles?" The shuttlebay was a lot closer than the aeroshuttle dock.``No air in the shuttlebay," said Carey.``Right," said Janeway. ``Aeroshuttle it is, then." She left engineering, trying to remember how to get to the aeroshuttle dock. The map on the \textsc{padd} helped. She weaved through debris-strewn passageways and around gold-shirted repair teams.Carey didn't respect her and didn't care if she knew it. The further she walked from engineering, the more disgusted she was with herself for putting up with his attitude. Not for the first time that day, she wondered how in the hell she'd wound up in charge of \textit{Voyager}. Why hadn't Bujold put her at the end of the line of succession? Why had she taken the bridge officers' exam in the first place? She was a scientist, not a leader. She was born to do battle in the halls of academia, with contemptuous letters to the \textit{Starfleet Meteorological Review} editorial page. She hadn't planned on getting into actual battle with alien space pirates, let alone in a crippled ship on the wrong side of the galaxy.``You are getting dangerously close to feeling sorry for yourself, Kathryn," she said out loud. A nearby rating turned his head. Fortunately, he didn't seem to recognize her.She checked the ship's org chart again. Among the departments decapitated was Science---the computer had removed her as department head when she got promoted to \textsc{co}-by-default. She checked the next name down and tapped her commbadge. ``Janeway to Ensign Wildman."``\textit{Wildman here.}"``Have you ever run a science department before?" said Janeway.``\textit{No, ma'am.}"``You're about to," she said. ``We have to get our heads together. Gather up everyone in the department you can find and start working on how we got here and how we're going to get back. If the sensors don't work, notify Lieutenant Carey and get a repair team on it. First priority is that space station. Do a scan of the planet, too, while you're at it. Maybe there's something we missed the first time."``Yes ma'am," said Ensign Wildman.``Janeway out," said Janeway, who only afterwards realized she had no idea what Ensign Wildman even looked like.She walked on, fiddling with the \textsc{padd}. She dragged names around with her finger, trying to put together a chart that made sense. She was resigned to putting ensigns and junior grade lieutenants in charge of departments; in that sense, she was lucky to have Carey, or else an ensign would have been her chief engineer.And speaking of ensigns...She found him standing in the middle of a group of crewmen, looking lost. Gold shirt, one pip, round face, jet-black hair. ``Ensign!" she said.He jerked and spun around. ``Yes ma'am?" he said.``What's your name?" she said.``Ensign Harry Kim, ma'am," he said.``You're the backup ops officer, right?" she said.``Yes, ma'am."``I see. Then what the hell are you doing down here?"``I was sent by---"``I don't want to hear it," she said. ``This ship needs an ops officer. You're the only one left, I'm sorry to say. Get your ass to the auxiliary bridge, on the double."Ensign Kim spent a moment staring, wide-eyed. ``Yes, ma'am!" he said. He scurried away.\textit{Did I just chew the ass off a baby-faced ensign because I let Carey walk all over me?} she thought. The crewmen were still standing around, watching her.``Computer," she said. ``Locate the nearest \textsc{nco}."``Petty Officer Jarvis is in section 917," said the computer.``You heard the computer," said Janeway. ``Get to section 917."The crewmen saluted and scattered. ``You sure showed them who's boss," said Janeway to the empty air. She sighed and walked towards the aeroshuttle dock.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Val Jean}}\\Chakotay, Seska, and Bendera waited in \textit{Val Jean}'s tiny transporter room. Chakotay tapped his foot. It made him nervous, having Starfleet on his ship.``Are you sure about this?" said Seska.``I told you once: that ship's a flying science lab. Unless you think Tuvok can figure out how that station works all by himself, we're going to need their help to get home."Seska nodded. ``I understand. Just don't start trusting them."``What do I look like?" said Chakotay. ``Some kind of idiot?"The transporter hummed to life. After a few seconds of sparklies, a lieutenant with a blue uniform and her arm in a sling appeared on the pad.Chakotay was instantly annoyed. \textit{What, I'm not worth Janeway's precious time}? ``I thought you were sending Captain Janeway," he said.The woman smiled grimly. ``I'm Acting Captain Janeway," she said. ``You must be Chakotay. Permission to come aboard?"Chakotay was glad his skin was dark enough to hide his flush. Beside him, Bendera was swallowing laughter. ``Yes, of course," said Chakotay, recovering himself. He offered his hand. She stepped down off the pad and shook it. Her grip was firm, and she looked him straight in the eye. Only a slight rivulet of sweat on her temple betrayed how nervous she was.``Well, we should get started straight away," said Chakotay. ``This is my second-in-command, Seska Jiasha, and my sensor operator, Kurt Bendera. Kurt will lead us to the mess."Tuvok and B'Elana were waiting in \textit{Val Jean}'s cramped mess. Janeway greeted them all with handshakes and, for Tuvok, a tentative Vulcan salute. ``Take a seat wherever you want," said Chakotay. ``We're not formal here. Do you want anything to eat?"Janeway shook her head. ``I'd rather get started," she said.Janeway sat down at the end of the table. The four Maquis clustered at the other. ``Well," said Chakotay, ``first things first. What brings you to the Delta Quadrant?"Janeway explained the story of how they managed to join \textit{Val Jean}, starting in the Badlands. She was surprisingly candid about the fact \textit{Voyager} was hunting them; he had expected a line of Starfleet bullshit about cataloging gaseous planetary anomalies or something. She was frank and candid about the damage to \textit{Voyager}, too. More than once, he and Seska exchanged glances. No wonder they'd had so much trouble with the Kazons.``What about you?" said Janeway. "\textit{Val Jean} looks like she's seen some action, too."``We took all of this back in the Alpha Quadrant," said Chakotay. ``When we arrived here, we had some bumps and bruises, but no more damage to the ship. The Kazons showed up, but we outmaneuvered them and they couldn't score a hit. That's how we learned they don't have subspace sensors."``And the transporter trick?" said Janeway.``Seska's idea," said Chakotay. ``She was the first one who noticed they had to open up gunports in their shields."Janeway nodded her thanks to the Bajoran. ``I'm sorry we didn't have more juice in that torpedo."Chakotay shrugged. ``Those are tough ships. They're not very sophisticated, not a lot of technique, but they're built for slugging matches. They're punchers." He shadowboxed a little to demonstrate.``What do you know about the station?" said Janeway.``Not much," said Chakotay. ``Our sensors were mostly fried when we got here, and we didn't hang around very long. We've spent most of the last three days in this system's Kuiper Belt, trying to put the ship back together. Tuvok's been studying what we have, but it's not much. We were hoping you could gather more. A lot more."Janeway nodded. ``The entire science department on \textit{Voyager} is working on the problem. I'm willing to share data with you."Chakotay looked to Tuvok. He nodded. ``Send it to Tuvok," said Chakotay. ``What do you want in exchange?"``We'd like you to stick around to give us a hand if the Kazons show up again."Chakotay nodded, but added a caveat: "\textit{Voyager} can take a lot more punishment than this ship. She can dish out a lot more, too. You'd be better off if you could defend yourselves."``We're working on making repairs," said Janeway. ``We have the impulse reactors providing auxiliary power, and the engines themselves should be online soon."B'Elana spoke up. ``What about your warp core? Doesn't that provide the bulk of the power to your shields and phasers?"The look on Janeway's face said it all: \textit{I don't know}. She looked suddenly like a student who hadn't done her summer reading. ``Yes," said Chakotay. ``All modern Starfleet vessels do it that way."Janeway slowly nodded. ``Yes, it does. But it could take days, possibly weeks to get the warp core back online."Torres scowled. ``If it was that damaged, you would have lost the ship," she said.``My chief engineer has assured me that if we do it by the book, the inspections alone will take days," said Janeway. She was trying and failing not to sound defensive.``So throw out the book," said B'Elana. ``We don't have time for Starfleet bullshit."``B'Elana!" said Chakotay.``The `book' was written in blood," said Janeway. ``Every procedure in there exists because---""---because of hard-won experience, right, I know," said Torres. ``I got that lecture in the Academy, too. But that's a load of crap. \textit{Half} those procedures were written in blood. The other half were written by lawyers. The trick is to figure out which is which. Your chief engineer should know, if he’s any good at his job."``That's enough, B'Elana," said Chakotay. He lowered his head, took a breath. ``But she's right, Captain Janeway. Now isn't the time for following the book. The Kazon will come back; you can count on that. Safety's important, but so is combat readiness." He scratched his chin. Janeway was listening. She looked angry and defensive, but she wasn't arguing. ``I have an idea," he said. ``How about I sent B'Elana to \textit{Voyager} to help your chief get the warp reactor restarted? She's gotten this old girl running more than a few times."``I think," said Janeway, ``that there's a difference between an \textit{Intrepid}-class warp drive and whatever's powering this thing."``It's powered by matter and antimatter, isn't it?" said Torres. ``I've gotten this `thing' flying with worse damage than what you've got, and without a team of crack Academy-trained engineers to help me. If your guy can't get it done, then beam me over there and I'll have your warp drive running in half a day."``B'Elana, maybe you should---" said Chakotay.``I want to go \textit{home}, Chakotay!" said B'Elana. ``I want to get the hell \textit{out} of here, and right now our only ride home is broken and nobody's trying to fix it!"``B'Elana, go," said Seska.Torres slammed both fists down on the table before storming out of the room. Nobody said anything for a moment.``She's right," said Seska. ``And she's good. She's not some Maquis wrench monkey. She knows how to nurse a warp core."``So do my engineers," said Janeway. ``I'll decide when and how we bring our warp drive back online." She stood up. ``Are we finished here?"Chakotay stood as well. ``Yes, I think so."Tuvok, who had said nothing the whole meeting, finally spoke up. ``Captain Chakotay, Captain Janeway, with your permission, I would like to transfer to \textit{Voyager}."``What for?" said Chakotay and Janeway simultaneously.``I believe it might be useful for me to liaison directly with \textit{Voyager}'s scientific staff."Chakotay looked at Janeway. ``I have no problem with that. He could be useful to you; he's the closest thing to a scientist I have."Janeway nodded. ``For something like this, face-to-face works better than e-mail. All right, I agree. He can come back with me."``Good," said Chakotay. ``Captain, I'm sorry about B'Elana's outburst. Please consider my offer if you find yourself shorthanded in engineering."``I will," said Janeway. She had smoothed down her uniform and had put her calm, professional Starfleet face on. Chakotay had read enough of those to know she meant,\textit{When hell freezes over}.Chakotay escorted her back to the transporter room, along with Tuvok, Bendera, and Seska. When the Vulcan and the Starfleet officer finished dematerializing, Chakotay turned to the other two.``Well?'' he said.``I think she's an idiot and she's going to get us all killed," said Seska.``What do you think, Kurt?'' said Chakotay.``I don’t know,'' he said. ``I think there might be something to her.''``Working with her is a mistake,'' said Seska.``You have any better options?" said Chakotay.Seska said nothing.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textbf{\textit{Voyager}}\\To Janeway's surprise, she materialized in \textit{Voyager}'s regular transporter room. Carey must have gotten them fixed. The lights were burning steady, too. Not bad for half an hour's work.``Welcome to \textit{Voyager}," she said to Tuvok. ``Let me show you to the science labs."``Captain Janeway," said Tuvok. His face was an expressionless Vulcan mask. ``There is one thing I believe you must know."``What?" she said.``I am not a Maquis. I am an agent of Starfleet Intelligence, working undercover within the Maquis. Once we return to the Alpha Quadrant, I intend to arrest Chakotay and his crew."``What the hell is this?" said Janeway, ``Some kind of test? You can tell Chakotay that if he doesn't want to trust me, he can find his own way---"``Computer," said Tuvok. ``Verify Starfleet identity number and biometric signature." He rattled off a string of letters and numbers.``Identitiy comfirmed: Lieutenant-Commander Tuvok, Starfleet Intelligence," said the computer.Nobody said anything.``I take it," said Tuvok, ``that Captain Bujold did not brief you fully about \textit{Voyager}'s mission."``No, she didn't, actually," said Janeway. \textit{Fuck me running}, she thought.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textbf{Kazon battleship \textit{Predator}}\\\textit{Predator} limped at low warp back to base, one system over from Ocampa. Maje Jabin cursed the Caretaker for not allowing the Kazon to maintain a base in its system, cursed the aliens for what they'd done to his ship, cursed himself for falling into their trap, and cursed his ship for just barely surviving, instead of simply exploding and saving him from the disgrace that awaited him once word of this disaster spread.``Kinell!" said Jabin. ``Your report!"Jabin's first mate scurried up to the dais where Jabin kept his command seat. Kinell was carrying a tablet with a video queued up. ``We found the security footage," said Kinell.``Let me see," said Jabin, taking the tablet. He started the video. On the screen, a Kazon warrior---the hapless Mierna---was guarding a primary power junction. Suddenly, behind him, there was a shimmering, sparkling light, and a black lozenge-shaped, coffin-sized container appeared out of thin air. Mierna reached out for it, there was a flash, and the camera went dead.``So they do have some kind of teleporting weapon," said Jabin. ``How did it get through our shields?"``We don't know yet, Maje," said Kinell.``Well, find out!" said Jabin.``Yes, Maje," said Kinell. He scurried away with the tablet.Jabin sat back in his seat and thought about many things---about how to salvage what he could from \textit{Predator}, about all the letters he had to write to newly-made widows and orphans, about how he was going to explain and atone for this disaster, about how he might save his honor and career. But most of all, he thought of that sleek white alien ship, latest in a string of increasingly capable and dangerous ships the Caretaker had dropped in his lap, about teleporter bombs and shields and how he was going to punish those aliens if it was the last thing he ever did.He thought about the \textit{Caretaker}, too. ``That fucking machine," he said, ``is becoming more trouble than it's worth." After a while, he took out his own tablet and started composing his thoughts.\begin{center}\rule{3cm}{0.4 pt}\end{center}
\noindent\textbf{Acting Captain's Log, Stardate 48308.1}:\\
\textbf{It has been twelve hours since we have arrived in the Delta Quadrant. I remain in command of \textit{Voyager} as acting captain, despite my own reservations about my qualification for the position. Starfleet doctrine is clear: in a crisis, a stable chain of command is vital. Accordingly, I have assigned the senior surviving officers in each department the position of acting department head. The only position still vacant is first officer. I can't spare anyone to take the job; as it is, I have ensigns and junior lieutenants heading departments. Lieutenant Carey is the most senior surviving officer besides myself, and should I be killed or incapacitated, command of \textit{Voyager} will devolve to him, but the actual duties of first officer---discipline, organizing department heads, and the regular day-to-day minutia of running a starship---I have taken on myself.}\textbf{In the meantime, the enormous task of repairing \textit{Voyager} continues. Our defensive systems are working again---more or less. Without warp power, phasers and shields are limited to less than half their full capacity. Worse, our impulse drive is still out; after three failed test starts, engineering still has not identified the problem. Fortunately, we do have photon torpedoes working properly again, and the structural integrity field is back at full strength. Mr. Carey had to use most of our spare plasma relays to do it, but he reminded me how badly damaged we were by our trip out here. If we have any hope of surviving a return trip to the Alpha Quadrant, we'll need the SIF at full strength.}\textbf{We still have no warp power and no prospect for getting it. I stand by my conviction that Starfleet regulations were written for a reason, and we can't risk further damage to the ship by restarting the warp core without a full inspection...but every minute we sit here, exactly where the Kazons found us the last time, I itch.}\textbf{Our only hope for returning home lies with whatever brought us here to begin with. We know the station is involved—\textit{Val Jean }observed it activating when we came through, and we’re reviewing their data—but we don’t know who or what is operating it. More than one person has suggested that the Kazons are somehow controlling it. I admit the idea has a certain logic, but it’s hard to imagine them having any trouble dealing with us if that were the case. More likely I think they’re opportunists that prey on the station’s victims. What’s maddening is not knowing why the station does what it does in the first place.}\textbf{For now, our only hope of getting home lies in figuring out the answer to that question. Ensign Wildman is coordinating the science department to learn everything we can about the station and the planet below. As expected with a 22 year old ensign, there have been a few snags in organization that required my personal intervention to sort out, but we're now collecting good data and have started analyzing it. I'm helping with that as much as I can, when my other duties don't demand my attention.}\textbf{Which brings us to the problem of Tuvok. Ostensibly, he's here to assist the science department and report our findings back to Chakotay. I find that he hasn't been much help. Humans tend to assume every Vulcan is either a scientist or a mystic, but just because a man has pointy ears and a uniform, doesn't mean he's Mr. Spock. Tuvok knows barely more about science than a fresh academy graduate. He’s quite intelligent, but he has virtually no formal scientific education. He may well have been Chakotay's go-to `science guy', but that could only be because the rest of his crew knew even less. }\textbf{Lieutenant Gombe, who does not know Tuvok's true mission, suggested Chakotay must know that Tuvok can't help us in the science department, and sent him as a spy. At first I dismissed it as too clumsy, but I wonder if Chakotay, for all his tactical skill, truly understands intelligence and counter-intelligence. The evidence suggests otherwise; after all, one of his most trusted subordinates is a Starfleet spy.}\textbf{I wish I didn't have to think about this. I have enough problems without worrying about how we're going to arrest the Maquis (who saved our lives) as soon as we get back. Tuvok wants a meeting to talk about it; I've put him off for now.}\textbf{Finally, the casualty report. The Doctor [note to self: he needs a name] has revised the total number of deaths up to fifty-three, with six missing and a dozen more critical injuries that require hospitalization. That's more than one-third of the crew dead or incapacitated. The missing are almost certainly crew members who were incinerated by plasma blowouts or blown out into space. The only hope left is that some of them are trapped in isolated compartments that have lost internal sensors. The Doctor has devised a probe we can beam into these compartments without risking the lives of search crews. I'm sure it's an illusion, but he seemed quite proud of it. We will start beaming them to ``black" compartments within the hour.}\begin{center}\rule{3cm}{0.4 pt}\end{center}Paris was sulking in his bunk when he was startled by a bright flash, followed by a single whoop of the red alert siren, before he was flung to the deck of the brig. He stood up, only to get thrown to the deck again by a violent shock.``What the hell was that?" said Paris. He crawled to his bunk, held onto it as he rose to his knees, braced for another shock. He looked around, noticing the lights were flickering. The cell's forcefield held steady, powered by a 72-hour backup battery if main power became unreliable.The Andorian able crewman who had been guarding the brig had fallen to the deck, but was pulling herself up at her station. She had a huge cut on her face, and blue blood was dripping off her chin onto the control station.``Hey!" said Paris. ``What's happening?"``Quiet," she said. Her fingers flew over the control panel.``Let me out," said Paris. ``I know first aid; I can help you."``I said keep quiet," she said. She tapped her commbadge. ``Brig to security."``Security," replied whoever was on the other end of the channel. It sounded like pandemonium in the background.``This is Tsien. I'm requesting instructions."``Stay at your post."``Acknowledged."``That's it?" said Paris. ``You didn't even ask them what happened."``They're busy," she said.The lights steadied themselves. Paris was starting to wish he was back on New Senegal.``You're bleeding pretty bad," he said.``I'll be fine."``You should let me help you."``You are not to leave your cell."\textit{Andorian pride}, thought Paris. \textit{Even a Klingon would put a bandage on that.} ``Look, I'm a pilot, not some kind of kung-fu master. And you have a phaser. There's a dermal regenerator in the first aid kit over there. Let me out, I'll fix you up, and then I'll go back in my cell. If I try anything, you can stun me and dump me back in here."She hesitated before responding.``We're on a starship," he said. ``Where am I going to go?" \textit{To the shuttle bay, after I seal your eyelids shut, steal your phaser, and shoot everyone between here and there.}A low-warp shuttlecraft would be just the thing in the Badlands.Able crewman Tsien touched a button on the control panel; Paris heard the brig's security doors lock. ``Okay," she said. ``I'll let you out."She was reaching for the panel when there was a deafening bass roar---\textit{the warp core!} thought Paris---and all the lights went out. Behind able crewman Tsien, a wall panel blew out in a fountain of iridescent gas. For an instant she was silhouetted against a cloud of blue death, and then she was overwhelmed, her scream cut off as if by a knife, and the brig force field glowed blinding purple-white against the energy of the plasma.Eventually---it was only a few seconds, though it seemed like decades for Paris---some cutoff valve upstream shut off the plasma flow and emergency vents opened in the brig, flushing the atmosphere, clearing the air so that Paris could see the devastation the blowout had wrought. Nothing was left of able crewman Tsien except a pile of steaming bones.\begin{center}\rule{3cm}{0.4 pt}\end{center}Paris woke from his nightmare into thick, steamy darkness. The ventilation and lights had failed in his cell hours ago, leaving him to drift in and out of oxygen-deprived consciousness total blackness, while the air grew hotter (has the cooling system failed? he thought) and saturated with dampness from his own breath and body. When he was awake, all he could think about, besides his own misery, was how stupid he'd been to get himself stuck in this situation. Once again, he'd screwed up, and this time, it would probably kill him.His eyes were so dark-adapted that the faint blue sparkle of transporter dazzled him. It was outside the cell. Instinctively, he stood up and tried to walk over to get a better view, only to be stopped by the forcefield, the only thing left on the brig that still worked. Even from his angle, he could tell it wasn't man-sized.``Hey!" he shouted anyway. ``Help me!" And then he stopped shouting, momentarily flabbergasted, when he saw what had arrived in the brig. Floating just outside his cell, illuminated faintly by the lights of its own screen, was an unfolded medical tricorder, dangling from the bottom of a hoverball.After a minute, it disappeared in another ripple of sparkles. A moment later, so did he.\begin{center}\rule{3cm}{0.4 pt}\end{center}The replicators were working again. Janeway was taking advantage with her third cup of black coffee in a row. She was sitting in the science department's conference room, waiting for Tom Paris to arrive.``What do you know about this character?" said Janeway.``He is unreliable," said Tuvok. ``His motives are transparently selfish. Chakotay never trusted him. Wisely."``Yet he trusted you," said Janeway.``I am a better liar than Mr. Paris," said Tuvok.The doors hissed open and Paris strolled in. He stutter-stepped when he saw Tuvok.``I guess \textit{Val Jean} is here, too," he said.``Indeed," said Tuvok.``Sit down," said Janeway. ``You're the civilian expert Bujold brought on board?"``Yes, ma'am."``What were you doing in the brig?" said Janeway.``Bujold thought I was yanking her chain, so she sent me there."``Were you?" said Tuvok.``Of course not," said Paris. ``What do I care what happens to Chakotay?"``Did you know anything about this?" said Janeway to Tuvok.``We did not. I find the logic of using Mr. Paris as a guide...interesting."``You don't trust me, either," said Paris.``Your history demonstrates that it is usually unwise to do so."``I should just get ear extensions," said Paris. ``If everybody's going to treat me like a Ferengi, I might as well look like one."Janeway drew a finger across her throat, silencing the budding argument. ``Well, however trustworthy you are or aren't, I'm too shorthanded to have you sitting in the brig wasting oxygen. If I even had a working brig. Do you have any useful skills?"``I'm a great pilot," said Paris.``That's not very helpful right now. What else can you do?"Paris shrugged. ``I was a trustee in the prison hospital for a while."``Good," said Janeway. ``Get down to sickbay, talk to the Doctor about helping him."``Sure," said Paris. ``What's his name?"``He doesn't have one. Dismissed."Paris, blinking and confused, got up slowly and left. Janeway tapped her communicator as soon as he was gone. ``Mr. Gombe, have someone make sure Mr. Paris doesn't get lost on his way to sickbay."``Yes, ma'am."Janeway sighed, pinched her nose, and hung her head. For a minute, maybe two, she zoned out, thought of nothing. She snapped out of it and reached for her coffee. Her hand was shaking slightly; she focused on the muscles in her wrist and arm and it stopped.Tuvok was still in the conference room, watching her the whole time.``What do you want?" snapped Janeway.``Lieutenant Janeway, may I make an observation?"``Feel free," said Janeway.``You are exhausted," said Tuvok.``I'm fine," she said. ``I've pulled plenty of all-nighters before."``With respect," said Tuvok. ``you are not cramming for your Astrogation 401 exam. The stakes are considerably higher, and you are fifteen years older than you were then."Janeway cracked a smile. ``I never took Astro 401," she said.``The point stands," said Tuvok.``Mr. Tuvok, I appreciate your concern, but I have too much work to do. This ship needs a commanding officer. I'll sleep when we get home."``Lieutenant---"``The discussion is closed, Tuvok," said Janeway. ``So was Bujold looking for Chakotay, or for you?''``Me," said Tuvok.``You're sure."``I knew Captain Bujold for many years. I expected her to search for me. I wish she had not.''``Paris doesn't seem to know."``The only way he would know is if Bujold told him. That seems exceedingly unlikely.''``She didn’t tell her own senior officers.'' \textit{She didn’t tell me, anyway.}``Exactly,'' he said.``All right,'' she said. ``If what you say about him is true, the less he knows, the better.'' She tapped her commbadge again. ``Ensign Wildman, I'm ready for you now."The doors hissed open and Ensign Samantha Wildman entered. She was human, of medium height and build, square-faced, blonde, twenty-two. Not yet due for a promotion to lieutenant (j.g.). Practically a baby in diapers, running an entire department in a dire emergency.She hesitated as she approached the table, unsure where to sit. Janeway gestured for her to take a seat next to her. Tuvok shifted so the three of them were clustered at one end, and could all easily see Wildman's \textsc{padd}.``All right," said Janeway. ``Report."``Do you want to hear the report on the station first, or the planet?"``The station," said Janeway.Wildman frowned. ``We don't have much. Our sensors can't penetrate more than a few centimeters beneath the surface. We're still trying to get a handle on the material composition, but nobody seems to know where our quantum spectrometer is and---"``It's on \textsc{ds9}," said Janeway. ``If you can't find it, that's where it is. Bujold left most of our scientific equipment behind because this was supposed to be a quick mission." She took a sip of her coffee and reminded herself there was no point being angry at a dead woman.``Er, right," said Wildman. ``We have learned a few things by examining the surface."``Such as?" said Janeway.``It's really old. And battle damaged. Look." Wildman tapped her \textsc{padd}, calling up a slideshow of visible-light photos of the surface of the station. Each photograph showed obvious battle damage; pits and divots, trenches, faded scorch-marks, hasty repairs. The entire planet-facing hemisphere of the central station was scarred with metal patches and the melted stumps of some kind of support struts.``Any idea who did this to it? The Kazons?"Wildman shook her head. ``This damage is \textit{old}. Look at this picture. See this patch? It obviously melted and re-froze. It looks like a lunar maria. Well, just like a lunar maria, you can tell how old something like this is by counting craters and comparing to the known rate of meteoroid bombardment."``Forgive me," said Tuvok, ``but how could you know that?"``We took a census of the sub-millimeter debris in the inner solar system and estimated based on their orbits. It's not perfect, but we can say pretty confidently that these battle scars were made at least ten thousand years ago. Almost certainly longer. The maximum age is one hundred thousand years."``Assuming it's been here that long," said Janeway. ``For all we know, it could have come from some other solar system; maybe a younger one with a lot more debris. Or it could have spent time in an asteroid belt."Wildman nodded. ``Yes, that's a possibility. I'd like to get a surface sample so we can do an isotope comparison between the local interplanetary medium and the surface deposits on the station. Then we'd know for sure if it's a wanderer."``Send a probe to do it," said Janeway. ``No \textsc{EVA}s anywhere near that thing until we understand it better."``Yes ma'am."``Can we figure out anything else from those battle scars? Any signature left behind by the attackers?"Wildman shook her head. ``If there was one, it decayed a long time ago."``OK. Anything else on the station?"``No ma'am. Not yet."``Fine," said Janeway, not feeling fine at all. ``What about the planet?"Wildman perked up. "\textit{That's} more interesting." She tapped her \textsc{padd}, bringing up a long list of facts and figures about the planet. ``Class \textsc{n} terrestrial; atmospheric composition 96.5\% Carbon dioxide, 3.5\% Nitrogen, 0.015\% Sulfur dioxide, miscellaneous trace gases. Atmospheric pressure 90 bar. Mean surface temperature 735 kelvin. Surface completely obscured by sulfuric acid clouds. One moon, composed of metal-poor silicate rocks, likely formed by an ancient glancing collision with another planetesimal."``Sounds like a typical class \textsc{n}," said Janeway.``That's where it stops being typical, ma'am. We made a radar map of the surface. Look at this." She tapped on the \textsc{padd} and turned it so Janeway could see.Class \textsc{n} planets---like Venus, a typical example---had distinctive surfaces. They had liquid mantles with active convection, like class-\textsc{m} planets, but without oceans to lubricate tectonic plates---impossible at such surface temperatures---the crust was too rigid for tectonics. Instead, the heat and pressure built up in the interior until the crust failed entirely, and the entire planet was resurfaced in a planetary-scale volcanic event. It had happened to Venus in 2330, undoing a century and a half of terraforming efforts. The resurfacing events created a distinctive, easily-identified surface of vast basaltic plains, with a few continent-sized volcanic uplands, riven with cracks and faults, randomly splotched about the planet.This planet did not look like that.Janeway wasn't a geologist by training, but anyone who had ever looked at a topographic map of a class \textsc{m} planet would have recognized these features---oceanic basins with central spreading ridges and subduction trenches along the edges, continental shelves falling off to deep abyssal plains, river valley systems and fan-shaped deltas, upthrust mountains, earthquake faults, glacier scars and glacial lakebeds at high latitudes, even identifiable sedimentary structures. All of it desiccated and baking at temperatures hot enough to melt lead---the high mountains even had deposits of lead oxide ``snow" at their peaks---but very obviously formed by familiar class-\textsc{m} processes.``This is a ruined class-\textsc{m}," said Janeway. ``Not a natural \textsc{n}." Wildman nodded. ``Was it inhabited?"``Yes," said Wildman. ``We've detected concentrations of refined metals, disturbances to the landscape indicative of agriculture and mining, and the ruins of structures."Janeway closed her eyes. Starfleet had discovered worlds like this from time to time---worlds inadvertently ruined by their own inhabitants pushing the climate into greenhouse tipover. Sometimes the species survived in space, living in habitats and asteroids. Sometimes...they didn't. Whoever lived on this planet hadn't.Maybe Wildman had guessed what she was thinking. ``It wasn't their fault, Captain. Look." She played another slideshow on her \textsc{padd}. Radar and subspace images of ruined structures, enhanced by the computer, flipped by. All of them were masonry, heavy, rough, primitive. No flying buttresses, no domes, not even any arches. The styles were subtly different, but most were variations on ``big pile of rocks" like Egyptian or Mayan pyramids, with the most sophisticated structures looking vaguely Egyptian or Minoan; thick stone walls and massive columns. ``The only refined metals we detected were bronze and very little iron. No steels, no aluminum."``The acid in the atmosphere," said Janeway.``It wouldn't have eaten it all away," said Wildman. ``Most of it never reaches the surface. It's so hot down there it disassociates. No culture on this planet got past the iron age. They didn't ruin their world."Janeway steepled her fingers. ``But you wouldn't be bothering with all this buildup if it were natural, would you?" she said.``No ma'am," said Wildman. ``Look." She called up one last picture on the \textsc{padd}. It was a tower, more than a kilometer high. ``It's made of the same stuff as the station. There are a hundred more just like it still standing, and more which have collapsed." She highlighted a ruined structure near its base. Janeway thought it was small, until Wildman zoomed in and a scale indicator appeared. It was an enormous building, set at the nexus of a dozen radial avenues lined with more ruined buildings. ``What do you think that is?"``It looks like a temple," said Janeway. ``Like they worshipped these towers." She turned to Wildman. ``Did the towers have anything to do with what happened to the atmosphere?''``We don't know for sure," said Wildman. ``But given the geological and astronomical evidence, it’s very unlikely the greenhouse tipover happened naturally, and those towers are the only evidence of advanced industrial culture on the surface. How it could have happened, none of us have any idea. I’d like to launch a probe to study one of the towers up close."``Do it," she said.``I should report this to Chakotay," said Tuvok.``Yes, fine," said Janeway.Gombe's voice came over the intercom. ``Bridge to Janeway, he said.``Janeway here."``Ma'am, you'd better come up here. Long range sensors just detected another ship entering the system at warp. He's on his way to the inner system."``Yellow alert," said Janeway. She popped up out of her seat and finished her coffee in one swig. ``Let's go," she said.\begin{center}\rule{3cm}{0.4 pt}\end{center}``Do we have \textit{Val Jean} on the circuit?" said Janeway."\textit{We read you, }Voyager," said Chakotay.``Good. Hail the alien, Mr. Gombe," said Janeway. \textit{Let's hope he has subspace comms}.``Hailing frequencies open," said Gombe. ``Audio only."``This is Captain Kathryn Janeway of the Federation starship \textit{Voyager}. Identify yourself."``\textit{Go away}.''``Unidentified ship---"``\textit{My name is Neelix, my ship is the }Baxial\textit{, and I paid the Kazon-Ogla for salvage rights in this field, so you can just scram. Take it up with them if you don't like it}."Janeway put her hands on her hips and rolled her eyes. She made a ``mute" gesture at Gombe."\textit{Hostile little booger, isn't he}?" said Chakotay.``He hasn't shot at us yet," said Janeway. ``That might pass for hospitality around here." She gestured for Gombe to turn the comms back on. ``Mr. Neelix, we're not interested in jumping your salvage claim. We're a long way from home and we're just looking for some information."``\textit{Tell him you'll pay him}," said Chakotay.``We're willing to pay you for your time," said Janeway.There was another pause.``Captain, he's opened a video channel," said Gombe.``Well by all means," said Janeway, ``put it on screen."Gombe did. The alien on screen was short and stocky, made to look even shorter by an unflattering camera angle. He had a stiff mane on top of his head and spotted skin on his temples. The cockpit of his little ship was strewn with debris. He wore a set of coveralls in lavishly clashing colors. He smiled at the camera, showing a mouth full of pointed teeth.``Greetings," he said. ``What, um, what would you be willing to pay me?"``Well, I doubt our currency is worth anything out here," said Janeway. ``But we'd be happy to barter supplies or services."Chakotay, who was on the viewscreen in an inset, mouthed ``Services?"Neelix seemed to think about that for a minute. Finally, he said, ``How much water can you spare?"\begin{center}\rule{3cm}{0.4 pt}\end{center}``Ahhhhhhhh," said Neelix, as he slid into the bathtub of near-scalding water. The bathroom was thick with steam. Janeway, Tuvok, and Chakotay looked on. Apparently, Neelix didn't value his privacy much, or had a different concept of it from the rest of them.He also stank like a monkey's cage. The computer automatically dispensed soap into the water.``Gotta conserve water on my little ship," said Neelix. ``Don't even have a shower. Ahhh...this is nice, forgot how nice a hot bath was." He suddenly looked self-conscious. ``You know, my people are actually very hygenic. But when it's just me for weeks and weeks, there's no reason to waste water on a bath. That's what stations are for."``And your people are...?" said Chakotay.``Talaxians, native sof Talaxia. About seven hundred light years spinward from here. I'm from a moon called Rinax...used to be a nice place."``Used to?" said Janeway.Neelix appeared somber for a moment. ``Yeah. There was a...well, there was a big war. We, um, lost." Then he shook it off, and his voice and body language became upbeat again. ``But, no use dwelling on the past, right? So where are you fine folks from?"``We're from the United Federation of Planets," said Janeway. ``Mr. Chakotay and I are humans, from a planet called Earth. Mr. Tuvok is from the planet Vulcan."``If you're from Earth," said Neelix, ``why aren't you called Earthians?"Janeway and Chekotay looked at each other and shrugged. ``It doesn't sound very good in our native language," said Chakotay, which Janeway figured was as good an answer as any.``I see," said Neelix. ``So where is this Federation of yours?"``About seventy-five thousand light years from here," said Janeway.``Oooh, that's quite a ways. We don't see many from that far off."``You mean there's been more like us?" said Chakotay.``Oh, yes! It was one or two every year, for years. Lately, though, it's been one or two a month. Nobody knows why the Caretaker does it. Usually it grabs them from somewhere nearby, but once in a while it reaches way out and snags somebody like you."``The Caretaker? Who is that? Does he live on that station?" said Chakotay.``As far as anybody knows, he \textit{is} the station," said Neelix. ``Nobody knows why he does it. It's been good business for the Kazons, though. And those of us living off the Kazons' table scraps." He suddenly looked embarrassed. ``Not that, you know, it isn't terrible for the poor people who get sucked out here."``Why is he called the `Caretaker'? What's he taking care of?"``Nobody knows that either," he said. ``If you ask me, there's something on the planet. But that's just a guess."``Has it ever taken another Federation starship?" said Janeway.``I don't know," said Neelix. ``Usually we only find out about the ones Jal Jabin catches."``Who is he?" said Janeway. ``Who are the Kazons?"``Jal Jabin? He's the Maje---boss---of this system. He reports directly to First Maje Jal Razik. Razik is the boss of the entire Ogla sect, and Jal Jabin’s cousin, which is why Jabin got the right to this system. The Ogla are the biggest Kazon sect, and they own everything from here to about fifty light years spinward."``How many more sects are there?" said Chakotay.``There are eighteen big sects," said Neelix. ``Or nineteen. Sixteen. It's hard to remember; they're always marrying each other and having civil wars and the like. And then there are hundreds of smaller sects. Some of them are just one extended family with one ship. They fight each other all the time, unless they have someone else to fight." He eyed Janeway, Chakotay, and Tuvok. ``People like you. Jal Jabin has five hundred kills, if you believe him."``Does anybody ever defeat him?" said Chakotay.``Sometimes," said Neelix. ``Most people just try to run away, but sometimes they fight. There was one species---a `Jam Haddar'---which deliberately rammed their ship into his personabl battleship, \textit{Predator}. It took them almost a year to repair it, and then you showed up and blew it up." He looked around. ``How did you fight him off?"``We trans---" started Janeway.``Our weapons are far more sophisticated than theirs," said Chakotay. ``We wrecked \textit{Predator} in one shot."Janeway expected Neelix to be impressed. And he was...to an extent. But he looked pensive, too. ``Captain, you might not want to stay here too long," he said. ``Jal Jabin doesn't like sharing his loot, but if the Ogla think you're a threat, they'll come back with more ships."``That's their mistake, then," said Chakotay, but Janeway could hear a whisper of uncertainty in his voice, too.``We'd like to get out of here before the Kazons come back," said Janeway. ``How do you know the Caretaker's name?"``Well, I know because it told the Kazons."``It communicated with them?" said Janeway. Her heart started pounding. For the first time, they had something to communicate with. If you could communicate with it, you could negotiate with it.Chakotay and Tuvok looked to be having the same thoughts. Neelix tried to let them down easy. ``It was only once, years ago. It told them they could come in the system, but they couldn't build a base here and they weren't allowed to try to board the station."``Did they ever try?" said Chakotay.``Well, they could never find a way into the station," said Neelix. ``But they tried building a space station, yes. In orbit of this planet."``What happened to it?" said Janeway.``The Caretaker...moved it."``Moved it where?"Neelix started to fidget. ``Um...the sun," he said.``The Caretaker threw the station in orbit of the sun?" said Janeway.``No," said Neelix. ``It threw the station \textit{into} the sun."Janeway, Tuvok, and Chakotay all looked at each other, none of them able to think of anything useful to say.The tension was broken by the intercom. "\textit{Engineering to Captain Janeway}."Janeway didn't recognize the voice. ``This is Janeway. Who is this?""\textit{This is Ensign Vorick, ma'am. Lieutenant Carey and Lieutenant Rodriguez are sleeping until 0400.}"``I didn't order them...never mind. What do you need, Mr. Vorick?""\textit{There is an electrical fault in grid 11, subsection C. It is a simple repair, but in order to make it safely, we must shut down several non-essential systems for fifteen minutes, including the internal communication network.}"``Fine," said Janeway. ``Make it fast."``Yes, ma'am."Vorick made a shipwide announcement, and then the comms went dead. Janeway tested it by tapping her commbadge; it only mustered a strangled ``Error" chirp.Neelix started climbing out of the bathtub. Alarmed, Janeway and Chakotay turned away; Tuvok tossed him a towel. ``Well," said Neelix. ``It would probably be best if I got back to my ship. You're lovely people, but all that scrap isn't going to sort itself. If, um, you feel like throwing in a little extra payment, that'd be most appreciated."``Wait," said Janeway. ``Has the Caretaker ever sent anybody home?"``No," said Neelix. ``The only way home is the long way."\begin{center}\rule{3cm}{0.4 pt}\end{center}``Well, what do you think?" said Janeway. She, Chakotay, and Tuvok sat alone in the science department conference room. Janeway had another coffee. Her stomach was churning and she had to piss every fifteen minutes, but she kept chugging it down.``Assuming he was telling the whole truth," said Tuvok, ``We may not have many options."``The whole truth?" said Chakotay. ``Do you think he was lying?"``That possibility cannot be ruled out," said Tuvok. ``However, I find it more likely that he simply doesn't know everything the Kazons do."``You're saying we have to talk to the Kazons," said Janeway.``That may be necessary," said Tuvok.``Fantastic," said Janeway. ``I'm sure they'll be in the mood to help us."``Maybe," said Chakotay. ``That depends on if we can offer them something they want."``Such as?" said Janeway.Chakotay waved his arm. ``Transporters. Subspace sensors. Phasers. Replicators. Better shields, better computers. Holodecks. Take your pick."``Absolutely not," said Janeway. ``The Prime Directive forbids it."``They're warp capable," said Chakotay. ``The Prime Directive doesn't apply."``That's bullshit and you know it," said Janeway. ``You used to be a Starfleet officer; you know the Prime Directive has shades of meaning. We can make contact with warp-capable civilizations. We still can't interfere with their development by giving them technology centuries more advanced than their own. And then there's the follow-on effect: giving them advanced technology would absolutely upset the balance of power here, interfering with the development of hundreds, possibly thousands of cultures. And finally, I don't know if you noticed, but you just proposed giving sensitive Federation technology to a species which fired on a Federation starship without warning. All in the hope they know something about the Caretaker that could get us home? No, absolutely not."Chakotay was clearly not a man used to being told his ideas were ``bullshit". ``Captain Janeway, you're right about exactly one thing: I \textit{used} to be a Starfleet officer. I'm not anymore, and \textit{Val Jean} isn't a Federation starship. I put about as much stock in the Federation's precious principles as the Federation council did when it abandoned my world to the Cardassians. If you're not willing to set aside the Prime Directive for the sake of our two crews, I'll go to them myself."``The crew of this ship took an oath to uphold the Prime Directive, even if it costs us our lives," said Janeway.``Mine didn't," said Chakotay. He stood up. ``You can't stop me. I won't lie: I'd rather do this together, but if I have to go it alone, I will."Janeway stood too. She didn't know what she was even going to say. She never got a chance to figure it out.The doors hissed open. Tom Paris walked in, wearing a borrowed blue uniform and holding a medical tricorder. ``Captain, the Doctor wanted to remind you that he needs to examine your shoulder again, but the comms aren't working, so he sent...me." He trailed off. He was looking directly at Chakotay.Chakotay was looking directly back at him. His mouth was hanging open.``So that's how \textit{Voyager} found us," said Chakotay. ``You son of a bitch, how much did they offer you to sell out the Maquis?"``I don't know. How much did they offer you to steal my ship and dump me in Starfleet's lap?"``Fuck you," said Chakotay. ``I won that election fair and square. Maybe if you weren't a worthless fuckup in command, your crew wouldn't have voted for me. Even your girlfriend wanted me, not you."Paris wound up and threw the tricorder at Chakotary's head. Chakotay ducked, vaulted the table, and charged.\begin{center}\rule{3cm}{0.4 pt}\end{center}Paris had forgotten Chakotay's hobby was boxing. The big man drilled Paris with a right hook to the temple that dropped him to the deck. Chakotay hauled Paris back to his feet and delivered a body-blow to the solar plexus. Paris staggered backwards, breathless, dazed, and reeling, his vision blurred. Chakotay was winding up for another punch to the head.Suddenly, Tuvok grabbed Chakotay's arm. Chakotay wheeled on the Vulcan. ``What the hell are you doing?" he said.``Captain---" started Tuvok, but he didn't finish because Paris took advantage with an off-balance swat at Chakotay's left ear that miraculously connected. Chakotay shook off Tuvok and turned on Paris, knocking him back to the deck.``You're really going to get it now," said Chakotay. He drew back his leg, ready to attempt a penalty kick with Paris's head. Paris braced himself, wondering if the Doctor would be able to get the dent out.``Chakotay!" cried Janeway. There was a whining hiss---a phaser---and Chakotay grunted and crumpled to the floor, crashing on top of Paris. It hurt, but it hurt a lot less than a kick in the face. Paris lay there for a moment, trying to recover his breath, and finally crawled out from under Chakotay. He sat up and looked around, expecting to see Tuvok holding the weapon.He wasn't. ``Get him to sickbay," said Janeway. She set the phaser down on the table gingerly, like it would explode. She half-sat, half-fell back into her chair. ``Fuck me," she said.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textbf{Kazon-Ogla Staging Area}\noindent\textbf{3.4 Light Years from Ocampa}\\\textit{Predator} limped into his dock like a dying old man. Maje Jal Jabin's personal belongings had been evaporated by gamma ray flux, so when he stepped through the gangway, the only possessions he had left were his uniform and his gun. He didn't know how long until they took the former and shot him with the latter.Maybe not long at all. A man was waiting for him at the end of the gangway, wearing the uniform of the First Maje's office. ``Maje Jabin," he said. ``Follow me."Jabin may have been a dead man walking, but as a Maje he still had rights. ``Who demands it?" he said.The man from the First Maje's office drew up straight. He was half a head shorter than Jabin and, judging by his skull ridges, of an inferior caste, not even important enough to be allowed to serve on a starship. But he wore the herald of the First Maje on his breast, and that gave him the right to ignore all proper social conventions. If Jabin laid a hand on him, Jabin would lose it, and the officious peasant knew it. ``The First Maje demands it, oh great Maje Jabin. He wishes to inquire into the condition of his ship."Jabin briefly considered shooting the peasant and then himself, just for the satisfaction of taking somebody with him while avoiding a drawn-out execution.``If the First Maje wants me, then I am at his service," said Jabin.He was led through a maze of cramped passageways towards the center of the station. The design of the place was ad hoc, with hundreds of additions over the years and no logical sense to the layout. Along the way, they passed a window looking down into an internal hangar, where the wrecks of some of Jabin's earlier prizes floated. \textit{I made a lot of money for the Ogla sect}, thought Jabin. \textit{Maybe that will buy me another chance.} It was the best hope he had.They walked deeper into the station, finally found a horivator bank (Jabin suppressed a snarl as the peasant got into the warrior caste car with him). It took them to the station's multi-level central promenade. Like the promenade of every Kazon station, it was crowded with civilians, the camp followers of the warrior caste who ruled Kazon society. The decks reserved for warriors were less crowded (and cleaner and better maintained), but there were still many, many Kazons. \textit{The First Maje brought his personal fleet}, thought Jabin. Word of the disaster that had befallen Predator had spread fast.The First Maje's offices were at the very top deck, above even the station's control room and Jabin's own station quarters (rarely used). He had an office at every station in Kazon territory, attended usually by mid-ranking functionaries, ensuring the First Maje got his cut of every crown that passed through every Ogla's hand. Now they were full with the First Maje's entourage. The peasant passed him off to a warrior-adjutant. ``Come with me," he said.The First Maje's personal office was a throne room. First Maje Jal Razik himself, bald and immensely fat, clothed in fine fabrics of deep maroon and orange-gold, sat on a throne of ornate hand-wrought ironwork covered in gold leaf. The walls and ceiling were marble trimmed with gold. Courtiers and courtesans lounged around the room, eating, drinking, and smoking, pointing at Jabin and quietly snickering. Every last one of them appeared to be addled on drugs. Jabin approached the throne and prostrated himself before it.With a grunt, the First Maje managed to lever himself out of his throne. He wheezed his way off the dais and plodded down the carpeted aisle to Jabin. Jabin dared not move.``Rise, Maje Jabin," said Razik. Jabin did, taking care to avert his eyes from looking directly at Razik's face.``Look at me," said Razik. He reached forward with one fat hand and turned Jabin's head until the two men were looking eye-to-eye. Razik and Jabin stared at each other.``Rejoice!" said Razik. ``Our brother Jal Jabin lives!" And then he grabbed Jabin and embraced him in a crushing bear hug. The courtiers---looking confused and disappointed, but knowing what was good for them---stood and dutifully applauded. Jabin felt his legs go limp with relief. The First Maje had chosen to spare him.``Walk with me, brother," said Razik.``I obey," said Jabin. They walked together---Razik made a show of leaning on Jabin for support---to Razik's private office off the throne room. It was the opposite of the throne room: small and comfortable, decorated with traditional Ogla art and photographs of the First Maje's grandchildren. The First Maje offered Jabin a seat, then collapsed into his own chair---one which had much more padding than the iron throne.``Do you remember, my friend, when we were both boys?" said Razik. ``And our grandfather led the Kazon-Ogla to glory without needing any of this rubbish around them?"``I do, First Maje."``I worry that we've lost our way," said Razik. He shook his head, sending his chins wobbling in three different directions. ``But that is not why I am here. I am truly glad you're alive, my friend."``I'm not," said Jabin. ``I lost nine hundred warriors. For my incompetence, I should serving them in Paradise for ten thousand years.''``I have seen the video and read the report, Maje Jabin. It was not your fault. I have forgiven you; so have your fallen warriors, and so should you."``I am not sure I'm ready."``This is why I have always liked you," said Razik. ``You take responsibility. Too many so-called Majes seek only glory; never blame." He leaned back in his seat. ``So," he said. ``If you will not forgive yourself, what is your plan for redemption?"``It's time we destroyed the Caretaker," said Jabin.Razik leaned forward, resting his fat face in his upturned hands. ``You've gained more than any of us from the Caretaker," he said. This was a lie. Between his share of the loot, the lease he was charging Jabin for a battleship and a starbase, and all the taxes he was collecting on the supplies needed to run the operation, Razik was making more from the Caretaker than anyone. But if the Caretaker were destroyed, Razik had his fingers in many other pies, while Jabin would be out of a job.``I know," said Jabin. ``But \textit{Predator} has twice been nearly destroyed by aliens twice now. What if it brings us more of these `Federations' and their teleporting bombs? What if it brings us more of those lunatic `Jem'Hadar'? \textit{What if it brings us something worse?}"``We are powerful, Jal Jabin," said Razik. ``What we lack in technology, we make up in numbers. The Vidiians are far more advanced than us, and we've held them at bay for decades. Talaxians, Hakkonians, the bloody \textit{Trabe}; we have triumped over and over against superior technology and desperate odds. The Caretaker pulls in ships one at a time. What could one ship do?"``It's not one ship," said Jabin. ``\textit{Val Jean} arrived three days ago. It slipped away from me."``I know," said Razik. ``It's happened before."``Yes, but most of the time, they run away as fast as they can. \textit{Val Jean} stayed, and now it's working with \textit{Voyager}. Don't you see? This could be the beginning of an invasion."``Or they could be allies of desperation," said Razik. ``Jal Jabin, are you certain your concern is genuine, or do you just want revenge on the Caretaker for what happened to your crew?"Jabin honestly didn't know. ``Maybe both," he admitted.``First things first," said Razik. ``Our priority now is those `Federations'. If this \textit{is} the beginning of an invasion, we need to smash it immediately, before they establish a beachhead."``I have dispatched scouts to Ocampa," said Jabin.Razik shook his head. ``Skulking in the Oort Cloud with passive sensors won't do," he said. ``We need better intelligence. Would you agree that it's likely \textit{Voyager} and \textit{Val Jean} have subspace sensors on board?"``Given how \textit{Val Jean} was able to drop exactly on top of us only a few minutes after we arrived at Ocampa, that seems certain," said Jabin.``Then we need our own real-time \textsc{ftl} intelligence. We will move a Spyglass into Ocampa's Kuiper belt, along with a fleet to protect it."``They'll see us," said Jabin.``They have two ships. They are powerful, but they're not gods."``Those teleporting bombs..." said Jabin.Razik grinned. ``My engineers have analyzed your data," he said. ``It was a trick, Maje Jabin. Just a simple trick. And simple to defeat. The next time we fight, it will be on our terms."\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Voyager}}\\Janeway stormed down the passageway on her way to the auxiliary bridge. Tuvok followed behind her.``That was unwise, Lieutenant," said Tuvok.Janeway stopped, spun, and got in Tuvok's face. ``I wouldn't have had to do anything if you hadn't been just standing there! And from now on, on my ship, you will address me as Captain Janeway."``As you wish, Captain," said Tuvok. His calm voice was only angering her further. In her entire Starfleet career, she had never fired a phaser at anyone. Adrenaline sloshed through her veins, winding her up, fraying her already disintegrating nerves. ``Captain, I admit, I should have acted faster. However---"``You've been Chakotay's lapdog for so long that you couldn't bring yourself to nerve pinch him even when he was beating a civilian to death," snarled Janeway. She kicked a nearby wall; the panel fell off. ``Piece of shit fucking ship!" she said. She pointed at Tuvok. ``Chakotay's waking up out of stun in twenty minutes. As soon as he does, place him under arrest."``I cannot do that," said Tuvok.``Why the hell not?''``Because doing so would compromise my mission. I am sorry, captain.''``What mission? Your mission is over; we know where Chakotay is, and he’s coming back to the Federation with us.''``My mission is not over until my superiors say it is over,'' said Tuvok.``This is my ship—````And you have no authority to contradict my orders on matters relegated to ongoing Starfleet Intelligence operations. Again, I am sorry, Captain.''``Fine,'' snarled Janeway, too exhausted to argue. ``Can I have him held for attempted murder, or do you need to consult with Starfleet Intelligence for that, too?''``He committed an assault on board your ship,'' said Tuvok. ``You would be within your rights. His crew will not take it well, however.''``No shit. Unfortunately the two of you didn’t leave me many options.'' She tapped her commbadge and was all the way through ``Janeway to security'' when she realized it had error chirped. ``Oh for fuck's sake. Tuvok, make yourself useful and go down to Main Engineering. Tell Vorick we need comms back right away.''``As you wish," he said, and he left. Satisfied, Janeway stomped off.Halfway to the bridge, she had to stop and lean against a door jamb until she stopped shaking. \textit{What the hell is wrong with me?} she thought. She knew the answer: she was scared and exhausted and strung out and lost on the other side of the galaxy. But she had to stay awake, had to stay in command. She'd sleep when they got home.She hurried to the bridge. When she go there, the first thing she did was corral a security rating. ``Grab a team, go to the conference room, and drag Chakotay to the first available vacant cabin and lock him in.''``What's going on, Captain?" said Gombe. He was on his second eight hour shift in the last day. Beside him was a petty officer from the maintenance department, who'd been drafted as a backup tactical officer trainee.``I just arrested Chakotay," said Janeway, taking her seat. ``As soon as the Maquis find out, there's going to be trouble."``I'll say," said Gombe."\textit{Vorick to bridge. I have restored the internal communications system}."``Thank you, Ensign," said Janeway. ``Janeway to security.""\textit{Security here.}"``Status of Chakotay?""\textit{We took him to deck five, to a vacant cabin. He’s coming around, but he’s still groggy.}"``Lock the door and a guard posted at all times.""\textit{Yes, ma'am.}"Janeway took a deep breath. ``Mr. Gombe, hail \textit{Val Jean}. Yellow alert, shields up. Somebody wake Carey and Rodriguez."\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Val Jean}}\\``She did what?" said Torres.``She arrested him," said Seska for the second time. ``For assault on some civilian."``That's bullshit!" said Torres. ``They're arresting him for being one of us."``Calm down," said Seska.``Tuvok's over there," said Bendera. ``Can he rescue Chakotay?"``I haven't been able to raise Tuvok at all," said Seska. ``They might be holding him too."B'Elana snarled and slapped her hand on a console. ``Then we have to spring them both. Find them on sensors and beam them both out."``Don't you think I already tried that?" said Seska. ``Their shields are up."Torres sprung to the tactical console. ``They're only at fifty percent. The idiots still don't have a working warp core. We can punch a hole through, and then get Chakotay and Tuvok," said Torres.``Are you crazy?" said Seska. ``Even with half-shields and half-phasers, they can squash us flat. Photon torpedoes alone---"``We'll fly in close," said Mohommad. ``Get in under their guns. Photorps don't have the turning radius to hit us inside a kilometer if we're moving fast enough, and even if they did, they'd do as much damage to themselves as us."``Have you forgotten that the only way we're getting home is with \textit{Voyager}'s help?" said Bendera.``They probably know how to get back already!" said Torres. ``They got what they came for, and now Janeway's going to take him back to the Federation and leave us stranded here!"``That's ridiculous! Why haven't they left yet, then?"``How should I know?" said Torres. ``They're probably jerking off taking pictures for science or some stupid shit. Think about it. Not even Starfleet is stupid enough to sit here in hostile space with a dead warp core. The only explanation is that they must know how to get back already. Look, Janeway is a blueshirt. A \textit{science} officer. She might not know shit about commanding a starship, but you know those Starfleet eggheads love figuring out how ancient alien bullshit works."``Maybe it wasn't even an accident that \textit{Voyager} followed us out here. Maybe they already knew about the Caretaker," said Mohommad. ``This whole thing might have been a trap."``Okay, enough conspiracy crap," said Seska. ``There's no activity from \textit{Voyager} or the Caretaker."``How do we know what activity from the Caretaker looks like?" said Torres. ``We've never seen it send anyone back."``It has to do something!" snapped Seska.``Seska’s right, we shouldn’t panic,'' said Bendera. ``We should hail Janeway and—''``We're getting them back!" said Torres. ``Who's with me?"Hands, claws, and tentacles went up around the bridge. Only Seska and Bendera kept their hands down.``This is suicidally stupid," said Seska.``Either you lead us or I do," said Torres.``Over my dead body," said Seska, dropping into the captain's chair. ``Shields up, phasers online. Kurt, take the weapons console. Mohommad, get us close." \textit{Prophets protect me}, she thought.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent``They've raised shields," said Gombe. ``Locking weapons."\textit{Okay, stay calm. Remember the bridge officer's exam: a bad decision is better than no decision.} ``Red alert. Engineering, do we have impulse back online yet?"``\textit{Yes ma'am, but only at thirty percent}."``They're closing in on us," said Gombe.``Evasive maneuvers. Don't let them get too close," said Janeway.For the first time in more than a day, \textit{Voyager}'s massive sublight engines rumbled to life. Janeway felt the vibrations through her seat.``They're still closing," said Gombe. ``They are faster and more maneuverable than we are."\textit{Of course they are}, she thought. \textit{30\% impulse, we're practically immobile compared to them}. She realized she was trying to postpone the inevitable. She was going to have to shoot their only allies.``Lock phasers," said Janeway. ``Target their weapons systems."``Yes ma'am."On the viewscreen, \textit{Val Jean} closed in on them.``They're firing phasers!" said Gombe.\textit{Val Jean} blasted \textit{Voyager}'s ventral shields. Janeway felt the vibrations in her chair.``Ventral shields down to 25\%," said Gombe. ``Bleedthrough damage to deck 15. Main deflector is offline. Captain, I can't lock their phaser power distributor; it’s too small and they’re moving too fast."``What about their engines?''``In their state, that would risk destroying their entire ship.''Janeway had a sudden insight. ``Can you knock out their sensors?"Beat. ``Yes, ma'am."``Do it!"\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent``\textit{Voyager} is firing!"\textit{Val Jean} shook with the impact. ``Their phasers are at half power," said Bendera. ``Still crushing our shields."``Mohommad, come about and take us over their dorsal side," said Seska. ``We need to hit their impulse reactors if we want to have any chance."``Yes ma'am," said Mohommad. \textit{Val Jean} cut her engines, pivoted around, and leapt to full power.``Target their impulse engines!" said Seska. ``Fire!"\textit{Val Jean} blasted \textit{Voyager}'s shields, directly at the weak spot where hot propellant from the engines passed through the shields. They got one clean hit directly on the starboard impulse engine, which flared and died. All the lights went off on \textit{Voyager}.``Got them!" said Mohommad. ``Their shields are---"\textit{Voyager}'s lights came back on. \textit{Val Jean} took a phaser burst right in the face. The crew was thrown out of their seats.``Report!" shouted Seska.``They punched right through our forward shields!" said Bendera. ``They knocked out the main and the backup sensor array. I'm totally blind. I can't even get the external cameras to respond."``Mohommad, get us out of here!" said Seska.``I'm blind too!"``For the love of the Prophets, we're in \textit{space}! Pick a direction, go to warp, and try not to crash into the sun!"\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent ``They're warping off," said Gombe. ``It looks like they picked a random direction off the plane of the ecliptic."Janeway let her breath out with a shudder. For an instant, she'd experienced something like pure, raw joy. Victory! Ancient primate instincts sweeping a lifetime of civilization aside in one burst.But that passed, and she was left with the knowledge that her ship was now more broken than it had been before.``Casualty report," said Janeway.``None," said Gombe. ``But engineering is reporting the starboard impulse reactor is completely destroyed and the backup badly damaged and forced into shutdown mode. We've lost half our remaining power generation and propulsion."``How long until they can get the backup online?" said Janeway.``Mr. Carey is reporting six weeks," said Gombe.Janeway hung her head. \textit{I hope sparing the fucking Maquis was worth it}, she thought. \textit{Now we're even deeper in it.}And then it got worse.``Captain, I have new contacts on subspace sensors," said Gombe. ``Sixteen Kazon vessels have left warp in the system Kuiper belt."\textit{Oh, shit}, thought Janeway.\chapter*{Part III}
\textit{\textbf{Voyager}}\\``Mr. Gombe, can you identify the ship types?" said Janeway.``Fourteen are identical in configuration to \textit{Predator}. One appears to be \textit{Predator} itself. The last is substantially larger, and appears to be some kind of surveillance or electronic warfare ship."``They're looking for us," said Janeway. ``Janeway to engineering: what's the status of our defensive systems?"``\textit{Not good}," said Carey. ``\textit{I can get you thirty percent shields and phasers. Photon torpedoes are ready.}"``We could hold them at bay with photon torpedoes," said Gombe. ``Three full-yield shots should be enough to disable one battleship."``What's our remaining loadout?" said Janeway.Gombe grimaced. ``Thirty, captain."``What will phasers do to their armor at 33\%?"``Ruin the paint," said Gombe.``And the engines don't work," said Janeway. \textit{We can't fight, and we can't run}. She looked up at the viewscreen. Planet Hell, the ugly yellow ball, was floating serenely, silent and abandoned, as it had been for ten millennia.``Engineering, this is Janeway. How long could our shields hold up in the planet's atmosphere?"``\textit{What altitude?}"``Zero, Mr. Carey."\begin{center}\rule{3cm}{0.4 pt}\end{center}\textbf{Main Engineering}\textit{Has she gone crazy?} thought Carey. ``Twelve hours, but that's not the biggest problem. The heat dissipation system is down, so we can't dump our waste heat into subspace, and the backup system won't be able to dump it into the environment. Even if the shields could block out every bit of heat from the air and ground---and they can't---we'll be roasting in half that time. And if the shields fail, even for an instant, we'll get crushed like a bug."``\textit{How fast can you get the warp drive online?}"``Six hours, minimum," said Carey.``\textit{Then we have no choice. Prepare the ship for landing. Do whatever you have to do to reinforce the shields and ensure they stay up no matter what. You have five minutes.}"``Five minutes!" said Carey. ``Captain, you have no idea---"``\textit{Five minutes, then we're taking this ship into the atmosphere whether you're ready or not! Janeway out.}"Rodriguez stared at Carey. ``What?" snapped Carey.``What are you going to do?" said Rodriguez.``What do you think I'm going to do? Reroute all available power to the shield generators, and put every backup generator and battery we have on standby. Start shutting down every extraneous system; we need to save every joule of waste heat we can."``Yes sir," said Rodriguez. Beat. ``She's going to get us all killed," he said.``Not if I have anything to say about it," said Carey.\begin{center}\rule{3cm}{0.4 pt}\end{center}``Captain, I'm detecting a subspace particle beam coming from a point source in the Kuiper belt," said Ensign Wildman, working at the bridge's makeshift Science station. ``It looks like some kind of crude subspace sensor."``That e-war ship," said Janeway. ``It has to be from there. We need to take it out."``It's guarded by fifteen Kazon battleships," said Gombe. ``And we can't reach it."``We can't, but the aeroshuttle can," said Janeway. She stood up. ``Mr. Gombe, get a pilot, an engineer, a transporter operator, and as many antimatter bottles as you can carry. Get down to the aeroshuttle, start prepping it for launch. Mr Kim, blue alert. We're landing in Hell."\begin{center}\rule{3cm}{0.4 pt}\end{center}\textit{Voyager} descended into Planet Hell's atmosphere. They were already through the sulfuric acid clouds and could see, through heat shimmers, the ruined surface.``\textit{We only have ten more minutes of cruising before we have to either land or return to space}," warned Carey.``Mr. Gombe, are you ready?" said Janeway.``\textit{Yes ma'am. Aeroshuttle ready for launch in two minutes.}"``Mr. Gombe, does the shuttle have a name?" said Janeway suddenly. She'd heard sending a ship without a name into battle was bad luck. She'd never believed it, but now she needed all the luck she could get.``\textit{No ma'am}."Janeway thrummed her fingers on her armrest. ``How does \textit{Earhart} sound?" said Janeway.``\textit{I like it}," said Gombe.``We'll give her a proper christening when you get back," said Janeway. She stood up and, fighting the bucking of the ship as it pushed through the thick air, walked to Wildman's science station.``We need to find a landing spot now," she said.``I've got one," said Wildman. ``Thirty kilometers north-northeast, there's an old submarine canyon. It's deep enough the Kazons would have to be almost directly overhead to see us, and it's less than a hundred kilometers from one of those towers. Hopefully our magnetic signature will be lost in the background."``It's the best chance we've got," said Janeway. ``Helm, take us down."``\textit{Bridge, this is }Earhart\textit{. Pre-launch sequence complete; we are ready for launch.}"``Release the docking clamps," said Janeway. ``\textit{Earhart}, don't ignite your warp core until you've cleared the atmosphere. We don't want to give the Kazons any clue we're down here."``\textit{Yes ma'am}," said Gombe.``Good luck and good hunting, \textit{Earhart}," said Janeway.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textbf{Kazon battleship \textit{Wrath}}\\``Nothing," said Jabin, reading the display. ``I thought I saw something for a moment in orbit of Ocampa, but now it’s gone."``What of \textit{Val Jean}?" said Razik. Wrath was his flagship, and he maintained a throne on its bridge.``It's in an eccentric orbit of the star, six AUs out and well above the plane of the ecliptic."``Is \textit{Voyager} still on visual sensors?"``Yes. Right in the same place \textit{Predator} found them. But those images are five hours old. If they restarted their warp drive, they could be anywhere by now, out of range of the Spyglass."``None of our observation stations have detected \textit{Voyager}," said Razik.``I think we should consider the possibility our observation stations \textit{couldn't} detect \textit{Voyager}," said Jabin.``Perhaps," said Razik.``We can send the scouts sunward into \textit{Voyager}'s light cone. We can at least find out if they're still here."``No. Not yet. If \textit{Voyager} is still here, it'll see them coming before they see it. There's safety in numbers for us."``I obey, First Maje," said Jabin. And then: ``I have heard the Halkonnians have subspace sensors which can detect material composition, not just mass. It would be nice to have one of those." \textit{Then I’d know if that ghost I saw was made of metal.}``Why steal Halkonnian junk when we can steal from the Federation?" said Razik.``\textit{Voyager} will fight to the death," said Jabin. ``They'll leave nothing of themselves to steal except scrap and ashes."``Only if we are careless," said Razik.\textit{What the fuck does that mean?} thought Jabin. He looked the First Maje over when Razik's attention was diverted. He was starting to suspect Razik's motives for personally commanding the revenge fleet were about more than just honor.``We can't afford to go easy on \textit{Voyager} out of greed," said Jabin.``And we shouldn't waste an opportunity out of spite," said Razik. His tone had gone cold. Jabin changed the subject.``What should we do about \textit{Val Jean}?" said Jabin. ``They're undoubtedly observing us on behalf of \textit{Voyager}."``We'll never catch them with a battleship," said Razik. ``And they outgun our scouts. Leave them alone for now. When we locate \textit{Voyager}, \textit{Val Jean} will be forced to assist, and then we'll engage them both on our terms."\begin{center}\rule{3cm}{0.4 pt}\end{center}\textit{\textbf{Earhart}}Lieutenant Obayana Gombe glanced at the crate full of antimatter bottles and tried to make the sour feeling in the pit of his stomach go away.``We've cleared the atmosphere, sir," said Ensign Baytart, \textit{Voyager}'s senior surviving helmsman, now part of \textit{Earhart}'s five-man crew.Gombe toggled the communicator. ``We're ready, captain," he said.``Good," said Janeway. ``Is the relay link operating?" Her image and voice was staticky, with weird pops and whistles in the background.``The link is working, but your signal is coming in poorly," said Gombe.``There's an electrical storm nearby causing interference," said Janeway. ``Welcome to the wonderful world of radio. Unfortunately, we can't risk a subspace transmission. Make sure you keep close to us. If you wander too far, lightspeed lag will start causing problems, too."``Understood, Captain," said Gombe, after relaying Janeway's last order to Baytart. ``Everything is ready here."``Well," said Janeway. ``No time like the present. Hail the Kazon."\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Wrath}}\\``Lord Razik, we are being hailed," said Wrath's communications operator. He turned to look at the First Maje directly. ``It is Janeway."``Well by all means," said Razik, ``greet her."``The signal is audio and visual," said the operator. ``The video format is new to me, but...it looks like it has its own decoding instructions built into signal." The operator, who had to be a certified electrical engineer to serve on the First Maje's ship, was plainly impressed. ``Stand by."``These Federations are very clever, aren't they, Maje Jabin?" said Razik.``Too clever by half," said Jabin.A picture appeared on the central viewscreen, of a blue starfield encircled by two branches of some sort. ``I have the signal, Lord Razik," said the comms operator.The stars-and-branches card disappeared, replaced by an ashen-skinned Kazonoid sitting in what looked like a starship's control room. His---her?---forehead was smooth and his hair seemed to be composed of straight strands wrapped tightly about his head. He wore a simple blue tunic with a gold badge and small metallic pips on his collar.The alien smiled. ``I am Captain Kathryn Janeway of the Federation starship \textit{Voyager}. With whom do I have the pleasure of conversing?"\textit{Female, then}, thought Jabin. He could barely contain his revulsion. The alien looked like a giant, talking Kazon fetus. Other aliens in the background shared the same appearance, with minor differences. \textit{Maybe Janeway is an albino}, he thought, noticing a dark skinned alien sitting beside her. He looked away; the smooth foreheads were making his skin crawl.``I am Jal Razik, First Maje of the Kazon Ogla. It is my distinct pleasure to welcome you to the Ocampa system."``I believe Jal Jabin already formally welcomed us to Kazon space," said Janeway.``Oh dear, yes," said Razik. ``You have caused us quite a bit of trouble, Captain Janeway."Janeway's signal was poor. Hisses, pops, and whines contaminated the audio, and occasionally the colors of the image would invert or the picture would 'ghost'. Jabin quietly slipped over the comms operator.``Can't you clean that up?" he said.``I'm trying," said the operator. ``It's coming from their end, though."Jabin scowled. ``What's the signal source?"``It's coming from the planet. Orbiting at mid-altitude."``\textit{Voyager}?"``I can't tell, Maje Jabin."``Are you sure this is a subspace signal? This looks like radio interference."``Absolutely, Maje Jabin."Janeway was speaking. ``Maje Jabin caused me trouble first. However, I'm willing to set aside the whole incident as a...misunderstanding."``A misunderstanding?" hissed Jabin. ``She killed---"Razik gestured for him to keep quiet. Jabin did.``In fact," said Janeway, ``I'm even willing to compensate you for the damage to Maje Jabin's ship."``Oh?" said Razik. Most Kazon, let alone most aliens, wouldn't have been able to read more than mild interest in Razik's voice, but Jabin, who'd known the First Maje since they were shitting their diapers, heard the surprise and excitement. \textit{Greedy fat fuck}, thought Jabin, resigned. He knew it was going to end like this. He'd be lucky to see a farthing of whatever Janeway paid---Razik was going to stick him with a wrecked ship and no chance to restore his honor.``In our part of space, several civilizations once issued currency backed by antimatter," said Janeway. ``Does that sound familiar to you?"Now Razik couldn't hide his excitement from anyone. ``As a matter of fact, the Ilidarian crown \textit{is} backed by antimatter. How ever did you know?"``A lucky guess," said Janeway.\textit{Neelix!} thought Jabin. He checked the sensor readout. Sure enough, there he was, in the \textsc{l5} junk field. Picking fleas out of his ass, sorting through garbage, and humming show tunes, totally oblivious to the Kazon fleet in the system. ``I'll take care of you, too," muttered Jabin.``A lucky guess indeed," said Razik.``I'm willing to offer the Kazon-Ogla five kilograms of anti-deuterium as payment for the damage inflicted to your ship."Razik's entire face shined with avarice. Even Jabin was given pause. Five kilos, an absolute fortune....``There are two conditions," said Janeway.``Name them," said Razik.``First, you withdraw your fleet from this system until we leave. Second, we know you've been in contact with the Caretaker in the past. We want to know every detail of that contact. Every word."``I can send you all our files on the Caretaker right away. But leaving the system...for that, we might need something more," said Razik.``Such as?" said Janeway.``Such as the secret of your teleporting bombs. Or subspace sensors small enough to fit on a starship."``I'm afraid I can't offer that," said Janeway. ``The laws of my people forbid exchanging our technology."``How unfortunate," said Razik.``I can offer you more antimatter," said Janeway.``How much more?"``Another five kilos," said Janeway. ``Five now, and another five we'll leave behind when we leave. You can leave one or two ships to monitor us, but not the entire fleet."``How will you deliver the first five kilos?"``As you have probably seen, we're out of the system. I hope you understand that after the arrival of fifteen of your battleships, we thought it might be...prudent if we left."``An understandable precaution," said Razik.``However, the starship USS \textit{Earhart} can ferry the antimatter to you."Several officers in the control room looked around in confusion, but Razik kept his cool. ``That would be acceptable," said Razik. ``Perhaps we could meet at the fifth planet?"``We can meet you in the Kuiper belt," said Janeway.Jabin was only half-listening to the conversation. He was looking for patterns in the static. He eased over to the comms operator again. ``Have you seen interference like that before? Solar flares, perhaps?"``I don't think it's being caused by solar interference," he said. ``Look at these static spikes. That looks like nearby lightning strikes."``An electrical storm?" said Jabin.``That would be my guess."``They're in a planetary atmosphere," said Jabin. ``Could they...Ocampa?"``I don't know, Maje Jabin. The pressure on the surface...but I'm no mechanical engineer. And who knows what these aliens can do?"``Can you tell if it's a gas giant storm or a terrestrial storm?"``Perhaps. Give me some time to analyze it."``Quick as you can," said Jabin.``There's no need for you to come all the way to the Kuiper belt," said Razik.``We would hate to trouble you," said Janeway.``It's no trouble at all," said Razik.``I insist," said Janeway.Razik leaned back and chuckled. ``As you wish, Janeway. We eagerly await \textit{Earhart}'s arrival."``I will dispatch them immediately," said Janeway.``I will give them our files on the Caretaker as soon as they arrive," said Razik.``Excellent," said Janeway. ``If we have no further business...?"``None whatsoever."``We'll be in contact. Janeway out." The screen went blank.Razik chortled. ``That woman must think I’m an imbecile," he said.``What are we doing, First Maje?" said Jabin.``They're hiding somewhere in this solar system," said Razik. ``I trust you are working on that problem already?"``Yes, First Maje."``Good. Do you think you can discover where they're hiding without using scouts?"Jabin looked to the comms operator. The operator indicated he could. ``Yes, Maje Razik," said Jabin.``Good. Move the scouts between the orbits of the fifth and sixth planets, but hold them there. No need to spook Janeway if she's still here."``She got help from Neelix. She couldn't have just guessed we use antimatter for money."``Hmm," said Razik. ``It looks to me like he's current on his salvage lease."``Perhaps he's overdue for a health and safety inspection."Razik chuckled. ``As you wish, Maje Jabin. You may dispatch two scouts to pay Mr. Neelix...a safety inspection."``Thank you, Maje Razik," said Jabin.``Now, we'll wait here for Janeway's generous 'gift' to arrive. I was unaware they had a third starship in the system," he said, shooting Jabin a troubled glance, ``so we will take care of it first. By then, we should know where \textit{Voyager} is. After we take care of \textit{Earhart}, we'll flush out \textit{Voyager} and take care of them and \textit{Val Jean}, too. And then, Maj Jabin, we will settle accounts with the Caretaker. I trust \textit{Predator} is ready?"``It is, my lord," said Jabin. ``What about their teleporting bombs?"``Randomly vary the power-up and firing timing on your coilguns," said Razik. ``The trick depends on them predicting openings in our shields ahead of time."``You're betting they can't teleport through shields," said Jabin.``If they can teleport through shields, we have no chance against them no matter how many ships we bring," said Razik.``That fact would seem to warrant caution, my lord," said Jabin.``Ah, but Maje Jabin," said Razik, ``If they could teleport through our shields, why would they be hiding?"Jabin considered that. When he realized he had no good answer, he smiled.``My lord," said the sensor operator, ``the Spyglass is detecting a new warp field in-system, near Ocampa. Configuration unfamiliar, but similar to \textit{Val Jean}. It's coming this way at ten times c."``Half an hour, then," said Razik. ``Excellent. All ships, prepare for battle."\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Voyager}}\\The connection with the Kazon went dead.``We're ready, captain," said Gombe.``Go. Your orders are to try to get their information about the Caretaker, but if things fall apart, blow up the Spyglass and get out of there."``Understood, ma'am," said Gombe. ``\textit{Earhart} out."The connection with Earheart broke. There was silence on the bridge. Most of the lights were out to save heat.``Mister Kim, exterior camera view, please."The main viewscreen, which had been blank, flashed on. \textit{Voyager} was sitting on a flat canyon bottom. Janeway could just make out the trench walls in the murky distance, hidden by heat shimmers and dust suspended in the impossibly thick, impossibly orange air.``We're getting fantastic data, Captain," said Wildman. ``The seismic readings alone...this isn't like any class \textsc{n} planet I've ever seen, ma'am."Janeway wished she could be excited. Now the only thing she heard was ``seismic". ``Is there any danger to us from seismic activity?"``Not from earthquakes," she said. ``We're far enough from the canyon walls we're in no danger from rockslides. It looks like all the loose material has fallen already. The sediment we're resting on is dry and compact; it won't liquefy."``What about volcanic activity?"``We're five thousand kilometers from the mid-ocean ridge. That's where most of the active volcanoes on this planet are. The subduction zone we're in doesn't seem to have any active volcanoes associated with it...which is damn weird. Pardon me, ma'am. Plate tectonics must have frozen already, which is unheard of on class \textsc{n} which tipped over from \textsc{m} so recently."``If tectonics have frozen, why are we getting seismic readings at all?"``The crust is frozen, but the mantle is very hot and active. If the star didn't show every sign of being a middle-aged \textsc{g3v}, I would assume this was a much younger planet. And...Captain, without better two more seismometers, I can't tell for sure, but there appears to be a very hot mantle plume directly beneath that tower a hundred klicks from here."``Did they build the tower in a caldera volcano?"Wildman shook her head. ``The topographic data doesn't look like it. The tower is standing in a river delta, so maybe river sediment buried all of it, but we have good radar data all the way down to the bedrock, and there's no sign of previous eruptions. In fact, there's no evidence of mantle plume volcanism anywhere near here."``Must be a new plume," said Janeway.``It would be an odd coincidence if it were," said Wildman.Janeway's head hurt. ``Just keep working on it," she said. ``Are we in any danger of an eruption?"Wildman shook her head. ``I don't think so, ma'am."``Good. Just keep gathering data. We can analyze it when we get home."``Yes, ma'am," said Wildman. She sounded faintly hurt. Janeway's stomach churned. Too much coffee.Janeway squeezed her eyes closed, trying to focus through the discomfort and exhaustion. Half an hour until \textit{Earhart} reached the Kazons.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Earhart}}\\``Approaching Kazon battlefleet," said Baytart.``Drop warp," said Gombe. ``Load the transporter. Keep the shields up until I say to drop them. Phasers on standby."\textit{Earhart} dropped to sublight speed sixty thousand kilometers from the Kazon battlegroup. ``Their shields are up," said Gombe. ``They're on their guard." He instructed the computer to highlight the ewar ship on the main viewscreen. Then he took a deep breath and hailed Jal Razik.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Wrath}}\\``We are being hailed by \textit{Earhart}," said the comms operator.``Show me the ship," said Razik.\textit{Earhart} appeared on the main viewscreen. It was smaller than a scout, with wings like an aircraft.``Not very intimidating, is it?" said Razik. ``Answer their hails."``They say they're ready to download information about the Caretaker."``Tell them we don't have the subspace bandwidth to send it quickly," said Razik. ``We will have to use a comms laser. Make sure they maintain a constant velocity and heading."``They have agreed," said the operator.``It's only a few quads," said Jabin. ``They'll see through this."``Then send them whatever," said Razik. ``Payroll reports, sports highlights, pornography, anything. Just keep feeding them garbage until we get a firing solution."``Yes, Maje Razik," said Jabin.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Earhart}}\\``Here it comes," said the engineer. ``Unfamiliar file format, but the computer is sorting it. Standby."Gombe gripped the sides of his chair. ``Ensign Baytart, be ready to warp. Don't even wait for my command. As soon as they start powering their guns, we go to maximum warp. Get us as close to that ewar ship as you can."``Got it!" said the engineer. ``Looks like there are actual reports about their encounters with the Caretaker here. Video too, standby, generating a codec."``Show it to me," said Gombe.An inset appeared in the main viewscreen. A naked Kazon was fellating another naked Kazon.``What a bunch of assholes," said Gombe. The computer sounded an alarm; they had just been pinged by a tracking radar.``Power up sequence!" said Baytart. ``Going to warp!"\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Voyager}}\\Janeway was shaken awake in her chair by Ensign Kim.``\textit{Earhart} has engaged the Kazon," he said.A feeble squirt of adrenaline hit Janeway's brain. It woke her up, but it wouldn't last long. ``On screen," she said.\begin{center}\rule{3cm}{0.4 pt}\end{center}``We have a firing solution on \textit{Earhart}," said Jabin.``Fire at will!" said Razik.\textit{Wrath} thundered with the power of a full alpha strike---massive overkill for a tiny scout. Every other ship in the fleet fired, too, creating a cone of death a hundred kilometers across, with \textit{Earhart} right in the middle.What happened next was so fast not even the computers could keep up.The subspace sensors detected a massive warp spike from Earhart and saw the ship warping faster than light to a position less than a hundred meters from the Spyglass. But the radar, infrared, and visible light sensors which controlled the guns saw two \textit{Earhart}s. The confusion lasted less than a tenth of a second, but it was long enough to delay the guns' reaction. Jabin had just noticed something was wrong when \textit{Earhart} fired on the Spyglass.\begin{center}\rule{3cm}{0.4 pt}\end{center}\textit{Earhart}'s phasers ripped at the ewar ship's shields. Up close, it looked like a collection of radar dishes bolted to a cylinder three hundred meters long. The shields, which had been designed by the Kazon to block kinetic weapons and lasers, flickered under particle beam bombardment. Sparks flew from the sensor dishes and the ship's hull.``Our phasers are getting partial burnthrough," said the chief engineer.``Mr. Baytart, keep us moving, full impulse. Stay as close to the ewar ship as you can." \textit{The ewar ship is unarmed}, thought Gombe. \textit{No transporter bombs here unless we can knock a hole in the shield}.Baytart took these contradictory commands and pulled a maneuver that made the inertial dampers wail in agony. Gombe was thrown around in his seat.``\textsc{warning! hull stresses exceeding safety margin}," said the computer.``Keep moving!" said Gombe. He keyed the phaser firing buttons and kept blasting the ewar ship. ``Bring us across their bow. That's where the subspace array is."\begin{center}\rule{3cm}{0.4 pt}\end{center}``They're firing their particle beam weapon at the Spyglass," said Jabin. ``The shields are only partially containing it. They're doing terrific damage to the sensor arrays."``The sublight sensors don't matter," said Razik. ``Just keep them off the subspace array. All nearby ships, fire your point defense into this area," he said, his fingers dancing across a touch board as he spoke.\begin{center}\rule{3cm}{0.4 pt}\end{center}\textit{Earhart} whipped across the bow of the ewar ship, right into a cloud of bullets. The shuttle's shields flickered continuously, rapidly eroding away. The phasers flashed uselessly against the Spyglass's reinforced forward shields.``Warp out!" said Gombe. The warp drive roared for less than a second, and they were ten thousand kilometers away from the fleet.``Microtorpedoes ready," said Gombe. ``Targeting the ewar ship."``Warping back," said Baytart.The warp engine lit up again. \textit{Earhart} fired its entire magazine of grenade-sized antimatter missiles in one burst. The missiles struck the bow of the Spyglass just as \textit{Earhart}came to rest at the stern. Baytart hit the impulse throttle and \textit{Earhart} skimmed over the ewar's ship dorsal side, raking it with phaser fire. They passed the bow, where the shields were still fizzing and glowing, enough to block transporters but not much else. \textit{Earhart} gave the ship a solid phaser shot in the face. They penetrated, splitting one of the detector's hexagonal cells before the shields recovered. More point defense bullets chewed away at \textit{Earhart}. They warped off again, this time to three full light seconds away.``\textit{Earhart} to \textit{Voyager}," said Gombe.``\textit{This is Janeway}."``Captain, the subspace array is protected by heavy shields. We managed to knock them down momentarily and damage one cell, but we can't penetrate them again with what we have left. What are your orders?"``We're not going to get another opportunity like this", she said. ``Warp back to transporter range, try to goad the battleships into firing their main guns. Kill as many as you can."``Yes, ma'am," said Gombe. ``Warp to within twenty-five thousand kilometers of the Kazons. Be ready to drop shields"\begin{center}\rule{3cm}{0.4 pt}\end{center}``They're back," said Jabin. ``They're making an attack run on us."“Could they make it any more obvious?," snorted Razik. ``Well, let's oblige them. Target them with main batteries and fire when ready."\begin{center}\rule{3cm}{0.4 pt}\end{center}``Main guns powering up," said the engineer.``Lower shields. Ensign Golwatt, activate automatic transport sequence."From behind the cockpit came the whine of a transporter.\begin{center}\rule{3cm}{0.4 pt}\end{center}Ensign Golwatt had specialized in transporter operations at the Academy. She had a knack for the finicky machines, an instinct for their operations that bought \textit{Earhart}and her crew approximately ten extra seconds of life.When the transporter beam struck the Kazon shields, it ``bounced" and the antimatter bottle re-materialized on \textit{Earhart}'s transporter pad. The problem was, the bottle's containment field was on a five second timer. And there wasn't enough time to cycle the transporter again.She did the only thing she could do. With one hand, she convinced the computer to open the airlock, and with the other, she raised the emergency forcefield to keep the rest of the ship from depressurizing. She snatched the bottle off the pad just as the doors blew open, and, pushing off the deck as the air rushed out, leaped off the ship with a bottle of death clutched to her breast. She was three kilometers clear of the shuttle when the seals fell and antimatter touched matter, vaporizing her and searing everyone in the still-unshielded \textit{Earhart} with enough raw gamma rays to kill a Brontosaurus.\begin{center}\rule{3cm}{0.4 pt}\end{center}Obayana Gombe knew he was dead even before he heard the radiation alarm. ``\textit{Voyager}, this is \textit{Earhart}," he said. ``We have taken severe damage. We will try to complete our mission." Pause. ``Tell my parents I love them." He sent \textit{Voyager} a copy of all the data the Kazons had sent him, then cut the comms.The world was starting to spin. \textit{Big dose}, he thought. He'd be unconscious in seconds. He focused long enough to put a course into the computer, made the sign of the cross and prayed the isolinear chips hadn't all been fried, hit the ``engage" button, and then slumped over into a coma.The Federation starship \textit{Earhart} lit her warp engines one last time. She slammed into the weakened forward shields of the Spyglass at warp 3 with nearly five kilograms of antimatter still on board. When the dust cleared, there was nothing left of the Spyglass but a slowly spreading field of half-molten junk.\begin{center}\rule{3cm}{0.4 pt}\end{center}The cabin lights were low. Janeway appreciated that. She sat on the bed, legs hanging over the side. Next to her sat Chakotay. She'd insisted the armed guards stay out.``They were waiting for it," said Janeway. ``They didn't just know how to block a transporter bomb, they knew how to throw it back at us."``How did they do it?"``They varied their power-up timing."Chakotay nodded. That's what he would have done. ``They're backwards, but they're not stupid," he said. ``You know the difference between a tactic and a trick?"``What's that?"``A trick only works once."Janeway sighed. ``I killed them."``Were they the first to die by your orders?"She shook her head slowly. Chakotay looked puzzled. She explained. ``Just before we left. Bujold asked me to send someone to the bridge while the ship was in the Badlands. I volunteered to go myself but she...didn't think my expertise matched her needs. So I flipped through my personnel files until I found someone with experience studying interstellar plasma anomalies—Lieutenant junior grade Mariana Donaldson, twenty-six, husband and infant son back on Alpha Centauri. The first time I met her was when I told her to report to the bridge."``And she died in the blowout," said Chakotay.``Yes," said Janeway.``It wasn't your fault," said Chakotay.``I've told myself that. It doesn't seem to be making any difference."``It never does," said Chakotay.``How many have you lost?" said Janeway.``Seven," he said.``How do you cope with it?"``I tell myself they died for a reason." The words hung in the air.``Even when they didn't?"``Gombe and the others bought us time. You said the Kazons have fallen back deeper in the Kuiper Belt, and their scouts are advancing slowly."``A few hours at most," said Janeway.``That's better than what we had," said Chakotay.``We can't hide forever."``Then let's not. Get the warp core back online and let's show them what this ship can really do."Janeway shook her head. ``There's not enough time. Carey's working as fast as he can, but they'll be here before he's finished." \textit{I waited too long}, she thought. \textit{My fault. Everything's my fault.}Chakotay had an answer. ``Let Torres help."\textit{Well}, she thought, \textit{What's the worst that could happen? We'll all die?} She laughed, once, a short bark that she refused to explain to Chakotay. ``You're right, why not?" She tapped her commbadge. ``Bridge, this is Janeway. Hail \textit{Val Jean}."``They're not responding, ma'am. Their communications might be out."``Understood," said Janeway. \textit{Oh, shit}. ``Oh, shit," she said.``What?" said Chakotay.``We knocked out their communications and their sensors. They're blind and deaf out there."Chakotay's eyes widened. ``If they Kazon go after them...Captain, I have to warn them." He seemed to think about it, and then added: ``I have to bring them spare parts. If their comms aren't back up now, it's because B'Elana doesn't have the spares to fix it."``How will you get to them?"``I'll take a shuttle."``We can't lower the shields to let you out," said Janeway.``We'll phase-invert the shuttle's shields; we'll pass right through \textit{Voyager}'s shields, like a photon torpedo."``That's incredibly dangerous. If you leave a gap in either shield, even for a moment..."“We have to take the chance," he said. ``I will need a good pilot, though, if we run into trouble."``I thought you could fly," she said.``I can, but not well," he said.``My best shuttle pilot is dead," said Janeway.``No, he's not."\begin{center}\rule{3cm}{0.4 pt}\end{center}``You're kidding, right?" said Paris.``No, I'm not," said Janeway. ``We need your help."Paris glared at both of them. ``Why should I risk my life to help the Federation \textit{or} the Maquis?"``Why don't you think about someone besides yourself for once in your sorry life?" said Chakotay.``I did! Fat lot of good it did me."``All right, fine," said Janeway. ``We'll find someone else. Go back to sickbay."``Tom, if you don't help me, A'shadieeyah is going to die," said Chakotay.Paris froze halfway to the doors. He turned around. ``She's on \textit{Val Jean}?"``Of course she is," said Chakotay.``Bujold tried to use her against me...I just thought she was lying...shit! Where's the shuttle bay?"Janeway pointed at a nearby goldshirt. ``Take him to the shuttlebay. Mr. Paris, start your pre-flight checklist as soon as you get down there." She tapped her commbadge. ``Mr. Carey, has the cargo been delivered yet?"``\textit{Yes, ma'am. One Mark XXI general-purpose sensor pallet. It's been loaded onto the shuttcraft} Drake. \textit{Crewman Jaxz is waiting there with it.}"``You're all set," said Janeway. She glanced at the door through which Paris had vanished. ``Is this going to work?"``Tom Paris is useless as a leader, as a friend, and as a human being in general," said Chakotay. ``But he's good at flying spaceships. Hopefully, I'll be back in a couple hours."``That's not exactly reassuring," said Janeway. ``Are you sure you don't want a different pilot?"He shook his head. ``I watched Tom Paris run an entire Cardassian wolfpack in circles for three straight days once. You fly with the Maquis, you learn how to fly in hostile territory."``But you hate each others' guts."``You learn to make do with what you have in the Maquis, too," said Chakotay. ``Besides, I can always kill him later."Janeway wondered how literal he was being.``I'd better go," said Chakotay. ``One more thing, though. If you don't mind, I have two pieces of advice for you."``What are they?" she said, expecting some tactical insight that would help them if the Kazon suddenly rushed to Ocampa.``Number one: get some sleep," he said.``But there's so much to do," said Janeway.``Trust your crew to do it," said Chakotay. ``They're Starfleet; they can look after themselves for a few hours."``Will a few hours make any difference?"``It could be the difference between the right decision and the wrong one. Or the right decision in time and the right decision too late."Janeway wanted to argue with him, but after all the talk of sleep, it was suddenly as if her mind was full of pancake syrup. She was holding off fatigue by sheer willpower and running out of it fast. \textit{Voyager} was, for the moment, immobile and hidden. If anything was going to go wrong, it would go wrong with or without her on the bridge.``What's number two?"``You're in command. You should dress the part."``What do you mean?"He pointed at her chest. ``Put on a red uniform."``I'm sorry I shot you," said Janeway.``It happens," said Chakotay.They parted with a salute. Janeway started wandering in the direction of her cabin. She paused a moment to lean against the wall to rest, and was startled to wake up on the floor five minutes later, having fallen asleep standing up.As it turned out, her cabin had taken a direct hit from a Kazon railgun shell and the entire section was vented to space. She needed to make new arrangements.``Computer, find the nearest vacant officers' cabin and assign it to me," said Janeway.There was a chirp and a moment later, the computer gave her a room number on the same deck. It wasn't until she got there that she realized it was Bujold's. A crazy accident or a subtle hint from the machine? She was too tired to care.As it happened, she and Bujold had been about the same size. She took one of the former captain's uniforms out of her wardrobe and draped it over a chair. \textit{How am I going to change uniforms with my damn arm in a sling?} she thought. Never mind. It could wait. ``Computer, wake me in two hours," she said. She laid down on the bed, flat on her back, eyes closed. She was asleep ten seconds later.\begin{center}\rule{3cm}{0.4 pt}\end{center}``Pre-flight checklist complete. We're ready when you are, \textit{Voyager}."``\textit{Acknowledged, }Drake\textit{. Stand by for launch clearance.}"Paris leaned back in his seat and danced his fingers across the Okudagram.``Do we have the right parts with us?" said Chakotay.``Yes. I already checked," said Paris.``Crewman.... Jaxz?" said Chakotay, taking a stab at the pronunciation. ``Could you check the cargo for me?"``I told you I inspected it already," said Paris.``It's a Mark \textsc{xxi} general-purpose sensor pallet," said Jaxz. He was a short, small alien in a gold uniform, not much bigger than a human twelve year old. Paris couldn't place his species.``I told you," said Paris. ``I'm not an idiot, you know," he muttered.``Could have fooled me," said Chakotay.``Drake, \textit{this is shuttle control. You're cleared for launch}."``Roger \textit{Voyager}," said Paris. A few more keystrokes, and Drake rose off the deck and glided into position over the launch zone.``Matching shield frequency to \textit{Voyager}," said Chakotay, tapping at his own console. There was a brief blue shimmer outside the cockpit. ``Phase inverted."``\textit{Opening shuttle bay doors.}" Pause. ``\textit{The chief engineer would appreciate it if we could close them again as quickly as possible}."``Roger that," said Paris.Ahead of them, the doors drew open like a curtain. A beam of hellish orange light speared Drake, widened to lay across the whole shuttlebay like a disease. \textit{Voyager}'s shield was visibly flashing and crackling.Paris's finger hovered over the launch button. Neither he nor Chakotay said anything.``Well," said Paris. ``It's now or never." He jabbed the launch button and Drake hurled itself towards the shield. The shuttlebay doors were already sliding closed again.Drake hit the shield with a bang and rattled so hard Paris thought for a moment they'd screwed up and bounced off. And then they were clear of the nacelles and rising vertically, the shuttle standing on its ass and roaring straight up, trying to clear the troposphere before the atmosphere crushed them. \textit{Drake}'s engines bellowed as Paris forced them through air like ocean water, drowning out the alarms and Crewman Jaxz's shouts. They cleared the canyon walls and there was nothing to see through the cockpit windows except the cloud deck. Paris glanced at the altimeter. The numbers were rising so fast he couldn't read them.``External pressure falling!" said Paris. ``Approaching the lower cloud layer."``Drake \textit{this is }Voyager\textit{. What is your status?}"``Thirty kilometers and climbing, \textit{Voyager}." The numbers on the external barometer and thermometer were falling. ``We're out of the danger zone." He scanned his sensors, looking for any dangerous weather. ``No thunderstorms nearby. We'll clear the atmosphere in ninety seconds."``\textit{The closest Kazon scout is six AUs from here. We're transmitting their coordinates now}."``Acknowledged," said Chakotay. To Paris: ``I've got a read on \textit{Val Jean}." He showed Paris the coordinates.``It'll take at least an hour to reach them at Warp 4," said Paris. He entered the coordinates. ``Engaging." The shuttle zipped away at more than 500 c.``This system is full of Kazon scouts," muttered Chakotay. ``I hope there aren't any hanging around Ocampa by the time we get back."``Does this thing have weapons?" said Paris.Chakotay tapped on his console. ``Type four phasers," he said.Paris snorted. ``Useless"``Kazon shields only partially block phasers," said Chakotay. ``On the other hand, their armor holds up fairly well. If we do get into a fight, we'll have to aim for a soft spot."``What are their scouts like?" said Paris.``Thirty meters long. Fastest I've ever seen them travel is warp 7. They maneuver pretty badly at sublight; not a lot of thrust for their size."``We can run rings around them, then," said Paris.``They're well armed," warned Chakotay. ``Their heaviest guns are forward mounted, but they've got good coverage from all angles. And they're tough for their size. This shuttle couldn't handle them."``Could \textit{Val Jean}?" said Paris.``We already have once. When we first got here. I have a feeling we're going to have to do it again before this is over."They settled down into an uncomfortable silence that dragged for fifteen minutes. Crewman Jaxz seemed content to sit in back and say nothing to the Maquis.``So," said Chakotay, ``how was prison?"``Just great," said Paris. ``Sorry you missed it."``Is that why you were on \textit{Voyager}?"``I was protecting you guys. I led Bujold on a wild goose chase for eight hours."``I hear they rescued you from the brig. Looks like you failed that that, too."``You're welcome," said Paris.``Oh, get over it," said Chakotay. ``Maybe if you didn't run around with that chip on your shoulder all the time, somebody might feel sorry for you."``That's funny coming from a guy who has such a bad temper he had to be phasered."``You started that fight," said Chakotay.``You deserved it," said Paris.``Why'd you do it, Tom? Why'd you agree to help Bujold in the first place?"``She offered me parole," said Paris. ``I had a choice between another decade on New Senegal or Betazed. Which would you have taken?"``Are you asking if I'd betray the Maquis to chase Betazed skirt? No, I wouldn't."``Betazed skirt" made Paris think about Lieutenant Stadi for a moment. He pushed it aside; too weird to deal with now. ``I didn't betray you."``You tried to play it both ways," said Chakotay. ``You wanted to help Starfleet enough to get paroled---don't try to deny it; \textit{Voyager} never could have made it to the Rat's Nest without your help---but not enough to hurt your conscience, such as it is. And it blew up in your face, just like it always does."When Paris didn't respond, Chakotay pressed on. ``Did you ever stop to think about why your time commanding \textit{Val Jean} was such a disaster?"``I got unlucky," said Paris. ``And then you took advantage."Chakotay sighed and shook his head. ``You're still blaming other people for your mistakes," he said. ``You blundered right into a trap. I told you it was a trap beforehand, and you didn't listen. And then you froze solid---three cruisers bearing down on us and you couldn't issue a single order. If I hadn't taken control, we'd all be starving in a Cardassian prison camp now. Is it any wonder why the crew voted me the new captain? And before you blame me for you getting caught by Starfleet, you were welcome to stay on \textit{Val Jean} as a pilot. You were the one who stormed off."``Now you're really full of shit," said Paris. ``Yeah, I was 'welcome' to stay---after you stood up on the bridge and said 'Tom Paris is incompetent to lead, incompetent to fight, and incompetent to be a Maquis, and if you don't vote for me, he's going to get us all killed'. You remember that speech?"Now it was Chakotay's turn to say nothing.``The vote was thirty-nine to one," said Paris. ``That I wasn't competent to be a Maquis. Would you have stayed?"``It's irrelevant," said Chakotay. ``Nobody ever would have accused me of being one."Silence descended on the shuttle again.``Anybody want something to eat?" said Jazx.\begin{center}\rule{3cm}{0.4 pt}\end{center}\textit{Drake} pulled up alongside \textit{Val Jean}. They were practically close enough to touch, but \textit{Val Jean} had no idea they were there.``Their sensors are still out," said Chakotay. ``Janeway really did a number on them."``Can't they look out the window and see us?" said Paris.``I covered up all the windows with armor plate," said Chakotay. ``It seemed like a good idea at the time."``Well, what do we do now?" said Paris.``Can we beam over?" said Jaxz.``Their shields are up," said Chakotay.``But they're very soft up front," said Paris. ``I'll bet we could push this shuttle right through."``That's insane," said Chakotay. ``There's a meter and a half of clearance between the hull and the shields."``Why don't we just shoot through them?" said Jaxz.``They'll start randomly maneuvering to evade," said Paris. ``We'll never be able to match speeds for a transport." He shook his head. ``Can you believe this?"Neither of the others said anything. Paris wondered, not for the first time, if he was having some kind of elaborate nightmare. And then, he had an idea.``I've got it!" he said. ``Chakotay, you know Morse code, right?"``Of course," said Chakotay.``Does anybody on board \textit{Val Jean}?"``Seska will," said Chakotay. ``But we've already tried radio; they're not responding."``Not radio. Use phaser pulses. Low power, just hot enough for them to notice. Hopefully Seska will recognize the pattern."``Does anybody have any better ideas?" said Chakotay. Jaxz didn't, and neither did he.``All right. I'll program the firing pattern into the computer."\begin{center}\rule{3cm}{0.4 pt}\end{center}\textit{\textbf{Val Jean}}Seska was so wound up the alarm caused her to jump out of her seat.``Someone's firing phasers at us!" she said. ``Bendera, what’s happening?"“I can’t tell. Sensors aren’t responding.”``Forget it!" said Torres. ``They're cooked!"Seska snarled a curse. ``Mohommad, prepare for warp!" She checked her screen, trying to identify the attacker. Whoever they were, they were shooting again.“Wait a minute,” said Bendera. “I think there’s a pattern here.”Seska decided to gamble. ``Belay that, Mohommad. Hold course."``Are you crazy?" said Torres.``Shut up!" said Seska. She leaned over Bendera’s shoulder to read his tactical display. ``Long and short...that's Morse code!"``What does it say?" said Mohommad.``Hold on...'I am Chakotay. Lower your shields.'"``Sure," said B'Elana. ``And I'm Queen of Neptune. This is a lame trick."``There has to be some way to communicate with them," said Seska.``Not radio, and not subspace," said Torres.``Do the running lights still work?" said Bendera.\begin{center}\rule{3cm}{0.4 pt}\end{center}``No response," said Paris.``Yes, there is," said Chakotay. ``Look at the lights." They were flashing a pattern back at them. "'Prove your Chakotay'" he said. He grinned. ``She used the wrong 'you're'. That's definitely Seska."``How are you going to prove you're who you say you are?" said Paris.``I'll tell her something only I would know." He glared at Paris. ``Don't read over my shoulder." He typed in his message.\begin{center}\rule{3cm}{0.4 pt}\end{center}``They're responding," said Torres.Seska decoded the message. Then she flushed crimson.Mohommad turned around in her seat, eyebrows raised and mouth hanging open. ``Really?"``I didn't know you read Morse code," said Seska, still bright red.``Wait, I can't. What did he say?" said Torres.``I'll tell you later," said Mohommad.``I'll throw you out the airlock if you do," said Seska. ``All right, that’s definitely him. Lower shields."\begin{center}\rule{3cm}{0.4 pt}\end{center}``Their shields are down," said Paris.``All right,” said Chakotay. “I'll beam over with Jaxz and the sensor pallet."``Like hell," said Paris.``What's your problem now?"``I want to see A'sha."``She won't want to see you. Trust me."``I don't care," said Paris.``We don't have time for a reunion!" said Chakotay.``All right, fine. You'd better beam over first, though. Who knows what they'll do if a stranger appears on their bridge."Chakotay shrugged. He had a point. ``All right." He took his place on the shuttle's transporter pad. ``Lower shields and beam me over."``Roger. Energizing."\begin{center}\rule{3cm}{0.4 pt}\end{center}Chakotay materialized on \textit{Val Jean}'s bridge. Seska cast decorum aside and hugged him. ``How did you escape?"``I didn't. Janeway let me go. She sent a peace offering."``What?"He tapped the commbadge he'd borrowed. ``\textit{Drake}, this is Chakotay. I'm ready over here."There was transporter whine and an extra-wide column of sparklies. ``Oh God damn it," said Chakotay, as Crewman Jaxz, holding the sensor pallet, materialized on the bridge with Tom Paris hanging on to his shoulders.\begin{center}\rule{3cm}{0.4 pt}\end{center}``He grabbed me as I was dematerializing!" said Jaxz. ``I couldn't stop him."``What the hell is he doing here?" said Seska.Paris ignored them. He was looking at the pilot’s station. ``Hello, A'sha," he said.``How much did Starfleet offer you?" she said.``Parole. I tried to protect \textit{Val Jean}."``You son of a bitch," said Torres. ``You dispicable traitor. I should gut you where you stand."``Hello to you, too," said Paris.``Enough," said Chakotay. ``We don't have time for this. The Kazon are bearing down on the inner system. B'Elana, I need you to go back to \textit{Voyager} and help get her engine started."``Have they figured out how to get us home yet?" said Torres.``No," said Chakotay. ``Janeway's people are working on it. If we can hold the Kazon off, maybe they can get us out of here. The only way that's happening is if \textit{Voyager} has a working warp core."``What about \textit{Val Jean}?" said Seska.``Crewman Jaxz and I will stay behind to install the new sensors. As soon as that's done, we're going to try to buy \textit{Voyager} more time. B'Elana, can you ride back to \textit{Voyager}without killing Tom?"``Maybe," she said.``If you kill him, you're going to have to dock with \textit{Voyager} yourself. They're parked on the surface right now. You ever fly in a Class N atmosphere?"``\textit{Fine}," said Torres.Tom had tuned out the conversation on the bridge. He and A'Sha locked eyes. They were dark and beautiful, just like he remembered. Unfortunately, there was no sympathy in them. She glared at him, angry. Neither of them were telepathic, but he could read her face easily enough: \textit{I didn't invite you back into my life}.``I'm sorry," he mouthed.She turned away from him. It was all the response he'd get. So much for that. Beaming over had been a stupid mistake. He wanted to go back to \textit{Voyager}. Even an hour in a shuttle with B'Elana would be better than this.Crewman Jaxz was already studying a schematic of \textit{Val Jean}'s electrical system. ``Oh yes, I can install the new sensors and antennas. Very easy," he was saying.``And if he runs into any problems, Seska and I can help," said Chakotay. ``B'Elana, Tom, get back to \textit{Voyager}. We don't have time to waste."“Wait,” said Bendera. “Where’s Tuvok? Is he all right?”Chakotay went to reply that he was, then hesitated. He hadn’t actually heard from him in hours, not since Janeway had stunned him. ``He's fine," said Chakotay. ``He's still working on the Caretaker problem. B'Elana, I said go; the clock's ticking."Torres picked up a tool kit. ``Fine." She pointed at Tom. ``Let's go, asshole."\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Drake}}\\B'Elana was sitting in the back of the Federation shuttlecraft, brooding, when Paris startled her by speaking up.``So what's your story?" he said. It was the first words either of them had spoken in half an hour.``What do you mean, 'what's my story?'"``I don't know. How's life? How have you been?"``Are you trying to make \textit{small talk}?"``It's not like I have anything else to do," he said.``I don't want to talk to you," she said.``Fine," said Paris. ``I'll talk. You want to know why I helped Starfleet."Torres grunted. What she really wanted to know was when he'd take the hint and shut up.``I'll tell you," said Paris. ``It's because they offered to help me. I was tired of digging holes in the desert, and if I helped Bujold, I wouldn't have to anymore. I figured I wouldn't find Chakotay anyway, so what's the harm?"``You led Starfleet to the Rat's Nest. That's one of our best hiding spaces, gone."``Oh come on," said Paris. ``The Federation and the Cardassians both knew about it already. It was only a matter of time before they charted the way in from both sides. Maybe I sped that up, but not by much." He leaned his head around his seat to look at her. ``You know, a little gratitude would be nice."``Gratitude? For what?"``If I hadn't led \textit{Voyager} to the Rat's Nest, you'd be stuck out here with no help."B'Elana laughed. ``Are you kidding? Since you arrived here, \textit{Voyager} broke our ship and then had to ask us to help fix theirs. Some help you've been."``Chakotay's right. The only chance you have of getting home is with Janeway's blueshirts. Unless you think you're up to the task of figuring out ancient alien space stations."``Janeway's an idiot," said Torres. ``If I were commanding that ship, the warp drive would have been running hours ago."``Starfleet isn't big on letting first-year Academy washouts command starships," said Paris.``You're one to talk," said Torres.``I didn't wash out, I quit," said Paris.``Please," said Torres. ``You had thirty demerits, your grades sucked, and you were drunk all the time. The only reason they let you quit is to save your father the embarrassment. If your daddy wasn't an admiral, you'd have been expelled just like me."``At least I didn't sleep with my instructor," said Paris. ``Or my roomate’s boyfriend, or half the football team."``You really are an asshole," said Torres. ``I never understood what A'sha saw in you." She spat. ``Never understood what I saw in you, either."``Screwed up people attract each other," said Paris. ``That's what you saw in me.``A'sha's not screwed up. She's going to lead her own cell one day."Paris took time to think about his answer. ``I tried to be better for her."``You did a shitty job," said Torres. ``You know, she would have been happy never to see you again."``I know she would have been. I wouldn't."``Always about you," said Torres.``I see you've been working on the angry Klingon act," said Paris, by way of changing the subject.``I've been under stress," said Torres. ``It's been a rough couple of days."``You're not going to melt down again, are you?" he said.``Fuck you, Tom," she said. In her mind's eye, she could see the discharge letter from Starfleet: \textit{Unfit for service...lacks emotional maturity and self-control...unrelated to Klingon physiology, despite Cadet Torres's claims...\textbf{psychological treatment strongly recommended}}. She'd been holding together for more than a year; finished top in her class in mathematics, aced the entrance exam, had no problem with the psych screening. She'd cruised through boot camp when ``tougher" cadets crumpled under the strain. And then she started classes, and in a few months, she'd come apart again. They promised they'd reconsider admitting her if she went through treatment and passed another psych screening. Instead, Tom Paris, who'd quit just weeks before her, recruited her into a Maquis cell.The shuttle fell silent again.After another twenty minutes of silence, Paris spoke up. ``What's Chakotay going to do if captain science whiz can't get us back home?"``How should I know?" said Torres. ``Why? Are you looking for a ride?"Paris laughed. ``Are you serious? If we're taking the long way home, I'd rather do it on \textit{Voyager}. Even in the state she's in."``What the hell happened, anyway? When we got pulled through, \textit{Val Jean} was shaken but not damaged."``Why does it look like a flying pile of shit, then?"``Watch it," said Torres. ``It’s all battle damage. We were in a running gun battle with two cruisers. What's \textit{Voyager}'s excuse?"``I think they tried to turn away from the displacement whatever-the-fuck and got hit broadside. That’s why starboard is smashed up harder than port. Bujold should have let me fly.” He thought again about Lieutenant Stadi. She’d ratted him out, but that had ended up saving his life.``What do you think of her?" said Torres.“Who?”“Janeway.”``Out of her league," said Paris.``That's what I thought, too," said Torres.``We're approaching the planet," said Paris. ``Hang on to your ass; this is going to be a rough landing. Once we're on the deck, you'd better get to engineering as fast as you can."``Why?" she said.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Wrath}}\\``It's definitely lightning," said the comms officer. ``\textit{Voyager} was sending the signal by radio to \textit{Earhart}, not subspace."``Which planets in the system have lightning in the atmospheres?" said Jabin.``Ocampa itself, and all the gas planets."``But if they were at one of the gas planets..." said Jabin.``Right. We would have noticed the lightspeed lag between them and \textit{Earhart}. They must be hiding on Ocampa."Twenty minutes later, the Kazon fleet was on the move.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Voyager}}\\``Captain Janeway."Janeway rolled over and groaned. How long had she been asleep? Not enough. ``What is it, Tuvok?" she said.``Sensors have detected the Kazon fleet moving in this direction. The advance elements will be here in sixty minutes."``Did Paris and that Maquis make it back?"``Miss Torres is in the engine room now. I'm led to understand she's here for the duration; Lieutenant Carey does not believe the shields will withstand another shuttle launch."Janeway sat up. Her head was swimming. She was still so tired. The air in the cabin was hot and sticky, oppressive. Tuvok presented her a hypospray.``From the Doctor," he said. ``It will keep you alert for several hours."``And then I pay for it, right?"``I believe so," said Tuvok.``Give it to me." Tuvok obliged, giving her a shot in the neck. It was as if someone had pushed an ``on" button. Instantly, she felt awake and aware. But it was a thin, jittery awareness, like too much coffee, a rickety bridge over a chasm of exhaustion. She cursed herself for not sleeping more when she had a chance.``Help me take this sling off," she said. Once it was gone, she tried moving her arm and shoulder. It was stiff and sore, but she had her full range.``Turn around for a minute," she said to Tuvok. He obliged, and she stripped off her bloodstained blue tunic and replaced it with the red one she'd left on the chair. As she'd hoped, it fit her pretty well.``How do I look?" she said, fixing her commbadge to her breast.He faced her again. ``You forgot your rank insignia," said Tuvok.``I'm getting to them," she said. She started transferring them from her old tunic to her new one. ``I never thought I'd get to wear red," she said. ``I took the bridge officer's exam as a self-improvement exercise. I never thought I'd get a command, even a science ship."``Predictability is not a hallmark of life in Starfleet," said Tuvok.She stuck the second pip in place. ``I've noticed," she said. She looked at herself in the mirror. Tuvok stood behind her, watching her watch herself.``How well did you know Bujold?" said Janeway.``As I've said, we were colleagues for many years. I would have called her my friend."``I'm sorry she's not here," said Janeway.``As am I," said Tuvok. ``I believe, however, that she would have been pleased with your performance, under the circumstances."She smiled. ``I don't think she would. But thank you." She straightened her tunic and put her hair back in place. ``Come on. We have a battle to plan."\begin{center}\rule{3cm}{0.4 pt}\end{center}B'Elana Torres wanted to drool when she got her first look at \textit{Voyager}'s warp core. \textit{If I had an engine like this...}. Then Ensign Vorick briefed her on the warp system's state and she wanted to cry.``What the hell have you been doing all this time?" she said.``Making repairs to everything else that's broken on this tub," said Rodriguez, the senior chief petty officer. Chief Engineer Carey was conspicuous by his absence. ``And inspecting the system. The good news is, we can still get warp speed from the portside nacelle. Unfortunately, the starboard plasma injector is completely shot, so we'll have to run on one nacelle."``What about the core itself?"``Good as new," said Rodriguez. ``And the antimatter injectors themselves are working.”“Then are we ready to restart?” said Torres.``No," said Carey, walking into the control room. ``The antimatter constrictor valve is shot."Torres rolled her eyes. The \textsc{acv} weighed less than a kilogram and could be installed in five minutes. ``So replace it," she said.``Right, I forgot. You're the dipshit Academy washout, and I'm just a professional engineer, so obviously you know more than me," said Carey. ``I checked the cargo manifest. The spares were delivered to \textsc{ds9} but they were never loaded on the ship. And we can't replicate the force field relays, so don't even ask."Torres cursed in Klingon. Carey looked vaguely satisfied---obviously he was the kind of guy who preferred being right to being alive.``Perhaps we can generate enough power with the impulse reactors to energize the warp coils," said Vorick.``That might have worked if the Maquis hadn't blown one of them up," said Carey. ``As it is, we can't generate enough electrical power with the impulse engines to cross the warp threshold, and we can't get the warp core back online. Oh, and in case you hadn't noticed, we have about two hours left before we all die of heatstroke, so we can't hide down here much longer, either."``It's such a simple part," said Torres.For the first time, Carey seemed sympathetic. ``Yeah, it is," he said. ``Until it breaks and you don't have a replacement."``Is there a spare on \textit{Val Jean}?" said Rodriguez.Torres shook her head. ``There’s no such thing as spare parts in the Maquis. We need everything we have just to keep the fleet running.”``Well, we have to do something," said Rodriguez. He snapped his fingers and looked up. ``Wait a minute. That guy Neelix---he makes his living raiding a junkyard. What if he has one?"``What do you think the odds are that some civilization in the Delta Quadrant just so happens to use the same type of \textsc{acv} as us, and that it happens to be floating in that particular junk field, and that hedgehog happens to have one?" said Carey.``Exceptionally poor," said Vorick. ``However, given what we know about the Caretaker and this solar system, the odds are, the wrecks in that junkyard did not all originate from the Delta Quadrant."Nobody said anything for a moment. Finally, Carey tapped his combadge. ``Engineering to bridge."\begin{center}\rule{3cm}{0.4 pt}\end{center}``I didn't know you guys were still in the system," said Neelix. Torres, Carey, Rodriguez, and Vorick were sitting in on the call from a repeater screen in Engineering.``We're having some mechanical problems still," said Janeway. ``We were hoping you could help us out with a part."``I'll see what I can do. What do you need?"``We need an antimatter constrictor valve," said Carey.Neelix frowned. ``The Kazons don't leave me a lot of engine parts. I have everything on board cataloged; I'll let you go through it. Stand by."``He's not going to have it," said Carey.``You must be great at parties," said Torres.A nearby computer panel *bleeped*. Neelix had transmitted his catalog over. Torres whistled; for a one-man operation, he was organized. Most of the parts had descriptions, which the computer dutifully translated, and pictures. She hoped it was indexed, too. ``Computer," said Torres, ``scan for any compatible \textsc{acv}s."The scan took less than a moment. ``\textsc{no compatible component found}," said the computer.``Well, so much for that," said Rodriguez.``Wait," said Torres. ``Computer, find \textit{any} \textsc{acv}s."Three of them flashed on the screen. One was so badly burnt she barely recognized it. The second was so alien she had to take the computer's word it was actually a constrictor.The third was Cardassian. Torres yelped and pointed at the screen. ``That one!"Rodriguez looked. ``That's a Cardassian valve."``It'll work, though," said Torres. ``I use spoon-head parts all the time."``No it won't," said Carey. ``Look at the damn connectors. We'll never get it to fit on our fuel line."``Haven’t you ever heard of a socket adapter? I’ve got a blueprint book on \textit{Val Jean }full of them. Solid metal, easy to replicate.”``Do they work?" said Carey. ``Because if they don't and the valve leaks, it'll blow the ship apart."``You want me to tell you how many times \textit{Val Jean}'s had the shit kicked out of her and my adapters have never failed? Besides, either we try these and we \textit{might} die, or we sit here until the Kazons come and bomb us and we \textit{definitely} die. Unless you have a better idea, this is it."``I think she's right," said Rodriguez. ``What else are we going to do?"``\textit{Engineering, what's going on down there?}" said Janeway.Carey tapped his combadge. ``Captain, Neelix has the part."\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textbf{Talaxian shuttle \textit{Baxial}}\\Neelix cut off the channel to \textit{Voyager} and started prepping his ship for warp. He was trying to figure out how much he would charge Janeway for the part---running back to Ocampa when there were angry Kazons in the system would cost a lot more than a bath. Maybe some of their guns---he'd seen a security goon carrying one. They were shaped funny and they didn't seem to have trigger guards, but he was sure they were powerful. ``I wonder how much a collector would pay for one," he said. He patted the alien ACV sitting on his passenger seat.Neelix had his course charted and was just waiting for the warp core to warm up when someone shot his spaceship.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Val Jean}}\\``Looks like Torres might be able to fix their engine," said Chakotay. ``There’s a Cardassian valve sitting on board Neelix's ship. As soon as he delivers it, \textit{Voyager} will have warp power again."Bendera was still trying to test and calibrate the new sensors. ``That's good to hear. Do we need to...uh oh."``What?" said Chakotay.``Two Kazon scouts just showed up in the junk field. They're firing. They're...I think they're broadcasting something."``On speakers," said Chakotay.".\textit{..of the Kazon Ogla. You're under arrest for abetting enemies of the Ogla Sect and the Grand Maje. Heave to and prepare to be boarded.}"Everyone looked to Chakotay, like they always did. He didn't hesitate.``A'sha, lay in a course, maximum warp. Battlestations."\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Val Jean}}\\``Two scouts, Alpha and Bravo, and neither of them see us coming," said Chakotay. \textit{Val Jean}'s crew was gathered on the bridge, crammed in where they could stand, while Chakotay used the main viewscreen as a blackboard. ``You can see here that scout Alpha has docked with Neelix's ship. We have to drop out of warp right on top of it and disable its engines. Then we'll bug off, turn around, come back, hit them again, until they’re totally disabled. Then we work on Bravo.”``Can we destroy Bravo in one pass?" said Seska.``Only with a lucky shot. And we don't want to hang around under their guns, so we'll have to do a lot of in and out."``I can't promise the engines will be up for that," said A'sha. ``No disrespect to you, Hogan, but we don't have B'Elana here to nurse them."Hogan nodded to show he wasn't offended. That faintly worried Chakotay, who didn't need an acting chief engineer who didn't think he was good enough to keep the engines running.``Hogan will be fine. Remember that time we got jumped by a \textit{Miranda} while Torres was drunk?" said Bendera. ``Hogan took care of us then."``Exactly," said Chakotay, nodding his thanks at Bendera. ``Remember, nobody here would be on my crew if I didn't know he was good enough. The engines will be fine. Seska, where's the rest of the Kazon fleet?"``Bearing down on Ocampa at Warp 5. They'll be there in half an hour."``Right. So we don't have much time. Once we've isolated and disabled this scout, we'll grab Neelix and the part. Hopefully we can just beam them out, but if we have to grab them, we'll send over boarding parties. Are the transporters ready?" said Chakotay.``They are," said Seska.``Kurt, do you have your boarding teams picked out?"``Ready to go, boss,” said Bendera.Chakotay nodded. ``We're as ready as we're going to be. Everybody take your positions."\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textbf{Kazon Scout Ship \textit{Maje Gulluh} (Alpha)}\\Neelix had been on the receiving end of Kazon beatings before, but not like this. He'd confessed to everything they accused him of as soon as the words came out of their mouths (including plotting to overthrow the First Maje, collaborating with a Federation invasion, plotting to sell Kazon children to Vidiian organ farmers, theft, murder, treason, smuggling, fraud, and an exhaustive litany of improbable sexual perversions), but they were still keeping it up, and he was coming around to the idea that they weren't going to stop until he was dead. Which, unfortunately for Neelix, whose Talaxian physiology was built to take punishment, would probably be a while.The lead ``interrogator" signaled for the others to stop. Neelix lay in a puddle of blood and piss on a metal floor. ``What's the matter?" said Neelix. ``Did your arms get tired?"The lead interrogator, an especially nasty Deputy Maje named Arzak, laughed. ``Don't think I don't know what you're trying to do, junkman. You're trying to goad me into shooting you and putting you out of your misery. Well, you've been so cooperative, I suppose I can spare you this one small mercy."And before Neelix had a chance to object or change his mind, Arzak withdrew his pistol from its holster, aimed, and fired two rounds...into Neelix's left shoulder.It was like a bomb went off in his left arm. Neelix screamed curses in Kazon and Talaxian and three other languages. The Kazons just laughed.After a while, shock started setting in and the pain faded enough that Neelix stopped screaming. Arzak took the opportunity to ask him more questions. He crouched beside Neelix and held a picture of the alien antimatter valve in his face. “The chief engineer tells me this is an ‘antimatter constrictor valve’. He says that it is a critical component to an antimatter powered warp core. So...who needs it? \textit{Voyager} or \textit{Val Jean}?”``I needed it. For \textit{Baxial}," said Neelix.Arzak sighed, stood up, and stomped on Neelix's shoulder.``Liar! That garbage scow of yours doesn't use antimatter for fuel, Neelix!" shouted Arzak, over Neelix's screams. ``\textit{Voyager} or \textit{Val Jean}?!"“\textit{Voyager}!” he screamed. “\textit{Voyager}’s stuck on Ocampa with engine problems! Please don’t hurt me anymore!”And then, suddenly, there was a blast that threw the Kazon off their feet. The alarms wailed.``\textit{Action stations, action stations! All hands to action stations! We are under attack!}" There was another blast and all the lights went out.Arzak stumbled to an intercom. ``Bridge, this is Arzak! What's happening?"``\textit{It's }Val Jean\textit{! We've lost main power and we're dead in space!}"``Well," said Arzak. ``I suppose you were telling the truth, Neelix." He took his gun back out of its holster. ``I suppose I can put you out of your misery now---"Arzak's words were cut off by a collision, a flying tackle from something short and squat and powerful and still much stronger than him even with only one good arm. Arzak had a moment to be surprised just before his head struck a protruding steel reinforcing rib that turned his brains into pudding. He was dead before he hit the deck.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Val Jean}}\\``Alpha has lost power and propulsion!" said Seska. ``Bravo tracking us with radar."``Going to warp!" said A'sha. \textit{Val Jean} jumped away from the furious Kazons and came to a stop five light-seconds away. ``Coming about, re-engaging warp!"``Full power to forward phasers; target Bravo, fire on my command!" said Chakotay. \textit{Val Jean}'s warp engines pulsed again, and the Maquis were back in the battle space, with starboard hull of scout Bravo square in their sights.``Fire!" said Chakotay.\textit{Val Jean}'s pulse phasers tore into the Kazon scout, but they’d had time to raise their shields and the armor absorbed the rest.``A'sha, warp!" said Chakotay.The whine of the warp engines powering up filled the cabin...and then cut off. An alarm sounded on A'sha's console. ``Warp drive---"\textit{Val Jean} rocked with a hit to the aft shields from a Kazon coilgun. It was small caliber, compared to what the battleships carried, but it did its job against the battle-damaged raider.``Evasive maneuvers! Seska, finish off Beta with aft phasers!"A'sha cranked \textit{Val Jean} into a breakneck turn away from the Kazons' guns as red-orange phaser beams played across the hull of Beta. The shots penetrated, but missed hitting anything vital.``Resetting warp injector controls," said Hogan. ``Now! They're up again!"A'sha lit up the warp drive again and this time it worked, hauling them away just before Beta could tear them to pieces. They came to rest two light minutes away.``Hogan, what's going on?" said Chakotay.``The deuterium injector controller is malfunctioning" said Hogan. ``The last time it did this, it took Torres three days to rebuild it. Captain, we can still go to warp, but we'll need thirty seconds to power up."``That's too long," said Chakotay. ``We can't hang around getting pounded for thirty seconds by those guns."``We can't get pounded by those guns for ten seconds," said Seska. ``The shields are barely at ten percent."``Can we finish off Bravo in ten seconds?" said A'sha.``No, not if they’re ready for us," said Seska. She looked down at the sensor display. ``Oh, and more good news: I think the Kazons sent a distress call. Three more scouts broke off from the main fleet and are coming here fast."``Well, what do we do, then?" said A'sha. ``By the time the shields are up again, we'll have five ships to deal with. Not to mention Neelix will probably be dead."``If we could just buy a little time," said Chakotay. ``Pull a Picard maneuver..."``That won't distract them for long enough," said Seska.``Wait a minute," said Chakotay. ``Wait a minute. I have an idea. Where's Jaxz?"``Right here, sir," said the alien.``That sensor pallet you installed. Can you project a false sensor image with it?"``What kind?" he said.``EM. Radar, infrared, visible light. Gravitic, too, if you can manage it."``EM, yes. EM is easy. But not gravitic. That would take a while to set up."``Never mind about gravitic, then. Can you project an entire fake starship? It doesn't have to be perfect. Just enough to distract them."``Oh, sure!"``All right," said Chakotay. ``Here's what we're going to do."\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textbf{Kazon scout ship Maje Cozak (Bravo)}\\Small Group Commander Sankur shouted into the radio. ``What do you mean you don't know where Arzak is?"``\textit{I'm sorry, my lord. He was interrogating Neelix when we were attacked}."``Send security to find him!" To his own crew, he said. ``We might have to abandon \textit{Gulluh}. Prepare crews to assist the evacuation."``Sir, \textit{Val Jean} is back!"Sankur snapped his head around. ``All weapons, target them and---"``Sir! Another Federation starship is on sensors!" The sensor operator, barely old enough to be a warrior, looked up in horror. ``It's \textit{Voyager}!"Sankur's eyes went wide. ``Alert the fleet! Engine room, prepare for warp!"``\textit{Val Jean} is firing!" \textit{Cozak} shook from the hits. “Dorsal shields collapsed!”``Where's \textit{Voyager}?"``Eighty thousand meters and closing fast."Sankur made his decision.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Val Jean}}\\Bravo’s guns went silent and the raider warped away. A cheer went up across the bridge.``The other inbound scouts just stopped. It looks like they're shifting into a search pattern," said Seska. ``Chakotay, they're looking for \textit{Voyager}'s light cone. They're going to figure out in a hurry that she's not here." ``Any activity from Alpha?"``None. No shields, no power to their weapons, no warp signature, and they have a major radiation leak in their engine room. I'm scanning for life signs...twenty-six Kazon and one unidentified alien. That must be Neelix. He’s in a compartment amidships with...looks like two other Kazons and six more waiting just outside the door."``Can we beam him out?"``Him, sure. But I can’t tell the valve from any other piece of metal on the ship. It could still be on his shuttle, for all I know. We’re going to need him to lead us to it."``Right, I figured as much. Boarding teams, stand by. A'sha, close on Alpha. Seska, lower shields on my mark."``Can we send over any grenades first?" said Bendera. “I don’t think those Kazons outside the door are making a social call.”``Good idea,” said Chakotay.“We’re in position to transport,” said A’sha.“Places everybody, ” said Chakotay.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Maje Gulluh}}\\Neelix lay on the blood-slicked interrogation room floor, using Arzak's body for cover. A shadow moved across the hatch and he fired at it. Kazon security thugs fired back, sending bullets ricocheting around the room. One struck Arzak’s cooling corpse with a wet thump. A second hit one of the other interrogators, lying wounded and moaning where Neelix had shot him. He screamed; Neelix flinched.“Surrender now, Neelix, and I promise you’ll get a fast, clean execution!” shouted the chief thug. “Otherwise we’re going to roast you to death with fire grenades in there.”“There are still two live Kazons in here with me!” said Neelix. “You’ll kill them too!”“Then they’ll have you for a slave in Paradise! Now surrender or burn!”Neelix checked the ammunition indicator on the pistol, and saw he had two rounds left—one to take one last shot at the Kazons outside the door, and one to finish the job on himself. He took aim at the crack in the hatchway.From out in the hall came shimmering blue light and a strange whine, followed almost immediately by a bright flash and the sound of bodies falling to the deck. Six columns of sparkling blue light appeared inside the interrogation room, resolving into six humanoids he didn’t recognize, all holding guns and wearing goggles. They had weapons drawn and one started shouting at Neelix as soon as the blue light faded.“Lower your weapon! We’re Maquis! From \textit{Val Jean}!”Neelix gladly did, tucking the gun into his belt and struggling to his feet. The other Maquis were securing the room. One was inspecting the fallen Kazon just outside.“They’re all dead,” he said. “Don’t know how long until reinforcements show up.”The Maquis leader nodded acknowledgement. “I take it you’re Neelix,” he said. He was scanning Neelix with some kind of small electronic device as he spoke. “My name’s Kurt Bendera. We’ve come to get you out of here.”“What is that thing?” said Neelix.“It’s called a tricorder. It’s a handheld scanner; very useful.”“Can it see that I’ve been shot?”Bendera nodded. “We’ll get you to \textit{Voyager}’s sickbay and let them patch you up. How are you feeling?”“Everything hurts, but I don’t think I’m getting any worse.”``Good. Let's grab that valve and get out of here. Do you know where it is?"``It's probably in the engine room," said Neelix. ``The chief engineer was examining it."``There's a radiation leak in the engine room," said one of the other Maquis. ``We can't transport anything out of there."``We'll have to grab it and haul it clear," said Bendera. ``\textit{Val Jean}, this is Bendera. Neelix thinks the valve is in the engine room. Beam him back and---"``Wait!" said Neelix. ``I know the layout of the engine room. I can find it faster than you."``You don't have to risk it. You've got no skin in this," said Bendera.``I owe the Kazons something," said Neelix. ``Come on. I've been in the Army. I know how to use a gun."The Maquis glanced at each other. On some hidden signal from Bendera, one tossed Neelix one of their energy weapons.``How does this work?" said Neelix.``Just point it and shoot. The beam will last until you let up on the trigger. Try not to shoot yourself in the foot---you'll be dead before you even feel it. Got it?"``I hope so," said Neelix.``Good enough," said Bendera. ``All right, form up! I'm on point; Neelix, you're behind me. Souder cover our backs. Everyone else fall in between. I want to be back on \textit{Val Jean} in three minutes."The Maquis formed up. Bendera scanned the hallway with his tricorder, and, satisfied there was nobody waiting for him, lunged out. Neelix scrambled after him, followed by the rest of the Maquis. They rushed down the dark, smoky passageway, Neelix stumbling over obstacles the Maquis could see and avoid with their low-vision goggles. A luckless Kazon stumbled out of a hatchway in front of them and was blasted by Bendera before Neelix could even level his raygun.Neelix suddenly heard more raygun fire behind him. He looked back and saw Souder firing up the passageway at some unseen target. An alarm klaxon sounded. ``\textit{Intruder alert! Security to main passageway aft! Engineering prepare to scuttle the ship!}"``Shit," said Bendera. ``Let's move!"They rushed up to the hatch to main engineering hatch, gunning down two crewmen emerging with weapons drawn.``The scuttling panel is in engineering," said Neelix. ``We don't have much time."Bendera nodded, raised his gun, and fired blindly through the engine room hatch, forcing the Kazons inside to take cover. Then he dove through.Neelix lunged through the hatch after him. There were emergency lights on, and in the murk, he saw the chief engineer of the ship, already looking sick and pallid from the radiation leaking from his damaged engine, unlocking a control panel. Neelix raised the gun and aimed center of mass.Gunfire echoed in the engine room and Neelix crumpled in agony.\begin{center}\rule{3cm}{0.4 pt}\end{center}As the other Maquis fired on the Kazons who'd shot Neelix, Lon Suder spotted the Kazon Neelix had been aiming at. He had his back to the Maquis and was working inside a control panel. Suder blasted him; the Kazon disintegrated. Cardassian weapons, like his stolen phaser rifle, didn't have stun settings. More Kazons screamed and fell as the other Maquis cut them down. Suder, for good measure, blasted the panel.Bendera knelt beside Neelix. ``He's hurt bad! Where's that fucking valve?"Jonas searched through the drawers of what appeared to be the chief engineer's desk. He snatched the valve out and held it up. ``Got it!"``We have to move forward for beamout," said Bendera. ``Jonas, Dalby, grab Neelix. Suder help me clear the way."``No problem," said Suder. He took position behind cover with a line of sight through the engine room hatch, firing blasts at onrushing Kazon crewmen. He kept firing even when they turned to run away.``Go go go!" said Bendera. ``\textit{Val Jean}, we're advancing out of the engine room. I'll take point. Suder, cover our backs."The team advanced up the blacked-out passageway. Phaser blasts provided the only light. They heard more blasts and shouting coming from further forward, where the second team had beamed in as a diversion. Suder was the last out of the engine room, and closed the hatch behind them.``\textit{That's it, you're clear}," said Seska. ``\textit{Hold still for beamout.}"Bendera turned to check on Neelix and the \textsc{acv}. A Kazon warrior appeared from around a bend. He and Suder fired at the same time. Suder hit the Kazon and vaporized him. The Kazon hit Bendera in the chest.``Energizing!"\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Val Jean}}\\The engine room team re-materialized with one engine part and two bodies. ``Medical emergency!" shouted Dalby. Seska, who was just arriving in the transporter room, staggered at the sight of all the blood on the transporter pad. ``There's no way we can help them here," she said. She slapped the intercom panel. ``Chakotay, we have to get back to \textit{Voyager}! Now! Tell them we have their engine part \textit{and} casualties."``\textit{Warping now}," said A'sha.``Come on, help me," she said. They cleared the other Maquis off the pad and stretched Neelix and Bendera out flat. Bandages, hyposprays, and dermal regenerators accumulated on a neat pile to her right. Seska scanned them both.``How bad is it?" said Dalby.``They both have severe internal injuries," she said. ``We can slow the bleeding, but they're going to die if we can't get them to a real sickbay. Come on." She looked down at the blood-caked engine part.Neelix's ship had been parked right in \textit{Voyager}'s shuttlebay just yesterday. \textit{If Janeway had her fucking act together, none of this would have happened.} Seska glanced over at Suder, still holding his Cardassian phaser rifle. Their eyes met.\textit{If she wasn't our only chance to get home...}\textit{Val Jean} raced back to Ocampa as fast as her engines would carry her.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textbf{\textit{Wrath}, en route to Ocampa}\\``That fucking \textit{cunt}!" bellowed Jabin. ``That fucking cunt and that fucking ship! How could Janeway have possibly escaped Ocampa without us noticing?"``She couldn't have!" said the radio operator. ``Our advance probes are covering every escape angle. Unless \textit{Voyager} can make itself invisible, it couldn't possibly have taken off without being seen."Jabin clenched his fists and tried to calm down. Screaming wasn't going to find Janeway. ``What's the disposition of our forces?"``Scout Group Seven is still hunting for \textit{Voyager}'s light cone, approaching \textit{Maje Gullah}. \textit{Maje Cozak}'s subspace transponder reports they're approaching the main fleet at faster-than-light. No sign of \textit{Voyager} or \textit{Val Jean}."``I want to speak with Group Seven."``Putting them through now," said the operator. The frightened face of some junior officer appeared on the telescreen.``Report!" said Jabin.``\textit{Val Jean} left \textit{Maje Gulluh} twenty minutes ago, my lord. \textit{Gullah}'s account is very confusing. They claim they were boarded by heavily armed aliens, but \textit{Val Jean} never docked with them and it's too small to carry boarding shuttles. They've taken massive casualties. Deputy Maje Arzak is dead. They want to know why \textit{Maje Cozak}abandoned them."``What about \textit{Voyager}?"``We never saw \textit{Voyager} on any of our sensors, my lord."Anger was building in Jabin again. ``Get me Group Leader Sankur. On video."The young Kazon captain's face appeared on a video screen. ``This is Sankur. How may I serve you, Lord Jabin?"``Transmit your sensor logs to Wrath. And tell me what was on \textit{Maje Gullah} that was so valuable to \textit{Val Jean}."``Nothing, my lord, except Neelix."``Was it a rescue attempt?"``I don't know, my lord. We made a tactical withdrawal before the boarding action."``That's an interesting choice of words, Group Leader. Did Neelix have anything or know anything that would have helped \textit{Voyager}?"``I can't imagine what, my lord."Jabin hissed. ``Really? Because I can. The rodent sells spare spaceship parts, you idiot! Was he carrying any with him when he was arrested?"``I overheard on the radio that he had an antimatter control valve."``I see," said Jabin. \textit{That's a warp engine part...but }Val Jean\textit{'s warp engine obviously works.}``My lord, I have \textit{Maje Cozak}'s sensor logs," said the operator.``Find me the part where \textit{Voyager} shows up."He did, and Jabin studied the tracks. The visible light, infrared, and radar signatures all looked like \textit{Voyager}...but the gravitic sensors were blank.``Tell Sankur I want his gravitic sensor logs, too."``He claims he sent them," said the operator.Jabin stared at the flat line on the gravity sensor.``Small Group Leader Sankur, would you please summon your first officer?"``Of course, my lord." He disappeared off screen for a few moments, and returned with his deputy, a man who looked rightfully terrified to be summoned before an angry Maje.``What's your name, Deputy Small Group Leader?"``Sorzar, Lord Jabin."``Sorzar, do you have your personal weapon with you?"``Yes, Lord Jabin."``Good. Kill Small Group Leader Sankur and take over command of his ship."``What?" said Sankur.``It was a trick, you idiot! \textit{Voyager} was never there! Sorzar, I'm not going to ask you again."``My lord, wait---"Sorzar placed the barrel of his gun against Sankur's head and pulled the trigger. Sankur dropped.``Thank you, Small Group Leader Sorzar. \textit{Maje Cozak} is your ship. I suggest you put it to better use than Sankur did."``I will, my lord. Thank you, my---"Jabin cut off the signal. ``All ships, make best speed for Ocampa."Razik waddled onto the bridge. ``What's this I hear about an execution, Maje Jabin?"``I had Small Group Commander Sankur shot for cowardice and stupidity."Razik grunted. ``I’m going to hear about that one from my daughter-in-law. Sankur was her brother."Jabin tried to get him focused on the task at hand. ``\textit{Voyager} never left Ocampa. We'll be on top of it in half an hour."``And \textit{Predator}? Is he ready?"``Oh yes," said Jabin. ``\textit{Predator} is ready."\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Voyager}}\\``\textit{Val Jean} is inbound," said Kim. ``Four minutes to transporter range."Janeway sat in the captain's chair, sweat soaking her uniform. It was over fifty degrees on the auxiliary bridge. ``Where are the Kazons?" said Janeway.``Practically right behind them, captain."Janeway nodded and tapped her commbadge. ``Engineering, are you ready?"``\textit{Everything is prepped and ready to go}," said Carey. ``\textit{As soon as we have the piece, we'll install it}."``How soon until we have warp power after that?" said Janeway.``\textit{We can button the warp core up quickly, but it will take twenty minutes to warm up the dilithium matrix.}"``Twenty minutes?!"``\textit{I'm sorry, captain. That's as fast as it's physically possible to do it.}”``Understood, engineering. Sickbay, we have two gunshot victims with severe internal bleeding on the way. Four minutes and counting."``\textit{Sickbay is ready, captain}," said the Doctor, his voice as cool and monotone as ever.``Transporter room, what's your status?"``\textit{Ready, captain. But we can't do anything with the shields up}."``I know, transporter room. Mr. Kim, bring repulsors online."``Yes, ma'am."\textit{Voyager} started shaking as the antigravity lifts built up power. There was a shudder, and suddenly \textit{Voyager}'s nose lurched up.``That's it, helm," said Janeway. There was another shudder and the stern came up, too. \textit{Voyager} rose rapidly out of the canyon.``Retracting landing gear," said Kim.``Helm, get us into takeoff attitude. All hands, this is Janeway. Brace for liftoff."\textit{Voyager}'s nose tilted up again, up to forty-five degrees, as steep an angle as the repulsors could manage. She hung for a moment in the scalding air.``Engage impulse," said Janeway.There was a blast like a bomb, and then a steady deafening roar that drowned out a thousand alarms. \textit{Voyager} rocketed through Ocampa's atmosphere on a pillar of fire.``Helm, take us to fifty kilometers and level off!" bellowed Janeway. At fifty kilometers above the surface, the temperature and pressure were almost Earth-normal, low enough to risk lowering the shields for a transport.``\textit{Voyager}, this is \textit{Val Jean}," said Chakotay. ``We're dropping warp in ten seconds."``Roger, Chakotay," said Janeway.``The Kazons are right behind them," said Kim. ``They're converging on almost the exact same point. I think they have a pretty good idea where we were hiding, ma'am."``You might be right," said Janeway. ``Tactical, load torpedoes. Let's give them something to think about when they drop warp."The bridge doors slid open. ``Permission to enter the bridge, captain," said Tuvok.``Granted," said Janeway. She patted the empty first officer's chair.\begin{center}\rule{3cm}{0.4 pt}\end{center}“You lied to her,” said Torres. “It’s not physically impossible to start the warp core faster than twenty minutes.”“It is if you don’t want to blow the ship apart,” said Carey.“Not true. You could--- ”“No,” said Carey. “I’m not doing it. That’s only ever worked once, and they were ridiculously lucky they pulled it off. I’ve spent three days trying to put this spaceship back together and I’m not going to blow it up now to save twenty minutes.”“We might not get twenty minutes,” said Torres.“We’ll worry about that if we have to.” He glared at her, and then added, ``And don't you dare try suggesting it to Janeway, either."\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Val Jean}}\\Ocampa reared out of the blackness and exploded onto \textit{Val Jean}'s viewscreen as A'sha dropped the raider out of warp.``I see \textit{Voyager} on scan," said Seska. ``Kazons right behind us. Dropping warp...here they come!"``On screen," said Chakotay.Seska switched to the rear view camera. Fifteen battlewagons and twice that many scouts were less than one thousand kilometers behind \textit{Val Jean}.``Captain!" said Seska. That was all she had time to say before four photon torpedoes went screaming by \textit{Val Jean}, struck the lead Kazon battleship, and completely blew it apart.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Wrath}}\\Razik and Jabin stared in disbelief and horror as four antimatter missiles struck the battleship \textit{Revenge} and destroyed it in seconds.``This was a mistake," said Razik.\textit{They can't have that many missiles}, thought Jabin. ``All battleship, return to warp!" said Jabin. ``Rendezvous on the far side of the moon! Scouts, find the source of those missiles!"\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Val Jean}}\\Janeway's opening salvo had driven the battleships away, but someone had guessed (rightly) that \textit{Voyager} couldn't afford to use photon torpedoes against scouts. \textit{Val Jean}darted and weaved and desperately tried to avoid their fire.``Come about mark zero three five!" shouted Chakotay. ``Lock phasers on target India and fire as soon as you have a shot!"``Hogan, I need more power to the phasers!" said Seska.\textit{Val Jean} rocked with a hit from behind.``Bogey on our tail," said Seska. ``Aft phaser offline; I can't scrape him off."``Hogan, max power to aft shields," said Chakotay. ``\textit{Val Jean} to \textit{Voyager}."``Voyager \textit{here}," said Janeway.``I could use some fire support."``\textit{We'll give away our position if we do.}"``If you don't, we're going to die," he said.Beat. ``\textit{Stand by, Chakotay.}"``Stand by? What the fuck does that mean?!" said Seska.A phaser beam swept up from the clouds and cut the chasing Kazon scout in half.``Oh," said Seska. ``That."``Oh, no," said A'sha. ``I think they found her."All but a handful of Kazon ships started ignoring \textit{Val Jean} and started firing missiles into Ocampa's atmosphere.``Detecting high concentrations of plutonium-238 and uranium-235 in the missile warheads," said Seska. ``Those are nukes."``Target them!" said Chakotay. ``Janeway, you have a nuclear strike inbound on your position."\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Voyager}}\\``\textit{...nuclear strike inbound on your position}."``Dive!" said Janeway.\textit{Voyager} heeled over and plunged back towards the troposphere.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Wrath}}\\``The scouts have \textit{Voyager} targeted. They're diving back into the atmosphere."``All battleships, warp back to Ocampa," said Razik.On an unwatched viewscreen, the hulk of the battleship \textit{Predator} settled into lunar orbit alone.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Val Jean}}\\\textit{Val Jean} dove into Ocampa's atmosphere behind \textit{Voyager}. Seska reached out with quick, cool phaser shots, just enough to send the missiles tumbling.``We're not getting them fast enough," she said.The missiles weren't shielded and weren't dodging very well, but they were rocketing down at Mach 25. From down below the clouds came phaser shots from \textit{Voyager}, swatting more away, but they weren't whittling their numbers down fast enough, either.\textit{We're not going to get a chance to lower our shields for transport}, thought Chakotay. \textit{Even if they survive this, the Kazons will never give us enough time for that}. ``Hogan! You need to think up a way to transport through shields!"``Ripple the shields. It'll open a millisecond hole. It'll be enough to get one person through."``We have two people to send," said Chakotay.``That's the best I can do, captain," said Hogan.``Chakotay, the battleships are back," said Seska.``Take us into the troposphere, A'sha," said Chakotay.``We won't last long down there," said Seska.``We won't last long up here, either." He watched the missiles close on \textit{Voyager} on his screen. ``If \textit{Voyager} is still here in ten seconds, open a channel."\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Voyager}}\\\textit{Voyager} plunged into Ocampa's nightmare atmosphere, missiles closing in. Janeway gripped her armrests with sweating hands and wished there was something she could actually \textit{do}.``Three missiles closing in," said Kim. ``Five seconds to impact!"A shot from \textit{Val Jean} blew one of the missiles away. \textit{Voyager} nailed another with a snap burst from the short emitters on the back side of her saucer. The final missile burned in clean.``All hands, brace for impact!" said Janeway.The missile's warhead detonated a kilometer above them. \textit{Voyager}'s shields were seared by a blaze of hellish light. An instant later came the blast wave, striking \textit{Voyager}'s entire dorsal profile, crushing the ship like the hammer of God.On the bridge, the crew was tossed around in their seats. Something behind the forward bulkhead exploded, spraying the helmsman with shards of burning plastic. He screamed and fell to the deck.Janeway waited a beat for the helmsman's backup to take over, only to realize there weren't any backups left. ``Bridge to sickbay! Medical emergency!" she shouted. With nobody at the control, the ship pitched aft, dragged down by the weight of the warp coils. She was very close to falling ``off" her repulsor beams and plunging ass-first all the way to the ground.``Is there anybody on this bridge who can fly a starship?" she said. When she got no response, she bolted forward, swept the remaining burning bits off the panel and the chair, and took the helm herself. \textit{Voyager} bucked and shook as she tried to get her stable again.``Voyager, \textit{this is Chakotay. We're diving to your altitude. We're going to make a pinhole in our shields and beam the part and a casualty through.}"``How do we open a pinhole in the shields?" said Janeway.``\textit{You have to ripple the shields just the right way}," he said. ``\textit{Do you have anyone who knows how?}"\textit{Gombe would}, she thought. So would three or four others, all dead. It was a struggle to think and try to control the ship at the same time; \textit{Voyager} had the aerodynamics of a bread truck.``I can do it, captain," said Tuvok.``Take the tactical station," she said.The bridge doors hissed open and three sickbay orderlies ran in, including Tom Paris. She looked down at the helm panel. \textit{Why not?} she thought.``Paris! Can you fly a starship?"``Yes ma'am," he said.``Get over here and take the helm!"Janeway stood up to let Paris take the controls. For an instant, there was a look of panic on his face as he scanned the panel, and Janeway thought she'd just made a mistake. But then his fingers started dancing across the controls, and \textit{Voyager}'s flight settled down.``Chakotay, this is Janeway. We have our flight stabilized and Tuvok can pinhole the shields. Get that part down here before the Kazons try to nuke us again."\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Val Jean}}\\``You heard the lady," said Chakotay. ``A'sha, get us closer. We're not going to have a lot of bandwidth and there's a ton of electrical interference in this atmosphere."High above them, in Ocampa orbit, the Kazon battleships began firing their coilguns down into the atmosphere, aiming for \textit{Voyager}. They looked like thunderbolts on the main viewscreen.``We're flying into that," said Seska.``It looks like the shells are burning up," said Chakotay.``They have to have ammunition designed for a situation like this," said Seska. As soon as her words were out of her mouth, the shellfire stopped.``What happened?" said A'sha.``They're reloading," said Seska.``Jaxz, give them something else to shoot at," said Chakotay. ``Seska, this is going to be a tricky transport. I want you at the controls. I'll pinhole the shields."``Yes, captain," she said. She hurried off the bridge. Chakotay took her place.Fourteen battleships left. \textit{Voyager} didn't have enough photon torpedoes to stop them all, and \textit{Val Jean}'s phasers wouldn't penetrate their armor. \textit{Voyager} needed to get main power back online, or they were all going to die. He considered, for a moment, just warping off and abandoning them, leaving them to the tender mercies of the Kazons while the surviving Maquis figured out the next step on their own.He remembered the offer he'd tried to convince Janeway to make. \textit{Val Jean} was packed with goodies that would be worth a fortune to Razik...\textit{And he'll never, ever honor any deal you make}. Chakotay had spent enough time listening to the promises of Cardassian guls and Federation admirals to know a liar when he saw one.``We're closing in on transporter range," said A'sha.\begin{center}\rule{3cm}{0.4 pt}\end{center}Down in \textit{Val Jean}'s transporter room, they had Neelix and Bendera laid out side by side. The blood-caked \textsc{acv} was resting on Bendera's stomach, ready to beam over with him.``We're going to get you out of here, Kurt," said Seska.``\textit{Twenty seconds, Seska}," said Chakotay.``Acknowledged," she said. ``Transporter powered up and standing by."Bendera's eyes opened. He tried to speak, but Seska couldn't hear him. He beckoned her with one finger. She rushed by his side.``What is it?" she said. ``Are you in pain?"He struggled for breath. ``Don't try to speak," said Seska, but he ignored her.``What about him?" he said. He gestured, ever so slightly, at Neelix.``We'll send him down next," she said.``Only one chance," he said.``That's not true," she lied. Of course they weren't going to get another shot. Any moment, the Kazons would start raining shells on them again.Bendera was fighting not to pass out. ``Kurt, just---"With a sudden burst of strength, he picked the valve off his chest and put it on Neelix's.``Kurt, what the hell are you doing?" she said. She reached for the valve.``No. Him first," said Bendera.``Ten seconds, Seska," said Chakotay.``Kurt," said Seska, reaching for the valve again.``He saved us," he said. “They were going to set off a scuttling charge in the engine room. If it hadn't been for Neelix, we all would have died.”Her hand hung over the valve. She knew Bendera didn’t have the strength to give it to Neelix a second time.“Please, Jiasha,” said Bendera. “We owe him that much.”``\textit{Seska, we're in range! Are you ready? Where the hell are you?}"Seska dashed back to the controls. She watched the instruments, and when the moment came, Neelix and the valve dissolved. A moment later came the confirmation signal from \textit{Voyager}. And then \textit{Val Jean} banked hard and pushed to full impulse, rocketing away from \textit{Voyager}.``A'sha, what are you doing! We have another transport left!"``\textit{The Kazons are shooting at us again!}" she said.``\textit{Seska, get back up here}," said Chakotay. ``\textit{We'll beam the alien over later if we can}."She looked over to Bendera. He smiled faintly at her. Then his eyes fluttered shut.Seska cursed Janeway and pounded the transporter controls.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Voyager}}\\The streams of information, energy, and particles that had been and would be Neelix and the valve squirted through a microscopic hole in \textit{Voyager}'s shields, into a transport receiver, through \textit{Voyager}'s own transporter system, and then diverged, rebeamed to their respective destinations. Neelix materialized on a surgical bed in Sickbay, where a baffled Doctor (who had been told to expect a human) had to figure out a dying alien's physiology in the three or four minutes of life it had left. The valve went to main engineering, materializing on a platform by an open warp core maintenance hatch, where the old valve, already pulled, lay nearby.B'Elana Torres snatched it up along with her adapters and scooted into the crawlway. Luckily, \textit{Voyager} was a brand new starship, and the warp core's components hadn't had time to become radioactive yet, so she could work in the access tunnel without a radiation suit.\textit{Voyager} rocked and bucked in Ocampa's air. Unbeknownst to her, Tom Paris was on the auxiliary bridge, trying to make a 100,000 ton starship dodge shellfire from the Kazons like a runabout.Torres didn't bother trying to clean the blood off the valve (\textit{Whose blood?}, she thought). It took three minutes to attach the socket adapters and several other adapters that would allow the valve to receive power and computer control from Federation systems. It took another two and a half to insert it. She worked with speed and grace and silence. She could have done it with her eyes closed.``It's in!" she shouted when the last connection was made. She tossed her tools down the tunnel and slithered out after them. Vorick was already at the warp system master controls.``The forcefield is operational," said Vorick. ``We have an intact supply line to the intermix chamber."``Good job, people," said Carey. ``Vorick, start the warming cycle. Bridge, this is Carey."``\textit{Janeway here}."``You'll have warp power in twenty minutes. Start the clock."\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Val Jean}}\\The crew of \textit{Val Jean} didn't have time to celebrate the good news.``Attack pattern Chakotay Sigma," said Chakotay. ``Oscar is primary! A'sha, watch the sky; we're getting pinged by tracking radar!"``They're not reacting to the decoys I'm broadcasting," said Jaxz. ``I think they've figured out the trick."``Just jam them," said Chakotay.There was a crash and an explosion and suddenly \textit{Val Jean} was tumbling. ``Direct hit to the impulse reactor!" said Seska.``Fire in the engine compartment!" shouted Hogan.Two Kazon scouts took phaser hits from below and disintegrated. ``Val Jean\textit{, this is }Voyager\textit{. We're climbing to torpedo launch altitude. We'll try to cover you}."``Negative, \textit{Voyager}. We're taking too many hits; we have to pull out. We'll try to get back in the fight as soon as we can."Chakotay never saw who launched the missile. All he knew was that without warning, A'sha threw \textit{Val Jean} into a dive. That saved them from the worst of the blast, but when the nuke went off, they still took enough of it to knock out their shields for good.``Antimatter containment failure!" screamed Hogan. ``Ejecting the warp core and antimatter pods!"And with that, \textit{Val Jean} lost power for the last time. As \textit{Voyager} had nearly done, she tipped over backwards with the weight of her warp coils, and plunged into the toxic abyss.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Wrath}}\\``Hit to \textit{Val Jean}! They're in free fall!"Jabin clicked on the all-fleet radio circuit. ``\textit{Voyager} is trying to climb high enough that the air doesn't crush their antimatter missiles," he said. ``Don't let them." He turned to Razik. ``Another nuclear strike---"``No," said Razik. ``We might still be able to salvage something."Jabin didn't get angry; he'd expected it. He noticed that as soon as \textit{Val Jean} lost power, all the phantom spaceships and sensor ghosts that had been plaguing the fleet had vanished for a moment. He wondered if \textit{Voyager} had the same ability. If enough of the wreckage of either ship survived, he was going to make sure Ogla engineers learned the same trick.``I have \textit{Voyager} bracketed with the main guns," said the weapons office.``Fire!" said Jabin.\begin{center}\rule{3cm}{0.4 pt}\end{center}\textit{Voyager} had been taking Kazon shell hits for several minutes. Even with her shields badly weakened, she'd held them off, and the Kazons either couldn't or wouldn't put together another coordinated nuclear strike. Janeway was starting to think they'd get out of this after all.``\textit{Val Jean}'s in trouble," said Kim. ``She's lost power and she's falling fast."``Life signs?"``I can't tell. I think the Kazons are trying to jam our sensors."``Captain, I can get close enough to beam them out," said Paris.``If we do that, we won't be able to launch torpedoes," said Tuvok.``Tuvok, they're our friends!" said Paris.``In the time it takes us to rescue them, the Kazons will certainly destroy us both."Janeway said nothing. \textit{They just saved our lives!} she thought.She imagined Chakotay standing next to her. \textit{You're not going to have your cake and eat it too. You can't save us.}``Maintain course, Mr. Paris," said Janeway.Later she'd think if \textit{Voyager} had turned, she might have gotten out from underneath \textit{Wrath}'s guns.The Kazon heavy shell was made of depleted uranium and weighed nearly half a ton. It blew through \textit{Voyager}'s dorsal shields like a bullet through a soap bubble, through the entire thickness of the saucer, and out the other side.On the way through, it obliterated the power junction supplying electricity to the repulsors. The backup tried to take over, exploded in a shower of sparks thanks to unrepaired fire damage, and died. The repulsors shut down. \textit{Voyager}, she of the bread truck aerodynamics, started falling like one.\begin{center}\rule{3cm}{0.4 pt}\end{center}Torres felt and heard the hit down in engineering. Seconds later, \textit{Voyager} was falling.``Impulse status!" shouted Carey.``Impulse propellant pumps are not responding," said Vorick.``\textsc{warning! unrecoverable failure in the repulsor system. two minutes to crush depth.}"``We've got to get the warp drive online!" said Torres. ``It's our only chance!"``We've barely started the warming cycle!" said Carey. ``We'll blow the ship apart!"``Not if we do a Scott restart!"``I told you once already, no! Do you know how many times that's ever worked?!"``Once!" said Torres. ``So what? If the ship blows up now, what's the fucking difference?"The noise of the rushing air outside the hull was building. They were tilted ninety degrees backwards; if the artificial gravity failed, they'd all smash themselves on the far bulkhead.``That's not the only thing! Even if it does work...."``What?! Even if it does work, what?"``We'll go backwards in time!" shouted Carey.``\textit{Who cares?!}" shouted B'Elana.``I believe the logic of her position is inescapable, sir," said Vorick.“Fine,” said Carey. He tapped his commbadge. ``Bridge, we're going to attempt a controlled implosion. Stand by for warp power!"\begin{center}\rule{3cm}{0.4 pt}\end{center}Ensign Wildman was still at her post even as \textit{Voyager} fell. She touched her belly. \textit{Sorry about all this}, she thought.Something flickered on the screen---a thermal bloom far below. \textit{Val Jean}? No, \textit{Val Jean} was still in the air. It was coming from one of the towers.``Captain, something's happening on the planet," she said. Nobody was listening.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Wrath}}\\``\textit{Voyager} is falling, my lord," said the weapons officer. ``Ninety seconds to impact."``Should we let them enjoy their final plunge?" said Razik.``No," said Jabin. ``If they escape us again while we are gloating---."``I take your point," said Razik. ``All ships, target \textit{Voyager}. You may fire when ready."The sensor operator piped up. ``My lord, another Federation starship just dropped out of warp. They're right on top of us!"``It's another one of their fucking tricks," said Jabin. ``Target \textit{Voyager} with main guns and---"The three photon torpedoes struck \textit{Wrath} amidships.\begin{center}\rule{3cm}{0.4 pt}\end{center}\noindent\textit{\textbf{Voyager}}\\``\textit{Stand by for warp power!}"Janeway held on to her armrests with a white knuckle grip. ``Mr. Paris," she said, over the building noise of the falling spaceship, ``set course zero mark zero, warp one on my command."``Setting course dead ahead, aye captain."``Captain, we are being pinged by Kazon targeting radar," said Tuvok. ``All fourteen battleships are charging their primary weapons."\textit{Well, this is it, Kathryn}, thought Janeway.``Captain, there's another starship approaching at warp!" said Kim. ``It's...it's a Starfleet ship! \textit{Intrepid} class, dropping warp right in the middle of the Kazons!"``On screen!"High above them in orbit, a Federation starship, identical in appearance to \textit{Voyager} swooped in on the Kazon fleet, wrecked a battleship with three photon torpedoes, then tore into another with phasers.``Captain, I'm detecting major thermal, electrical, subspace, and seismic activity on the surface!" said Wildman. ``It's...it's everywhere! The entire planet is lighting up!" There was a sound like amplifier feedback, coming from everywhere and nowhere, rising in volume around them.``\textit{Bridge, warp drive ready!}," said Carey.``Punch it!"\begin{center}\rule{3cm}{0.4 pt}\end{center}Torres held her breath as the valves and gates opened and \textit{Voyager}'s warp core surged back to life. There was the whine of the warp drive building power, and then suddenly \textit{Voyager} was moving faster than the speed of light.``We did it!" she said. The engineers broke into cheering and applause. Torres looked over her shoulder and spied the ship's chronometer. It was running backwards.``Engineering to bridge, we did it!" said Carey.``Lieutenant, I think you need to take a look at this," said Rodriguez. He was pointing at a display panel.``What's the problem?" said Carey.\textit{Voyager} shuddered hard enough that B'Elana had to grab a handrail to stay upright; the red alert klaxon howled. Carey and Torres rushed to Rodriguez's station.``Oh, shit," said Torres."'Oh shit' is right," said Carey. ``Bridge, this is Engineering. We're in a resonance cycle with our own warp field---" He grabbed the panel as \textit{Voyager} shuddered again. ``Stand by, I'll try to break us out of it."``\textit{Do you want us to drop warp?}" said Janeway.``No!" said Carey and Torres together.Carey clarified: ``If we drop warp without breaking the resonance, it will tear the ship apart."``\textit{Understood}," said Janeway.``All right," said Carey, ``this is bad, but let's not panic. Let's see if we can choke back---" shudder "---the plasma stream and weaken the field strength. Vorick, soften the SIF and let the ship flex at bulkheads four, twelve, and nineteen."Torres tuned him out. A temperature gauge had caught her eye.``Lieutenant, what's the normal operating temperature for your reactor?" she said.``Where?"``In the reaction chamber walls."``Ten million kelvin at the force field boundary, thirty-five hundred in the wall structure itself."``You're at four thousand," she said.``Residual heat from the implosion," he said.``I don't think so," said Torres.``\textsc{warning! coolant pump b failure. insufficient coolant to reactor core intermix chamber}."``This is why you're supposed to run a level one diagnostic on the system before you restart the warp core," said Carey. ``Rodriguez, Vorick, get ready to try to break the resonance. Torres, find out what's wrong with the pump. Engineering to bridge, we have a new problem."\textit{Voyager} shuddered, harder than before, and then bucked violently. Carey looked to Rodriguez.Rodriguez shook his head. ``We're still in the resonance, sir."Torres's fingers danced across the Okudagram that controlled the engine coolant system. The hot plasma in the reaction chamber never touched the reaction chamber walls, but the radiant heat would melt them if there wasn't enough coolant flowing through.``\textsc{warning! reactor coolant system overpressure}."``Torres, what the hell are you doing? Reduce the flow volume before you blow the coolant lines!"``Wait!" said Torres. ``The coolant---"Carey reached over her shoulder and turned down the flow himself. ``God damn it, when I give you an order---"A new alarm sounded almost instantly. ``\textsc{warning! core temperature critical! three minutes to intermix chamber integrity failure!}"``You idiot!" said Torres. ``We were already under flow!"``That doesn't make any sense! How could we be over-pressure and under-flow at the same time?" said Carey.``The coolant is boiling," said Vorick. ``The vapor voids are inhibiting coolant flow and raising the system pressure."``It's a positive feedback loop," said Rodriguez. ``The more vapor, the less efficient the coolant system, and the less efficient the system, the more the coolant boils."``And lowering the fucking coolant pressure just boiled a shitload more of it," said Torres. ``Good job, Mr. Professional Engineer."``\textsc{warning! reactor coolant system failure imminent. two minutes to intermix chamber integrity failure}."``Rodriguez, try the high pressure coolant injectors," said Torres.``Already did," said Rodriguez. ``It didn't have any effect. If we do it again, we'll burst half the coolant pipes."``I didn't think," said Carey, to nobody in particular. ``I'm sorry, I didn't think."The doors to engineering slid open. Janeway walked in.``Captain," said Carey, composing himself.``What's going on?"``We're two minutes from a warp core breach if we can't shut the reactor down," said Carey.``Then we don't have any choice," said Janeway. ``We have to drop warp."The engineers didn't respond.``Right?" said Janeway.``She's right," said Torres. ``We have a better chance of breaking warp safely than we do of running the reactor any longer without a breach."``There are a few more things we can try to break the resonance," said Carey.``\textsc{warning! one minute thirty seconds to warp core breach}."``Maybe you should try them soon," said Janeway.Carey, Rodriguez, and Vorick took their stations. After a moment of frenzied button-pushing, \textit{Voyager} bucked and rolled.``Shit!" said Carey. ``Vorick, cut it off."``This isn't going to work," said Torres to Janeway. ``You have to order them to drop warp."Janeway tapped her commbadge. ``All hands, all hands, prepare for hull breach. Take shelter in internal compartments and locate the nearest emergency vacuum gear locker. Mr. Kim, raise all the emergency forcefields that still work."``\textit{Yes ma'am}," said Kim.\textit{Voyager} shook and bucked again. Something blew out and started venting steam into the engine room.``\textsc{warning! hull stresses exceeding design maximums. hull failure imminent}."``That's enough, Mr. Carey," said Janeway. ``Prepare to shut down the warp drive."``Captain, we still might---"``Just do it, Mr. Carey. Now!"Carey froze for a moment, and Janeway drew in a breath, prepared to relieve him on the spot.``Mr. Rodriguez," he said, ``shut down the reaction feed pumps."``Yes, sir," said Rodriguez.Rodriguez's fingers played over the main control board. For a breathless instant, nothing happened.The shock that followed knocked everyone off their feet. \textit{Voyager} shook like a train running off the rails.Janeway grabbed a handrail, trying to pull herself to her feet. She could see Carey shouting orders, but couldn't hear him over the noise.A short, young, female crewman with close-cropped blonde hair dashed into the control area, seemingly unaffected by the buffeting and rolling of the deck beneath her feet. She took up a station between Carey and Torres and began working the controls.Gradually, \textit{Voyager}'s vibrations settled down, until the ship was was running smooth and silent. The red alert siren stopped.``We're in an unpowered warp glidedown," said Carey, sounding like he couldn't believe his own eyes. ``We'll be at sublight in ten seconds."``What the hell just happened?" said Janeway.``Our own warp bubble was trying to tear the ship to pieces," said Carey. ``And then somehow, we just surged out of it. Then we just coasted to a stop."```Somehow?'" said Janeway. ``That's the best you have?"``It's the best \textit{I} have," said Torres. ``How the hell did...? Captain, we should all be stone dead right now."``What else is new?" said Janeway.``\textit{Paris to Janeway. We just dropped warp}."``Where and when are we?" said Janeway.``\textit{We're...we're in the Ocampa system Oort cloud. Captain, we were only doing Warp 1. That's only light speed. I don't know how---}"``I know how fast Warp 1 is. What day is it, Mr. Paris?"``\textit{Stardate 48302}," said Paris.``That's three days before \textit{Val Jean} arrived here," said Torres. ``Holy shit."``Any sign of the Kazons?" said Janeway.``\textit{None nearby}," said Kim.``\textit{Captain}," said Tuvok. ``\textit{I have analyzed sensor logs taken just before we departed Ocampa. I have identified the Federation starship that attacked the Kazons as} \textsi{uss} Voyager."Janeway looked around. Everyone was obviously at least as confused as she was.``Say again, Tuvok," said Janeway.``\textit{The Federation starship that attacked the Kazons was} \textsi{uss} Voyager. \textsi{ncc}\textit{-74656}."``Well," said Janeway. ``That's interesting, isn't it?"Motion at the corner of her eye drew Janeway's attention. She turned and saw the blonde crewman---with alien ears, Janeway realized---casually walking away from the control station.``Wait a minute," said Carey. ``What's your name? Why aren't you wearing a commbadge?"The alien ignored him. Carey stepped towards her, intending perhaps to physically stop her. Without looking at him, the alien grabbed Carey by the collar with one hand and shoved him away.``Intruder alert," said Janeway.The alien suddenly stopped walking. She made a half turn toward Janeway, froze, and then collapsed.``Sickbay, this is engineering," said Torres. ``Medical emergency!"``What the hell is going on here?" said Carey, dragging himself back to his feet.``I don't know," said Janeway. She crouched close beside the unconscious alien. ``Who are you?" she said.\chapter*{Part IV}
\noindent\textbf{-7 Days}\\The conference room was packed; Tuvok and Carey, Torres and Wildman, Harry Kim, the Doctor via video conference, other officers standing around the edge of the room, and Janeway at the head of the table wishing for a stiff drink and a twelve-hour nap. Everyone was talking at once. She slapped the table for attention. ``One at a time!" she said. ``Tuvok, you first." ``A few moments before we warped away from Ocampa, a Federation starship appeared in orbit and attacked the Kazon fleet. I have confirmed beyond any reasonable doubt that that starship was \textsc{uss} \textit{Voyager}, \textsc{ncc}-74656." ``How could that be?" said Torres. ``Isn't it obvious?" said Kim. ``We went back in time six days. We must have repaired \textit{Voyager} and then attacked the Kazons." ``Don't you mean 'we \textit{will} repair \textit{Voyager} and attack the Kazons'?" said Wildman. ``Yes," said Kim. ``Or no. I don't know." ``The event is in our own future and our own past," said Janeway. ``Ugh, I swore to myself if I ever became a captain, I'd never let myself get caught in one of these godforsaken paradoxes. The past is the future, the future is the past; it all gives me a headache. Tuvok, I don't suppose you can think of any good reason for us to charge back into that battle after we worked so hard to get away from it the first time." ``Captain, at the time the future \textit{Voyager} arrived, we were being tracked by Kazon fire control radar. We were, quite literally, only moments from annihilation." ``They weren't going to wait for us to hit the ground, were they?" said Janeway. ``It did not appear so. The evidence strongly suggests that our future actions enabled, and will enable, our past escape." ``Well that's just great," said Carey, ``Except we didn't hang around long enough to see how the Kazons reacted...will react...to us. We have one nacelle, a hole the size of truck clean through the saucer, no outside support, and a handful of spare parts. We're not going to be battle ready in six days or six months." ``We still have twenty-six photon torpedoes," said Janeway. ``Which aren't enough to wipe out all the Kazons, even if they did give us time to fire them all," said Carey. ``When our alternate selves engaged the Kazons, we specifically engaged and destroyed one battleship," said Tuvok. ``It may be helpful to know why." ``Somebody had to be first," said Carey. ``Perhaps," said Tuvok. ``However, there is no particular reason that ship had to be chosen. Captain, I would like to examine our sensor logs to determine if there is anything unusually important about it." ``It was probably their command ship," said the Doctor. All heads turned to the comm screen. ``Why do you say that?" said Janeway. ``Can you think of a better target for a surprise attack?" said the hologram. ``No," said Janeway. ``No I can't. And if we're going to have a chance against the other thirteen battleships, then wiping out their command and control would be a good start. Now, Carey, Torres, what exactly happened down in Engineering?" ``One of the primary coolant pumps failed," said Carey. ``Without it, we couldn't cool the warp core sufficiently. Standard operating procedure in that situation is to drop warp and shut the core down until until the pump can be repaired." ``But we couldn't drop warp because of the resonance," said Janeway. ``So what happened next?" ``We shut the drive down to prevent a breach. The resonance almost tore the ship to pieces. Then that alien just showed up," said Torres. ``She stepped right up to a control panel and then..." ``Then what?" ``I don't know!" said Torres. ``I've been over the logs and I still don't know what she did." She folded her arms across her chest, as if she was put off the alien had improvised better than she could. ``She manipulated the warp field somehow," said Carey. ``She altered the power flow to the field coils. That much we know. But the field form she created...I think we'd need a detailed mathematical analysis to understand it. Not to mention, she knew our systems well enough to manipulate the warp field in the first place. That's...very impressive on its own. If you beamed me over to, say, a Romulan warbird and told me to mess with their warp field, I wouldn't even know which buttons to press." ``I would," muttered Torres. ``And nobody knows who she is or where she came from," said Janeway. ``She's not in our personnel files," said Carey. ``And she is not Maquis," said Tuvok. Every head turned to the doctor again. ``Well," said Janeway, ``what can you tell us?" ``She does not match any entry in the Federation database." ``What's her prognosis?" said Janeway. ``I cannot say with any certainty. Her internal organs are functioning properly, to the best of my ability to determine. She shows no sign of any injury. Her brain is active. But she is in a vegetative state; she is awake but not aware." ``Is there anything you can tell us about her? Anything unusual?" said Janeway. ``Yes. Her empathic lobes are hypertrophied, suggesting potent telepathic potential. And despite the fact she appears to be a young adult, evidence from her bones and teeth suggests she is under two years old." ``Do we know of any other humanoid species that grow up that fast?" said Janeway. ``I could find none in any Federation medical database. Captain, her genes show markers indicative of extensive genetic tampering." ``By whom?" ``Unknown. It would take months of study to determine which proteins the tampered genes code for, and even longer to determine the macro-scale effects. Without knowing that, it's impossible to speculate what purpose the genetic changes may have had." ``Has Neelix regained consciousness yet? Does he know anything?" ``He is still under sedation," said the Doctor. ``I would prefer not to wake him for at least another twelve hours." ``Neelix?" said Torres. ``How did he get here?" ``He beamed over with the \textsc{acv}," said Carey. ``The Kazons shot him full of holes." Janeway waved her hand to cut off the side chatter. ``All right," said Janeway. ``Alert me and Ensign Wildman immediately if she wakes up." ``Captain," said Wildman. ``Just before we went to warp, there were major energetic disturbances on Ocampa's surface," said Wildman. ``They were centered on the towers. Captain, the planet is obviously part of the Caretaker's mechanism somehow. Maybe it's not a coincidence the alien arrived at around the same time." ``Well, she's not one of ours and she's obviously not Kazon. I guess the Caretaker makes as much sense as anyone," said Janeway. ``Maybe she \textit{is} the Caretaker," said Kim. Janeway closed her eyes and rubbed her temples. The Doctor's special wake-up blend was wearing off fast. ``Maybe, but I somehow doubt it." ``What about an avatar?" said Wildman. ``I cannot confirm any such speculation at this time," said the Doctor. ``Then we'll speculate later," said Janeway. ``After we have more information. Carey, Torres, did we damage the warp core any more?" ``Nothing we can't repair," said Carey. ``We were able to shut it down before there was any permanent damage to the dilithium matrix." \textit{Some good news for once}. ``All right. Whatever we decide to do, we're going to need a working ship to do it. Ensign Wildman, until our guest wakes up, I want you to keep working on the Caretaker. Did the Kazons send anything useful, or is it all porn?" ``I think so," said Wildman. ``I've seen some of the early returns. The computer is scanning the rest for viruses; it should be ready soon." ``Good. I want your whole team on it. Doctor, do you have all the staff you need?" ``What I need is another surgeon and at least four nurses. For basic first aid and assistance, however, the staff I have is adequate. \textit{If} Mr. Paris is returned to me." ``Done," said Janeway. ``Tuvok, I want you running the bridge. Watch the scope and if anyone hostile shows up, sound the red alert. Kim is on ops. Pick whoever else you need to staff it. Everybody else---and I mean everybody else---is on damage control duty. Mr. Carey, that's your responsibility. I'm officially naming you my second in command." ``Captain," said Carey, ``are we sure we should leave a Maquis in charge of the bridge?" \textit{He's not---} said Janeway's brain. A little strangled noise was all she managed to say. ``We don't have time to worry about distinctions like that. If anyone objects, they can take it up with Starfleet Command." ``Yes, Captain," said Carey. ``Captain Janeway," said Torres. ``Yes?" ``What happened to \textit{Val Jean} in the battle? What's their status?" There were uncomfortable glances around the table. Tuvok cleared his throat. ``\textit{Val Jean} impacted the planetary surface at mission time ninety-six hours, fifty-one minutes, nine seconds, at approximately the moment we engaged our warp drive," he said. Torres sagged into her seat, dumbfounded. ``Tuvok, why didn't you \textit{tell} me?" ``They were...they were already gone when they hit the ground," said Janeway. ``There were no life signs on board. They were caught in a Kazon nuclear blast." ``The end must have been swift," added Tuvok. ``When we get home," said Janeway, ``I promise you that everyone in the Federation will know about the crew of \textit{Val Jean}'s bravery and---" Torres's head snapped upright. ``Wait a minute. Wait a Goddamn minute here! We're in the past! We traveled backwards in time! None of this has to happen this way. Why don't we just get the warp drive running, drop in on \textit{Jabin} before he knows we're here, and blow him away before \textit{Voyager} even arrives?" ``That would cause a paradox," said Kim. ``If we destroy Jabin's ship before \textit{Voyager} arrives, then our past selves will have no idea who he is or why we should destroy him in the first place." ``It's more fundamental than that," said Wildman. ``If the Kazons didn't force us to hide on Ocampa, or blow away the antigravity lifts, we wouldn't have tried a Scott restart to begin with. We would have never gone back in time." ``Practically any change to the timeline would result in us never traveling through time," said Janeway. ``We can't risk a paradox." ``Why not?" said Torres. ``Who cares about a paradox? There's dozens of lives at stake." ``Starfleet regulations on interfering with the past are ironclad," said Janeway. ``We cannot take it upon ourselves to `edit' history, even our own. I won't violate the Temporal Prime Directive any more than I will the original Prime Directive." ``I can't believe what I'm hearing," said Torres. ``Dozens of people---real people, people who helped you when they would have been better off leaving you to the Kazons---are going to die if you don't help them, and you're sitting around this table talking about \textit{Starfleet regulations}. You owe them, Janeway! Every one of you owes them!" ``I can't, B'Elana," said Janeway. ``I'm sorry." ``How many times in your life have you wished for a chance to fix all your mistakes? Well, now you have one, and you're going to piss it away over a bunch of philosophical bullshit that doesn't matter. The Prime Directive is horseshit, Janeway! It’s horseshit!" ``That's enough, B'Elana," said Tuvok. ``For God's sake, Janeway, how many of your own people have died since you got here? Even if you don't care about Maquis, what about your own crew?" Janeway shot to her feet. ``That's enough!" she said. Torres stood, purple-faced, ready to shout. ``Perhaps a short break is in order," said the Doctor. ``Good idea," said Janeway. ``Ten minutes." The group stood to stretch, moving around the table and clumping together by crew---Kim, Wildman, Vorick and Carey in one corner, Tom Paris with Torres in the other, trying to calm her down. Tuvok hung back, watching as Janeway left. \begin{center}\rule{3cm}{0.4 pt}\end{center} Janeway had been sitting alone for five minutes in a darkened biology lab when the door hissed open and Tuvok stepped inside. ``Captain?" ``In here," said Janeway. ``Tuvok, give me one good reason why I shouldn't have B'Elana Torres strangled and dumped into space." ``She is a skilled engineer. We will need her, if we are to have any chance against the Kazons." ``The worst part of it is, I agree with her. The `Temporal Prime Directive' sounds like a great idea when you're sitting in an Academy classroom. Now I'm trying to figure out what `great consequences to history' I'm supposed to be risking, and I'll be damned if I can see any." ``The consequences may be to us. Captain, paradoxes, by definition, cannot logically exist. If the past can indeed be changed, they must be resolved. I fear that the likeliest resolution to any paradox involving \textit{Voyager} would be the destruction of \textit{Voyager}." ``Yeah," said Janeway. ``That could be a problem. But she's right---I owe Chakotay. Is there anything we could do? Any way to beam them out before the crash?" ``Not without being seen by ourselves and the Kazons. I'm sorry, captain." Janeway closed her eyes. She thought back to her conversation with Chakotay, about dealing with losing crew. She wondered if it stretched to allowing death, by inaction. \textit{Haven't you done that already? You didn't try to rescue them when you had the chance. Why is this any different?} ``Captain," said Tuvok. ``I confess I did not follow you here to offer advice." ``Oh? What for, then?" ``I would like to mind meld with the alien in sickbay." Janeway straightened up. ``Why?" ``Because our only way home is through the Caretaker, and she is our best hope of understanding it." ``When do you want to do it? I have no idea when she'll wake up and---" ``I do not wish to wait until she wakes up." ``You want to mind meld without her consent?" ``I am aware of the ethical issues involved," said Tuvok. ``Then you know she has a right to her own mind," said Janeway. ``The needs of the many outweigh the needs of the one," said Tuvok. ``I thought some things were always wrong," said Janeway. ``Like lying." ``Certain Vulcan philosophical schools subscribe to that viewpoint," he said. ``You might call them deontological. Others are more strictly utilitarian." ``Kant versus Mill," said Janeway. ``Bentham would be a better analogy," said Tuvok. ``Though human philosophy has not yet approached the deeper nuances. I don't suppose you have been introduced to Vulcan thinkers on these subjects." ``It's been a while," said Janeway. ``You might find a fresh reading rewarding," said Tuvok. Janeway dismissed him with a wave of her hand. ``Maybe later. I take it you subscribe to the more utilitarian school of Vulcan ethics." ``I do," he said. ``Well maybe I don't," she said. ``It's a serious invasion of her privacy, and I'll remind you that so far, all she's done for us is save the ship. How great an evil are you willing to tolerate in exchange for getting one hundred and thirty people home sooner?" ``At all," said Tuvok. ``Excuse me?" ``The proper question is, 'how great an evil are you willing to tolerate in exchange for getting one hundred thirty people home at all'? Captain, you must have considered by now that we will not be able to find a way home on our own. We may be entirely dependent on the Caretaker's will to return home." ``And you think forcibly reading the mind of its 'agent' will convince it to help us?" ``To this point, it appears nothing else has." ``Give me time to think about this," said Janeway. ``There is not much time left," he said. ``We have days until we can act. She could wake up on her own, for all we know." ``Or she could die. We know nothing about her or how serious her condition is." Janeway paced. She was impatient for information, desperate to solve at least some of the riddles that had been accumulating since they'd arrived. ``Give Wildman and the Doctor a chance to study her and the Caretaker first. If she is its agent or avatar or whatever, it might not appreciate us intruding on her privacy without permission." ``As you wish," he said. His tone, face and body language were unreadable. She was pretty sure that was Vulcan for ``I disagree, but I am bound by the chain of command not to say so." ``Meanwhile, I have another project for you," said Janeway. ``You're to work with Torres, Paris, Wildman, and Carey and find a way to rescue \textit{Val Jean}'s crew without altering history." ``That will be...exceptionally difficult," said Tuvok. ``I know. I want you to try anyway. Torres is right---I owe Chakotay my ship and my crew. And besides," she said, ``If I order Torres to find a way to rescue them, she won't try to freelance and maybe get us all killed." Tuvok said nothing for a moment. He seemed to be studying her, though for what she couldn't know. Finally, he nodded slightly. ``Wise," he said. \begin{center}\rule{3cm}{0.4 pt}\end{center} Neelix woke up that evening. He was sitting up on a sick bed in a hospital gown when Janeway and Tuvok arrived to talk to him. He had the v-neck of the gown pulled down so he could examine his chest. ``Is there anything wrong, Mr. Neelix?" said the Doctor. ``If I was shot in the chest, where's the scar?" said Neelix. ``After I removed the bullet and repaired the internal damage, I sealed the bullet hole with a dermal regenerator. There should not be any scarring." ``You...you just fixed me up?" ``Yes. That's why more advanced civilizations prefer energy weapons. The damage is harder to repair." ``How's he doing, Doctor?" said Janeway. \textit{He needs a name, she thought again}. ``He'll live. His blood pressure has returned to normal and his internal organs are recovering to their normal functional levels." ``What happened to you?" said Janeway. ``The Kazons shot me." ``Did they have any particular reason?" said Tuvok. ``We were stealing back the part you needed." ``Do you remember what happened after you were shot?" ``Just a lot of screaming and shooting. What happened? I guess \textit{Val Jean} made it back to Ocampa." ``\textit{Val Jean} transferred you here once they knew the extent of your injuries," said Janeway. ``Did the valve work?" ``Yes," said Janeway. ``Without it, we never would have made it." ``Well," said Neelix, ``I'm glad I could help, then. Listen, I don't suppose you could pick up my ship and give me a ride out of here? There's a neutral planet sixty light-years from here that you could drop me off at. I don't think I'm going to be too popular with the Ogla from now on." ``The situation is complicated at the moment," said Janeway. ``We have to lay low for a while before we go anywhere." ``How long is a while?" ``Seven days," said Janeway. ``What for?" ``We've traveled backwards in time." ``I think something's wrong with your magic translator," said Neelix. ``I could have sworn you just said we've gone backwards in time." ``It was an accident. We have to lay low until we catch up with our 'present'." Neelix pondered that. ``Could I make a couple of calls? Tomorrow I'm going to blow six hundred crowns on a pile of counterfeit duotronic logic boards, and I'd like to tell myself to leave them for the next sucker." ``Did anyone attempt to talk you out of making the purchase before?" said Tuvok. ``No," said Neelix. ``Then I'm afraid you can't," said Janeway. ``I'm sorry, we can't risk making any changes to the past." ``I had to ask," said Neelix. ``So I'm stuck here for now." ``The Kazons abandoned your ship intact. Once all this is settled, we'll recover it for you. In the meantime, you're welcome to enjoy our hospitality." ``Forgive my...well, my rudeness, captain, but it doesn't sound like I have much choice." ``You may choose not to enjoy it," said the Doctor. Janeway shushed him with a handwave. ``There is something you could do for us," said Janeway. ``If you don't feel like you've already done enough." ``Oh?" said Neelix. ``Doctor, can the patient walk safely?" ``If he takes it easy," said the Doctor. ``Come with me. I want to show you someone," said Janeway. Neelix scooted off the bed and followed Janeway to the furthest bed down the line. There lay the comatose blonde alien. ``Have you ever seen this species before?" said Janeway. Neelix leaned in close, focusing on her ears. ``I...I don't think so. Not in person, anyway." ``But you've heard of others from her species?" ``No," said Neelix. ``Definitely not." ``Why not?" said Tuvok. ``Because her species is extinct." \begin{center}\rule{3cm}{0.4 pt}\end{center} ``I'm sorry, Captain," said Wildman. ``I don't know how I missed this." ``You missed it because you weren't looking for it. Nobody was." Janeway shook her head. ``Are we sure of what we are seeing?" said Tuvok. ``You tell me," said Janeway. ``Do you think it's just our imaginations?" ``No," said Tuvok. ``Me either," said Janeway. She stared at the image on the computer screen, a sharp grayscale image from a Kazon scientific probe, of a ruined Ocampa palace or temple or some other monumental structure, exceptionally well preserved on the dead, waterless surface. A line of bas reliefs marched around the temple pediment, a procession of gods or kings in elaborate robes and tall Egyptian crowns. The figures were all in profile, and every one of them had the same ears as the alien lying comatose in \textit{Voyager}'s sickbay. ``So now we know what the Caretaker is taking care of," said Janeway. \begin{center}\rule{3cm}{0.4 pt}\end{center} \noindent\textbf{-6 Days}\\Torres was staring out the mess hall windows, utterly ignoring Wildman as she blathered about dumb Starfleet bullshit. Outside, beyond the sweep of \textit{Voyager}'s primary hull, was the gray-black landscape of the Oort cloud object the ship had landed upon. It had taken Torres fifteen hours of nonstop work to restore power to the ship's repulsers---Janeway had flatly refused Paris's offer to land the ship on thrusters alone. Torres had wanted to name the iceball after Janeway (``in honor of your inspirational leadership, Captain"), but Janeway had turned her down and named it, in a fit of imagination run amok, New Pluto. In retrospect, she thought Janeway might have seen through her sarcasm. ``So what do you think?" said Wildman. ``Huh? About what?" ``About my idea." ``What idea?" ``Haven't you been listening at all?" she said. ``Just summarize it for me." ``I suggested we recalibrate the main deflector dish to emit a stream of..." \textit{Oh God}, thought Torres. "...which would create an ion sheath in the atmosphere that would shield us from detection." ``Is that it?" said Torres. ``Yes," said Wildman. ``It stinks," said Torres. ``Perhaps the discussion would be better served with more constructive criticism," said Tuvok. She rolled her eyes. ``Okay, fine. Yes, technically, we'd be hidden from detection inside the ion sheath. The problem is, once we hit the atmosphere, the ion sheath would create a fireball the size of Finland, and I'm pretty fucking sure everyone in the solar system would be able to detect \textit{that}." ``How do you know it would create a fireball?" said Wildman. ``Because I've tried it before! Don't you think I wouldn't have tried that with \textit{Val Jean}? Every trick there is to hide a spaceship, if it works, I used it on \textit{Val Jean}, and if it doesn’t work, I tried it anyway." ``Well then why don't you make a suggestion once in a while instead of just sitting around pouting and badmouthing everyone else?" snapped Wildman. ``Because all my friends are dead because of you people, and this meeting is a waste of time. The only way to save them is to do what I told Janeway---fuck the space-time continuum, fix the ship, and go kill all the fucking Kazons before they know what even hit them." ``If you do not feel this committee is not a good use of your time, you're free not to attend," said Tuvok. ``The captain assigned you to it based on her belief you would be motivated to help our colleagues, but if that belief if mistaken, you are free to go." ``Oh, blow it out your ass, Tuvok," said Torres. ``Why aren't you giving Tom this line of sanctimonious shit? He didn't even bother to show up." ``I expected much more out of you than I did Tom Paris," he said. ``I'm going for a walk," she said. She got up and stormed out. She walked fast without running, trying to keep a purposeful look on her face. She knew from experience she was least likely to be bothered this way---look too casual, somebody might find a job for you; look too rushed, and somebody might ask what's wrong. She looped once around deck four, got back to the mess hall door, still didn't feel like going back, took the turbolift down one deck and started a circuit there. She didn't think, just walked. She'd never thought on these excursions; she'd long learned being alone with her thoughts was bad company. The passed the holodecks. The doors were locked open; the holodecks were deactivated, of course, but they were left open as ``recreation" rooms. She heard a steady thump from number two as she walked by. She glanced in to see Tom Paris bouncing a racquetball off the holodeck wall. She debated walking by unnoticed, but before she could, he glanced over his shoulder and spotted her. ``Tuvok send you to find me?" he said. ``Tuvok doesn't give a shit about you," she said. ``I just bailed." He smirked. ``Realized what a waste of time this is, huh?" ``Oh, shut up," she said. She drifted onto the holodeck. ``At least I've been doing work. What the hell have you been up to the last two days? This?" ``You wanna trade? I'll turn a wrench and you can do graves detail." ``Don't be such a fucking martyr," she said. ``It's not like you knew any of these people." He turned away from her and bounced the ball off the wall. She caught it the second time and bounced it back to him. ``Tom, we have to do something," she said. ``We have to save \textit{Val Jean}." ``Like what? If we can't find a way to do it without being seen, Janeway won't let us." ``I can take care of Janeway," she muttered. ``That would make Carey the captain. I thought he hated you." ``I can take care of him, too." ``What are you going to do, kill everyone until it's just you and me left? There's some Klingon strategic thinking for you." ``You are such a racist piece of shit," she said. ``What's your idea, then, smart guy?" ``Who said I had an idea? I think it's hopeless." ``If we had a cloaking device," said Torres. ``That would solve our problems." ``Yeah, probably," he said. ``You never got one of those working, though, did you?" She didn't respond right away. ``...did you?" he said. ``I tried buying one first, but the deal fell apart at the last minute and we barely got away with our asses. Then I tried to build one. I got close, but I could never keep subspace emissions bleedthrough under control. We always got picked up on sensors." ``Modern sensors,” said Tom, bouncing the ball again. ``As modern as the Maquis can scrounge up, anyway.” “What about older gear? Radar, ladar, infrared. \textsc{em} stuff. Could you hide from that?” “Probably, but what good does that do?” “That’s all the Kazons will have after \textit{Earhart} blows up their \textsc{ewar} ship.” She started nodding. “Right. You’re right. They’re subspace blind, and with \textit{Voyager}’s computers and shields I can hide our \textsc{em} signature. It would be a primitive cloak, but it might be enough.” ``What do you need?" said Paris. ``If you were going to build a cloaking device, what would you need?" ``I'd need to check the inventory for the parts. And I'd need direct access to the shield system, software and hardware." ``You don't already have that?" ``Defensive systems aren't supposed to be my specialty," said Torres. ``And Carey doesn't trust me. If I go to him talking about monkeying with the shields, he's going to want to know why." ``You have an idea to reinforce them," he said. ``That falls apart the minute he sees what I'm actually doing. He's going to want to hang over my shoulder the whole time. I can't go through Carey without giving away what I'm trying to do, and I promise you he won't let me if he knows." ``Then why not just go right to Janeway?" said Paris. She shook her head. ``Why not? Don't tell me you're too proud to ask her for help." ``If I thought there was a chance in hell she could actually help me, I would. But she’ll never listen to any of my ideas, not after that meeting. If I go to her, all that will probably do is warn Starfleet that the Maquis are trying to build a cloak.” ``Well, what about Tuvok, then? Let him pretend it's his idea." Torres shook her head again. ``Oh come on," said Paris. ``Why not?" ``Something...something's not right with Tuvok," said Torres. ``I don't trust him. He's way too close to Janeway. He's...haven't you noticed how Starfleet he's been acting?" Paris wanted to tell her she was talking crazy, but she was right. He \textit{was} acting Starfleet. He'd never exactly been warm and friendly on \textit{Val Jean}, but this stiff, standoffish, officer's attitude was new. And he \textit{was} spending a lot of time with Janeway. She'd even put him in charge of the bridge.A thought popped into Paris's head, unbidden. \textit{How did Bujold know so much about me and Chakotay?} ``What are you thinking?" said Torres. ``Nothing," said Paris. ``Listen, I have an idea. There's one other person who could give you access to the shields. And I think I could talk him into keeping quiet about it." ``Who?" said Torres. \begin{center}\rule{3cm}{0.4 pt}\end{center} Harry Kim was drinking a synthehol beer in the mess when Tom Paris suddenly appeared at his table, carrying an oblong bag. ``Mind if I sit down?" he said. ``Sure," said Harry. Tom took the chair across from Harry. ``Listen," said Paris. ``I was on debris duty in the forward observation lounge when I found this." He placed the bag on the table and pulled out something Harry instantly recognized---his clarinet, looking exactly as it had the day of the Caretaker disaster. Harry's found himself blinking back tears. ``I thought I'd lost it," he said. ``Then it's yours?" said Tom. ``Yes. It was a gift from my grandparents. My tenth birthday. I thought it got blown out into space." ``I found it at the bottom of a debris pile." ``I can't believe you found it," he said. He raised it to his lips and played an experimental scale. ``The reed isn't even cracked. Thank you so much, Tom. How can I repay you for this?" ``Don't worry about it," said Tom. ``It wasn't anything." ``No, I'm serious," he said. ``Tell me what I can do." ``Well," he said. ``There is one thing. Maybe." ``What is it?" ``Do you know how to access the firmware in the shield control systems?" ``I...guess? What for though?" Paris leaned in close, looking around to make sure nobody else was listening. ``B'Elana has an idea to help us evade the Kazons," he said. ``But Carey doesn't think it will work and he's blocking her. She's not a defense specialist so she doesn't have access to the system." ``Why doesn't she go to the captain?" Tom held up his hands and grinned helplessly. ``You know how women are," he said. ``Ha-ha, sure," said Kim. ``Look, it will only be a few minutes," said Paris. ``No one will ever even know." ``Come on, Tom, you know I can't." ``Harry, you have literally nothing to worry about, okay? Torres will be in and out. If it doesn't work, nobody will ever know, and if it does, no one will care.” ``What is she trying to do?" Tom and Torres had discussed what to do if Kim asked this. Tom had argued it was worth the risk to tell the truth---no Academy-fresh Starfleet ensign was going to break regulations for vague generalities. Well, Tom Paris might have, if he'd survived his plebe year, but plebe year was designed to weed out cadets like Tom Paris. ``She thinks she can build a cloaking device," said Paris. ``If it works, we'll have a huge advantage over the Kazons. And we might be able to rescue \textit{Val Jean} without causing a paradox." Kim sat back in his seat, looking stunned. ``Tom, those are illegal." ``They're illegal in the \textit{Federation}, Harry. And right now, we're seventy-five thousand light years away from the Federation." ``And we can't involve the captain," said Kim. ``Not yet," said Paris. ``If you don't help us now, we can't do it." Paris watched Kim's face as he agonized with the dilemma Tom had left him. ``I'm sorry, Tom. I just can't. Why doesn't she just go to Janeway or Carey? They'd have to recognize what a good idea it is, wouldn't they?" ``She's Maquis, Harry. Starfleet types, they don't listen to crooks like her, no matter how good their ideas are." He corrected himself. ``Crooks like us, I guess." He glanced down at the table. ``Even after Torres saved all our lives?" ``Even after," said Tom. ``That's not fair," said Harry. ``Life's not fair, Harry," said Tom. ``Anyway, enjoy your clarinet." \begin{center}\rule{3cm}{0.4 pt}\end{center} Later, in Torres's cabin: ``Did he buy it?" said Torres. ``It's a perfect replica," said Paris. ``He played a couple notes, said it sounded exactly the same. We're just lucky he beamed his luggage over instead of carrying it on himself."``That was a good idea, recovering its pattern from the transporter." ``How much did you have to drink to admit I had a good idea?" said Paris. ``Shut up, asshole," said Torres. ``Save it for after this plan works. When will Kim get me access? Tonight?" ``Not too much longer, I don't think." \textit{Kim agonizes about it for a few hours, then goes to Janeway and tells her the whole thing. Janeway asks Tuvok about a Maquis cloaking device. Tuvok tells her everything, because either he's thrown in his lot with Starfleet or he's been a Starfleet mole the whole time. Janeway rolls the idea around for a few minutes and decides to go for it, because she's in over her head but she's smart enough to recognize a good idea when she hears it, as long as it's coming from someone she trusts.} \textit{Or if I'm wrong, she locks us both up for attempting to sabotage the ship}, he thought. Whatever. ``When?" said B'elana. ``I don't know. He said he'd let me know." Paris made a show of looking at his wrist, even though he didn't wear a watch. ``I've got a shift in sickbay starting in ten minutes." ``Then you should probably get out of here," she said. ``Yeah, I should," he said. He rolled out of bed and started picking up his clothes. ``This was fun. We should do it again," he said. ``Don't hold your breath," she said. ``Never heard that one before," he said. She balled up his tunic and threw it at him. ``Get out before I decide to knife you," she said. ``You know you're crazy and codependent, right?" said Paris. ``Oh, and you're a fucking paragon of good mental health, right? You need two people to be codependent, you know." He shrugged, finished getting dressed, and left; Torres fell back into bed to wait. She dozed off after a few minutes, and was awakened a few hours later to the chirp of her door chime. ``Come in," she said. The doors hissed open. Janeway walked in. ``Tell me how to build a cloaking device," said Janeway. \textit{Tom, you \textbf{asshole}}, she thought. ``Give me a minute to find my pants," she said. \begin{center}\rule{3cm}{0.4 pt}\end{center} \noindent\textbf{Captain's Log, supplemental.} \\\textbf{It has been two full days since we arrived in the Ocampa system Oort Cloud. Repairs to \textit{Voyager} are progressing. I admit I can only admire the ability and work ethic displayed by Lieutenant Carey in that time, as well as all the crew members working round the clock to make vital repairs. The last of the debris from our ordeal has been cleared and stored on Deck Fifteen, where it will remain until we can turn it over to Starfleet for examination. Most of the ship's compartments have been pressurized again, and those that cannot be have been sealed off from the rest. }\textbf{The bodies of most of our dead have been accounted for as well, and rest in cold storage until they can be returned to their families. I insisted only volunteers be assigned to graves detail, and that personnel are frequently rotated. Nevertheless, the Doctor has reported that some of them are already suffering from depression and nightmares. Unfortunately for us, \textit{Voyager} did not carry a counselor as part of her regular crew complement. The rationale is that \textit{Voyager} was designed for short deployments and didn't need a full-time counselor on board, but it reeks of yet another 'Wolf' cut.} \textbf{The Doctor has now been running for nearly one hundred hours of subjective time. He---it?---insists he is fine operating continuously, but I worry. I wonder if he is too convincing an illusion, too human. Perhaps if they had programmed him to look like an android, I wouldn't worry that a machine could get tired, or bored, or traumatized. For now, I comfort myself by looking at the results, which have been remarkable considering the limitations he's working under. His only concern appears to be our medical supply situation, where we have nearly exhausted several critical medicines. He is concocting substitutes as best he can, but there is only so much he can do---and often the ingredients in the substitutes are other drugs which are also in limited supply.} \textbf{B'Elana Torres has proven invaluable to the engineering staff. I can't say I've forgiven her for her words at the last meeting, but her abilities are impressive. According to Chief Rodriguez, she improvises like a jazz master. With her help, we now have impulse power back online, and she managed to repair electrical distribution node 'B', which allows us to use the antigravity lifts again. And then there's the cloaking device. Of course, just because we have one---assuming she can finish it in time, and assuming it works---doesn't mean our problems are solved yet. We still have the job of figuring out how we're actually going to rescue Chakotay and the gang and fight off the Kazons at the same time. }\textbf{I haven't admitted this to anyone, but I think I actually miss Chakotay's presence. I'm becoming conflicted about what to do, if we can rescue him and his crew. It's my duty to arrest them and turn them over to Starfleet, but prison seems like a pretty lousy thank-you for everything they did for us. I can't see any way around it, so for now I tell myself I'll figure out what to do once we get back.} \textbf{If we get back.} \textbf{My biggest disappointment so far has been in the Caretaker team. It isn't their fault, and they're working as long and hard as anyone on the ship, but they've made very little progress. Ensign Wildman has managed to confirm, using our own observations and what little legitimate information the Kazons sent us, that the towers on the planet's surface are a part of the Caretaker's mechanism. Beyond knowing that they do \textit{something}, however, we have few insights into who the Caretaker is or how his mechanism works, or how Ocampa came to be in the state that it's in.} \textbf{We \textit{have} learned more about the Kazon. It appears that they have placed an automated observatory on the near side of Ocampa's moon. I suppose this doesn't violate the Caretaker's ban on permanent outposts in the Ocampa system. Ensign Wildman has hypothesized that the observatory watches for activity from the towers and broadcasts a signal to a nearby Kazon base; Ensign Kim has identified a likely candidate approximately one and a half light years from here. }\textbf{Tuvok, meanwhile, has been examining our sensor logs from our last battle with the Kazons. As the Doctor (!) suggested, he believes the ship our future selves attacked was Razik's command ship, based on the volume of radio traffic coming to and from it. Tuvok insists that he would have discovered this on his own, eventually, but concedes that it might have taken longer without information from the future. Which strongly suggests that we knew to attack Razik's command ship because we attacked Razik's command ship. I'm not well-versed enough in temporal mechanics to fully understand all the nuances of that situation, but I'm pretty sure I don't like it. We have conjured up information \textit{ex nihilo.}It's superstitious, but I can't help thinking that our account with the universe is now out of balance, and the universe will soon demand we make it whole, with interest.} \begin{center}\rule{3cm}{0.4 pt}\end{center} \noindent\textbf{-5 Days} \\``That's all we have for now," said Wildman. ``No luck with the tachyon scan?" said Janeway. ``Same as before. We can't penetrate the outer skin of the array or the towers." ``All right," said Janeway. ``I have an engineering meeting at 1300; after that I'll join you in the lab to help work on our next idea." Wildman nodded. There were deep dark circles under both eyes and her body language was sagging. She looked inches away from burnout. Janeway turned to Tuvok. ``How's the work on the cloak coming?" ``It will take several more days," he said. ``We're cutting it awful close with this thing. Don't say anything---I know she can't go any faster. Have we thought about how we're actually going to use this thing? Can we transport through it?" ``We can beam something in, but not out, which will work for the purposes of the rescue mission," said Tuvok. ``And we can't fire while cloaked, right? Or can we?" ``I am afraid not," said Tuvok. ``Torres's cloaking device functions by manipulating the shields to mask all emissions. In the process, it becomes impermeable to our own weapons." ``So it helps us with the rescue, but not the battle with the Kazons." ``There may be ways to use it effectively in combat," said Tuvok. ``See what you can figure out," said Janeway. She had her private doubts---the Kazons had to be smart enough to shoot where they \textit{had been} if \textit{Voyager} suddenly disappeared. ``All right, then, as long as we're cloaked, the Kazons probably can't see us. What about ourselves and \textit{Val Jean}?" ``I believe if we take position over the north magnetic pole of Ocampa, the charged particles in Ocampa's Van Allen belt will screen us from casual observation," said Tuvok. ``Is this true, Sam?" said Janeway. ``Well," said Wildman, ``Maybe. We were all paying attention to other things, but the computer should have noticed something unusual. We were getting a lot of weird interference, so maybe that masked it." ``What kind of interference?" said Janeway. ``It almost looked like sensor ghosting, but I couldn't isolate a problem in our system." ``False sensor data, beamed directly into our recievers," said Tuvok. ``It is a deception Chakotay learned while he was in Starfleet. The computer interprets it as another starship. " ``Can we do that to the Kazons?" said Janeway. ``Yes. I am familiar with the technique," he said. ``All right, then we have something else we can use against them." ``I wonder why \textit{Val Jean} was spoofing us," said Wildman. ``It doesn't really make...sense...oh my God. It was us, wasn't it?" ``That would be the logical conclusion," said Tuvok. ``Absolutely nothing about this situation is logical," said Janeway. ``All right, so we supplement the cloak by spoofing our past selves' sensors. That will be Ensign Kim's job; Tuvok, it'll be your job to show him how to do that." ``Yes captain." Janeway rubbed her temples. Still so much to do. ``\textit{Val Jean} will be arriving here tomorrow night, before we have the cloak online. Is there any chance they'll see us?" ``Not with the precautions we’ve taken." ``Good. All right, we have a ton of work to do; let's all get to it." They stood up to leave; Wildman walked out right away. Tuvok dawdled in such a way that she knew he wanted to speak to her privately. ``How close did the Maquis come to a working cloak?" said Janeway. ``Very," said Tuvok. ``Torres nearly succeeded in buying one on the black market before she elected to build it." "'Nearly'?" ``The deal was disrupted by Starfleet Intelligence," said Tuvok. ``Your doing?" He nodded. ``You want to talk to me about the alien again," said Janeway. ``You are more perceptive than you let on," said Tuvok. ``I've been waiting for the other shoe to drop. Give Wildman more time." ``We are running out of time," said Tuvok. ``Don't assume that, if we do learn something from her, we can apply it right away." ``We have four days left," said Janeway. But they didn't. \begin{center}\rule{3cm}{0.4 pt}\end{center} Tom Paris was sorting lab samples when the alarm sounded; he reached the alien's bed at the same time the Doctor activated and dissolved into life. ``She's crashing!" said Paris. ``She is going into anaphylactic shock," said the Doctor, his voice as flat and emotionless as always. "20cc of ephinedren, stat." Paris prepped the hypospray and handed it to the doctor. He injected her. The alarm kept beeping. ``No effect," said the Doctor. ``Should I get another steroid?" ``Her biochemistry is too alien," said the Doctor. ``Prepare 10cc of pseudocortisol." Paris did; again, it had no effect. ``Her airway has closed," said Paris. ``Doc, do something or she's going to die." ``In the lab there is a sample marked \textsc{jd12237}," said the Doctor. ``Place it in the material scanner and replicate 20cc. Do it quickly." ``What are you going to do?" said Paris. ``Trach her. Now please do as I asked." Paris rushed into the lab and found the sample. His hands were shaking so badly he screwed up the order to the computer twice; it was only on the third attempt that it worked. The sample dematerialized and rematerialized in its bottle. ``\textsc{replication in process. please stand by}." said the computer. There was a chirp and suddenly a much larger vial of the sample liquid materialized on the replicator's out tray. Paris loaded it into a hypospray. ``Here," he said, handing it to the doctor. The doctor injected her; Paris held his breath. After a few moments where Paris was sure it wouldn't work, the alien's chest rose and fell. ``She's breathing," said the Doctor. ``Her immune reaction is returning to normal." ``What the hell happened?" said Paris. ``Did you start her on the new antibiotic regime I designed?" said the Doctor. ``Are you saying this is my fault?" ``Answer the question, please." ``Yes, I did. I hooked up the bag you mixed to her infuser exactly when you said I should, and I didn't change anything." ``I am not accusing you of anything, Mr. Paris," said the Doctor. ``The fault is my own. She is allergic to one of the new antibiotics in the mix." ``What was that stuff you injected her with?" ``Steroids derived from a sample taken from her own adrenal glands," said the Doctor. ``Mr. Paris, please inform the captain as to what happened." Five minutes later, Janeway was in the Doctor's office, along with Tuvok, who the Doctor had not invited, but who had become her de facto first officer and right-hand man.``Why is she on antibiotics in the first place?" said Janeway. ``She is developing bed sores, despite our best efforts," said the Doctor. ``I elected to start her on antibiotics to prevent an infection." ``Find another way," said Janeway. ``I have sterilized the isolation bay and placed her inside," said the Doctor. ``That should protect her for the time being." ``All right," said Janeway. ``Have there been any neurological changes?" ``None," said the Doctor. Janeway and Tuvok stood. ``Keep me posted," she said. ``Of course," said the Doctor. \begin{center}\rule{3cm}{0.4 pt}\end{center} Outside the sickbay doors, Tuvok turned to Janeway. ``Captain---" he said. ``Tonight," said Janeway, her voice shaking. ``Do it tonight." \begin{center}\rule{3cm}{0.4 pt}\end{center} Janeway followed Tuvok and two security goldshirts into sickbay. The lights were turned low and other than the alien in isolation, the sickbay was empty. The Doctor was in the adjacent medical lab, studying test results. ``Captain," he said. ``What can I do for you?" ``I am conducting a mind meld," said Tuvok. The Doctor stormed out of the lab to get in Janeway's face. It was the first time she'd ever seen it show any emotion. ``Without the patient's consent? Absolutely not." ``Excuse me?" said Janeway. ``It would be a breach of medical ethics to allow you to do that, Captain. My programming expressly forbids it." ``I'm ordering you to monitor her while we do it," said Janeway. ``My programming does not allow me to obey illegal or unethical orders." Janeway was trying to think of her next argument when Tuvok settled the matter for her. ``Computer," he said. ``Deactivate emergency medical hologram." The Doctor looked affronted. Then it disappeared. \textit{This is crazy}, thought Janeway. ``Tuvok, come with me to the lab. You two wait out here." ``As you wish," he said. They left the ratings behind and went to the medical lab and closed the door. They could still be seen, but not heard. ``Are you certain this is necessary," said Janeway. ``Are you backing out, captain?" “I need to know if this is really our only option. The Doctor recovered her this afternoon---" He wheeled on her, looking as close to angry as she'd ever seen any Vulcan. ``In three days, we have accomplished nothing towards getting home. We have studied data gathered by us and the Kazons. We have fired probes at and into the planet. We have scanned the Caretaker with every functional instrument on this ship. We have virtually begged it directly to help us. After all of that, we have nothing but the vaguest hypotheses and guesses of a single starship's understaffed science department, with no prospects for anything better. This alien is the last unexplored avenue remaining to us, and she nearly died today. What more would you suggest we do?" ``I don't know yet," she said. ``We'll can meet first thing tomorrow morning to figure out our option." ``Captain, the only conceivable purpose of a meeting at this stage is to delay the inevitable. And, perhaps diffuse your own responsibility for a hard decision." ``Every member of this crew took an oath to uphold Starfleet's values," said Janeway. ``To the death, if necessary. If the choice is between violating that oath and spending the rest of our lives out here, then God damn it, that's what we signed up for." ``Are you ready to tell them that?" he said, gesturing at the walls around him. Janeway sagged back. ``No," she said. She was the acting captain, a 29-year old science officer who was only in command because of a freak accident. She couldn't make that decision for the rest of them. ``Your commitment is admirable," said Tuvok. ``It is a fine trait for a Starfleet captain, as I now believe you deserve to be. But pragmatism is just as important a virtue for anyone who wishes to sit in the captain's chair." ``Stop," she said. ``Stop telling me bullshit to make me feel better." She sighed. ``Do it," she said. ``Read her mind." Tuvok nodded. ``Thank you, captain. As the Doctor will not cooperate, will you monitor her vital signs for me?" ``No," she said. ``I'm done with this job. If I can't make hard decisions, I shouldn't be the captain." She walked out of sickbay. Before the doors closed, she heard Tuvok speaking. ``My mind to your mind..." The doors hissed shut and she made for the nearest turbolift, intent on finding Lieutenant Carey and passing off command to him. Tuvok's screams echoed up and down the halls. Janeway spun around and sprinted back to Sickbay. She found Tuvok in a posture like a man being electrocuted, his hands clamped on the alien's temples, while he shook and jerked and bled from the eyes and nose. The alien was sitting upright, staring forward with a blank expression on her face. The two security ratings lay on the deck in the isolation bay, their skin burned and their uniforms smoking. There was a high-pitched squeal, like audio feedback, that was coming from everywhere and nowhere, painfully loud; Janeway's eyes teared from it. Covering her ears did nothing to attenuate it. ``Security to sickbay! Computer, activate emergency medical hologram!" The \textsc{emh} materialized in the middle of sickaby. ``Please state the nature---" ``Over there!" said Janeway. The Doctor strode across sickbay, straight through the forcefield. He grabbed Tuvok's arms. The alien glared at him, and a halo of fire flashed around the Doctor, who shimmered but otherwise ignored it. With obvious great strength, he pulled Tuvok away from the alien. Tuvok collapsed to the floor. The alien screamed and clambered off the table; the wail cut off like someone had thrown a switch and the fire around the doctor went out. Sickbay's door slid open and a team of four security ratings rushed in, still shaking their heads and rubbing their ears. Janeway didn't even know how to start to explain the situation. While they advanced on the isolation bay, the Doctor had the alien cornered. Whatever power she'd had before, it failed her now. He had acquired a hypospray from a medical locker inside the isolation bay. Now he held her still, pressed it to her neck, and supported her while she slumped to the floor. The Doctor turned to examine Tuvok and the two other ratings. ``They're dead," he said, pointing at the goldshirts. ``He's alive," he said, pointing at Tuvok. ``Just barely. I need to perform emergency surgery." The isolation bay forcefield fell. ``Get them out of there," said Janeway. ``Doctor, what about the alien?" ``She will be unconscious for several hours," said the Doctor. ``Put her in a bed with a restraining field," said Janeway. ``What the hell \textit{is} that noise?" ``What noise?" said the Doctor. She looked at him, baffled. ``You didn't hear that?" ``\textit{Bridge to Janeway}," said Kim. ``\textit{Captain, someone just sent a signal from }Voyager\textit{ to the inner solar system}." ``What kind of signal?" said Janeway. ``\textit{Captain, I....ma'am, please don't think I'm crazy.}" ``Just spit it out!" ``\textit{I think it was telepathic, ma'am.}" ``To Ocampa?" she said. ``\textit{Yes, ma'am.}" ``Okay," said Janeway. ``Now we have a new crisis." \begin{center}\rule{3cm}{0.4 pt}\end{center} A few hours later, Janeway assembled what was left of her ``senior" staff and briefed them on what happened. Carey sat at her right hand, watching her speak. The look on his face was that of a man who wanted to appear attentive without actually paying attention; he was clearly waiting for his turn to talk. ``Mr. Carey," she said. ``Ma'am," said Carey. ``You've been the official second in command since we arrived, but as I'm sure you noticed, I gave Tuvok many of the first officer's responsibilities so you could concentrate on your role as chief engineer. As Tuvok is now incapacitated indefinitely, I'm going to have to ask you to step up fully into both roles. I'm aware I'm asking you to do two difficult jobs at once, but that is how it will have to be for the time being." ``You can count on me, Captain," he said. \textit{I'll bet I can}, thought Janeway. \textit{I wonder when you suggest I might step aside `for a little while' to `rest and recuperate'}. Just a few hours before, she'd been ready to put the red uniform on him, disgusted with her own weakness and moral failure. \textit{You'd have done the exact same thing}, she thought. \textit{You'd have done it the minute Tuvok suggested it. You would have been inside that isolation bay with him, and you would have died, and we'd have lost Tuvok and our captain and our chief engineer all at the same time. }She moved to the next item on the agenda. ``B'Elana, your work on this ship has been exemplary. I don't know if what I'm about to give you is exactly a reward, but it's something I should have done already: I'm appointing you to the rank of provisional ensign in the engineering department, with responsibility for propulsion, power, and the cloaking device. You'll be junior-in-grade to Ensign Vorick, but you'll be a formal part of the chain of command." ``Thank you, ma'am," she said. ``Is there any word on Tuvok's condition?" ``The Doctor is keeping him in an induced coma for the next twenty-four hours," said Janeway. ``He's suffered severe burns and some probable brain damage. The Doctor is hopeful he will eventually make a full recovery, but his prognosis is uncertain." Torres nodded quietly and looked back down at her \textsc{padd}. ``Mr. Paris, I'm appointing you provisional ensign as well," said Janeway. ``Your primary duties will be in sickbay, but once we're underway, you're my pilot." ``Thank you, ma'am," he said. His voice and expression were wooden, and Janeway was certain he didn't really want to be Starfleet. \textit{Well, too bad}, she thought. ``I've been up all night developing a plan to rescue the crew of \textit{Val Jean}; unless anyone has a better idea, I intend to implement it four days from now. Once the cloak is ready, we will proceed under cloak to Ocampa and take position above the planet's north pole. The Kazons won't be able to see through the cloak, our past selves will be blocked by the planet's bulk, and \textit{Val Jean} will be too remote and too busy to notice us through the magnetic interference. We'll sit tight through the battle, using Chakotay's sensor-jamming trick to keep ourselves hidden if necessary. When \textit{Val Jean} loses power, we'll initiate a rapid emergency beam out of her crew. Once that's accomplished, we'll warp off under cloak to a position one astronomical unit away, come about, and warp back in. Our primary target will be the Kazon battleship \textit{Wrath}, which we are now confident is Razik's command ship. We'll shoot to cripple and offer terms: send the fleet away or we'll destroy him. We'll warp off to a suitable location and wait to see his reaction. If he takes our offer, we'll offer assistance with casualties in exchange for unimpeded access to Ocampa and the Caretaker for as long as it takes us to figure out how to get home. If he doesn't, we will warp back, destroy \textit{Wrath} and everyone left on board, and start again with the next ship down the line until these primitive assholes get the fucking message." She stood up without warning; everyone else scrambled to their feet. She was starting to enjoy that. ``If there aren't any questions," she said. Nobody had any. ``Dismissed," she said. On her way out, Carey stopped her. ``Captain," he said. ``I know you've been working very hard, and---" ``You can't have my job, Lieutenant, so save your breath," said Janeway. Carey's mouth worked, but no sound came out. Janeway smiled to herself. \textit{Maybe I \textbf{am} more perceptive than I let on}, she thought. ``I was just going to say you could use some rest," said Carey. ``We all could," said Janeway. ``You've got enough to do." ``If I'd been in command this whole time, we wouldn't be in this situation," he said. He looked surprised when he blurted it out, like he had been thinking it but didn't really think he had the courage to say it. Well. ``You're right," said Janeway. ``We wouldn't be in this situation. We'd all be dead or in a Kazon slave market instead. If I hadn't listened to you, we could have had the warp drive up and running before we had to fight fourteen Kazon battleships. Now, you made your recommendation and I followed it, and I'm not blaming you for giving me your honest professional opinion; it was on me to see the bigger situation. But since we got here, you've shown me nothing but condescension and contempt, and it's obvious you think you should be in charge." ``Captain---" said Carey. ``Shut up," said Janeway. ``Shut your mouth and listen. You think you should be in charge because you think I'm some blueshirt pencil-pusher who has no business commanding a starship. Well, obviously Bujold saw it differently, or she would have put you in front of me on the depth chart. And seeing as we're all still alive right now, you know what? She was right. I may be a blueshirt pencil pusher, but this ship is intact and its crew is alive, because of my decisions, not yours. ``Now, we have to work together for the next four days, and maybe for a long time after that. I'd ask you if you think you can work with me, but bluntly, I don't have anyone to replace you with, so I don't actually care about your answer. You are going to work with me, and you are going to accept your part in this, and you're going to do it without backbiting or undermining me, or I promise you, Mr. Carey, when this ship gets back to the Federation, your career in Starfleet will be over. Am I clear?" ``Yes, ma'am," said Carey. He was visibly seething, but Janeway didn't care about that. Let him seethe. As long got the message.\begin{center}\rule{3cm}{0.4 pt}\end{center} \noindent\textbf{-4 Days}\\\textit{Val Jean} arrived on schedule in a blister of space-time warped to the breaking point. She gave no sign she saw \textit{Voyager}. Kazon scouts came screaming into the system and spotted the Maquis; \textit{Predator} followed at high warp and dropped right on top of them in orbit of the planet, while Chakotay was still trying to get his bearings. Jabin was rewarded for his precise, practiced, coordinated attack with a withering phaser barrage from \textit{Val Jean} that forced the scouts to warp off; \textit{Predator} retreated to the outer solar system, also oblivious to \textit{Voyager}'s presence. \textit{Val Jean} hunted down and mauled a third scout; from that point forward, \textit{Predator} was alone. At about the moment \textit{Val Jean} popped out of the Caretaker's space-time blister, the alien in sickbay woke up. The Doctor looked up from his research work and saw her sitting up in the isolation bed. She reached out in front of her and struck a forcefield; she yanked her hand back like it had been burnt. She started feeling around methodically, looking for a way out of the bed; when she'd come a full 360 degrees without finding a break in the field, she threw herself at it. It threw her back harmlessly. At that point, she started to panic. The Doctor stood and approached her bed; she noticed him for the first time and drew back in fright. ``It's okay," he said. He knew he hadn't been programmed to be ``soothing"; that collection of vocal and body-language cues had been left out of his final design specs, but he knew it was important in this situation to try to calm the patient down. ``You are in an isolation bed for your own protection. I am a doctor; I mean you no harm." This did not calm the alien in any way. She started to cry out in an alien language. ``Sickbay to bridge," said the Doctor. ``\textit{We're kind of busy up here}," said Janeway. The alien heard the voice over the intercom and looked around wildly for a second person. ``The alien is awake." ``\textit{We'll be right there}." ``Doctor to Tom Paris." ``\textit{I heard, doc, I'm on my way.} The alien started thrashing against the force field again and crying out. The Doctor picked up a hypospray. ``You are only risking injury by struggling," he said. ``You cannot thrash through the force field." \textit{I hope}, he thought to himself. He approached the isolation bed. She shouted at him in her language; he didn't understand the words, but the meaning was clear enough: ``Keep away". ``I am going to give you a mild sedative," he said. ``It will help you calm down." Across the sickbay, the doors slid open; the sickbay's internal sensors told him it was Tom Paris. ``Computer!" she shouted. ``Deactivate Emergency Medical Hologram!" \textit{How did she know how to do that?} thought the Doctor. \textit{And when did she learn to speak Vulcan?} he added, just before the world went black. \begin{center}\rule{3cm}{0.4 pt}\end{center} By his internal clock, the world reappeared six minutes later. The alien was sitting on the edge of a bed in the middle of Sickbay, with Tom Paris, Captain Janeway, and Tuvok standing around her. Janeway was looking at the Doctor; his internal logs told him she had reactivated him. ``Captain!" he said, alarmed to see the alien out of isolation. ``It's all right," said Janeway. ``She was just claustrophobic." ``Are you sure that's all?" said the Doctor. The alien was staring at him, shivering in fright. Tuvok saw her alarm and whispered something to her. She calmed down, but still glanced uneasily at the Doctor every few seconds. ``I'm glad to see you're awake, Mr. Tuvok," said the Doctor. ``Her name is Kes," said Tuvok. There was a slow and dreamy quality to his voice; the Doctor noticed Janeway and Paris watching him as he spoke. ``As soon as Tuvok woke up, she calmed down," said Paris. ``I've scanned her already; I uploaded the readings to the medical log." The Doctor checked them in his ``mind". ``Body temperature normal, lung function normal, neurological functions normal, heart rate elevated but within normal range," he said. He checked again. ``And the same for Mr. Tuvok." ``I must thank you, Doctor, for your skilled treatment," said Tuvok, sounding more like his normal self. ``And I must apologize for my behavior last night." ``You committed a serious breach of ethics, Mr. Tuvok. ``If you were still a Starfleet officer, I would have to report you to Starfleet Command. As I must do to you, Captain." Janeway nodded gravely. ``I expect nothing less," she said. Behind her, Paris was making an odd face; the Doctor catalogued it as another one of Paris's strange behaviors and ignored it. ``Where is this place?" said Kes. ``Is this \textit{Voyager}?" Paris, Janeway, and the Doctor all glanced at each other. “Yes,” said Janeway. “This is the Federation starship \textit{Voyager}. My name is---” ``Captain Kathryn Janeway,” said Kes. “How do you know this?” said Janeway. “Tuvok, did she learn this when you mind-melded?” “She already knew,” he said. ``The Caretaker told me,” said Kes. “He told me everything.” She looked around her. “I’m Outside, aren’t I?” “I’m not sure what you mean,” said Janeway. “Outside what?” “Outside, the place beyond the world. The place where the Caretaker came from.” “She means space, Captain,” said Tuvok. “The Caretaker told me I’d be going Outside, to a place called \textit{Voyager, }to meet a person named Janeway.” “Why?” said Janeway. “I don’t...I don’t remember,” said Kes. “Something’s gone wrong.” “I’ll say,” said Janeway. “Kes, did the Caretaker tell you why he brought us out here?” “Yes, but I can’t...I can’t remember any of it.” “Well, great,” said Janeway. Kes looked hurt. “Sorry,” said Janeway. “It hasn’t been my week. Kes, can you contact the Caretaker?” “Not until the loop is closed,” she said. “What loop?” said Janeway. ``Captain," said Tuvok, ``Remember our temporal displacement.” “Oh, right,” said Janeway. “So when we return to the time that we left, then we can talk to him?” Kes looked into Janeway’s eyes a facial expression suddenly gone hard. “If you survive,” she said, her voice low and icy. Then, just as suddenly, the look was gone and her normal register returned. ``I'm hungry," said Kes. ``The Caretaker said it was safe to eat your food." ``Doctor?" said Janeway. ``Our standard hypoallergenic replicator menu should be safe for her consumption. If somewhat...uninspiring. I would like to supervise her meal here, just in case." ``Is that what you would like to do, Kes?" said Janeway. ``Yes please," she said. \begin{center}\rule{3cm}{0.4 pt}\end{center} After Kes's uneventful (and, as promised, uninspiring) meal in sickbay, Janeway went with Tuvok back to his cabin. The gravity was Earth-normal but the lights were deep red and the air was hot and dry. He replicated a cup of vile-smelling Vulcan tea; Janeway declined when he offered to make one for her. There were human-designed chairs in the cabin, but Tuvok had shoved them to one corner and arranged cushions around a low table. \textit{Vital scientific equipment and spare parts: left at Deep Space Nine. Vulcan furniture: priority loading. }She silently cursed Bujold again. ``How are you feeling?" said Janeway. ``I am in some pain," said Tuvok. ``It will pass." ``I thought I'd lost you for a while back there," said Janeway. ``I am led to understand it was you who summoned help. I thank you for that, captain." She nodded. ``And...I regret deeply my actions led to the deaths of crewmen Guiterrez and Swanwyck." ``Yeah, well," said Janeway, staring at her folded knees. ``Not the first we've lost." She looked back up. ``But hopefully the last." ``I also apologize I took advantage of your trust in me. Should you wish to discontinue our professional relationship, I will understand." ``I didn't appreciate that," she said. ``But right now I need all the help I can get. Anyway, since you did mind meld with her, we might as well make use of what you learned." said Janeway. ``I saw into her mind," he said. ``I believe the Doctor is right---she has been tampered with. There was a `firewall' between her Kes ego and her body; when we melded, I broke a hole in that wall." ``She was a prisoner in her own brain?" ``I do not believe she was aware of it, but yes, essentially." ``When happened when you broke through?" ``I believe I triggered a defensive reaction. She was as frightened by it as I was. The Kes ego was not in control then." ``You keep mentioning this `Kes ego'. What does that mean?" ``When we were connected, I sensed other personalities lying beneath the personality that calls itself Kes." ``Is she mentally ill?" ``Impossible to say. It is unusual, though not unheard of, for some sentient species to carry multiple `selves' or `personalities' in a single brain." ``Or it could have something to do with the tampering the Doctor found." ``Yes." ``Can you say anything about those other personalities? Were any of them hostile?" ``Not exactly," said Tuvok. ``Most seemed indifferent, or curious. But there was one...I am sorry, captain. I cannot fully describe it." ``Can you try?" ``All I can remember is a feeling of terrible purpose. That is the entity that attacked me." ``Do you remember anything else about it?" ``Yes," said Tuvok. ``We speculated that the alien---Kes---may have been an avatar of the Caretaker. The entity that attacked me was it. I am certain of it." ``And that telepathic broadcast...?" ``It was transmitting a copy of itself to the Caretaker array when the Doctor interrupted." ``How much made it back?" ``I cannot say," said Tuvok. ``All right," said Janeway. ``You rest for now. Do you think you'll be up to helping question her later?" ``Captain, interrogating Kes will teach us nothing. She is barely aware of the other entities inhabiting her mind. Worse, I am afraid I the 'firewall' containing 'Kes' is only partially breached; I am afraid you will find broad gaps in her memory until she can find her own way around it." ``You don't think it's even worth asking?" said Janeway. ``It will cause her distress and teach us nothing," said Tuvok. ``You've formed some kind of connection with her, haven't you?" said Janeway. ``I have," he said. ``I cannot fully describe it, but I know it is there. I find it...somewhat unsettling, captain. I feel as if I have lost the privacy of my own thoughts. An ironic comeuppance, I suppose." ``Tuvok, I have to ask: the Caretaker...ego...you encountered in her mind. Did you learn anything from it?" He closed his eyes and relaxed. ``I see a room, captain. A room filled with machines older than human civilization. And an old man, older than them. A nexus of time, space, and thought. " His hands played across a control panel only he could see. His eyes snapped open. ``Captain," he said. ``I know how to use the array. If you can get me inside, I can get \textit{Voyager} home." \begin{center}\rule{3cm}{0.4 pt}\end{center} \noindent\textbf{-1 Day}\\Everyone who could fit stood on the bridge, watching the view screen. ``Captain," said Kim, ``I'm detecting a warp signature inbound on this system. Looks like \textit{Predator}." ``They know," said Janeway. ``Ensign Wildman?" ``Intense activity from the planet's surface. It's happening any minute now." Janeway took a sip of coffee and watched. Five days of waiting for this moment. ``Where's \textit{Val Jean}?" she said. ``Kuiper belt, opposite side of the system from us," said Kim. ``They aren't looking this direction," said Tuvok. ``\textit{Voyager }and \textit{Predator} monopolized Chakotay's attention." She nodded and took another sip. Her hands were shaking slightly; she focused on stilling them and they stopped. ``Mr. Tuvok, activate the cloak." ``Aye captain." The lights flickered. Outside, \textit{Voyager}, a lone white speck at the bottom of a soot-black crater, shimmered and vanished. ``Here it comes!" said Kim. ``Here \textit{we} come," said Janeway. A blister rose in the fabric of space twenty thousand kilometers above the surface of Ocampa. It burst in a shower of exotic particles and out popped \textit{Voyager}, haloed in debris and escaping air, the hull surface so hot it was glowing red at the wedge-end of the saucer hull. \textit{Red alert.} Past-\textit{Voyager}'s lights flickered once and went out. Warp plasma vented from a hole in the starboard nacelle. Janeway closed her eyes. All her mistakes, from the moment she took command of \textit{Voyager}, all the people that had died, ran through her head. On the viewscreen, their past selves drifted in darkness and confusion, unaware of the Kazon battleship bearing down on them. Swanwyck and Guitirrez were still alive. Gombe and the crew of\textit{Earhart }were still alive. All the people who would die in the battle to come against the Kazons were still alive. One message from her, and maybe things would be different...She forced herself to stop. “Computer, initiate protocol Janeway Alpha Seven.” ``\textsc{instituting that procedure will lock out the external communications system for twenty-two hours. this action cannot be undone. do you wish to continue?}" ``Yes," said Janeway. The computer chirped. ``\textsc{lockout inititated. external communications are disabled for the next twenty-two hours}." ``Well," said Janeway. ``That's it." She got up and walked off the bridge, intending to grab whatever sleep she could. \begin{center}\rule{3cm}{0.4 pt}\end{center} \noindent\textbf{USS \textit{Voyager}} \noindent\textbf{Stardate 48309}\\``Transporter stations, report," said Janeway. ``\textit{Main transporter room, six pads, standing by."} ``\textit{Cargo transport one, four pads, standing by}." ``\textit{Cargo transport two, four pads, standing by}." ``\textit{Shuttlecraft }Drake, \textit{one pad standing by.}" ``\textit{Shuttlecraft }Aldrin\textit{, one pad standing by.}" ``\textit{Shuttlecraft }Amundsen\textit{, one pad standing by."} \textit{``Shuttlecraft }Wright\textit{, one pad standing by}." ``Mr. Nozawa, are you ready?" ``\textit{Standing by, Captain.}" ``Mr. Kim, assign remote access to all pads to Mr. Nozawa's station in transporter room one." ``Yes ma'am," he said. ``Lieutenant Nozawa, you'll have your targets assigned to you by the bridge. Remember, every pad has to cycle twice, so we're not going to have much time to waste. Remote operators, get your pads clear as soon as your targets materialize. Mr. Kim, have you identified Chakotay yet?" ``Yes ma'am. He's on the first list, main transporter room, pad three." ``Can he be beamed directly to the bridge?" said Janeway. ``Yes ma'am," said Kim. ``Time, Mr. Tuvok," said Janeway. ``One minute, thirty seconds to zero hour." Janeway nodded, sipped her coffee. The Battle of Ocampa played out on the viewscreen. Three Kazon scouts were chasing \textit{Val Jean}, hammering her with shell fire. Janeway, lurking behind her cloak, could do nothing but admire the little ship. And its crew. ``Transporter team stand by. Mr. Paris, do we have a clear line of sight to \textit{Val Jean}?" ``Yes ma'am," he said. ``Good. Let's keep it that way." ``There's the missile launch," said Kim. ``Right on schedule." Janeway held her breath as the atomic warhead bored in on \textit{Val Jean}. She knew they hadn't changed history, knew the ship would survive, knew the shields would protect the crew one last time. The warhead detonated. The gamma flash popped \textit{Val Jean}'s shields; moments later the ship's antimatter pods went flying in six different directions to explode harmlessly Ocampa's upper atmosphere. ``\textit{Val Jean} has lost power," said Tuvok. ``They are in freefall." ``\textit{Bridge, this is Nozawa. I have transporter locks on all targets. Standing by for your signal}." ``\textit{Energize}!" said Janeway. \begin{center}\rule{3cm}{0.4 pt}\end{center} \noindent\textit{\textbf{Val Jean}}\\Chakotay, A'sha, and Seska were all praying in their own ways. Chakotay wondered which heaven they'd wind up in. A light started shining through his eyelids. He opened his eyes. The light, blue and sparkling, was filling the cabin. A'sha's eyes snapped open. ``Transporter!" she said. \textit{Val Jean} vanished, and \textit{Voyager} appeared. He was still in a sitting posture, and was still so surprised that he didn't think to try to regain his balance. He fell on his ass on a thinly carpeted deck. He laid back and looked up. Janeway was standing over him, looking concerned. ``Is this heaven?" he said. ``I sure hope not," said Janeway. ``Captain," said the round-faced ensign manning the ops console. ``Lieutenant Nozawa reports both transports complete." ``Captain, it's time," said Tuvok. ``Warp out to the staging point," said Janeway. ``Warping now," said Tom Paris, sitting at the helm console. ``What's going on here?" said Chakotay. He looked at the view screen. ``How did you get into space without the Kazons seeing you?" ``It's a long story," said Janeway. She glanced down at the chronometer readout on her chair's armrest. ``We've reached the staging point. Mr. Paris, set course to return to Ocampa. Load torpedoes, prepare to drop cloak." ``At least summarize it for me," said Chakotay. ``B'Elana Torres turned our warp engine into a time machine and built a cloaking device," said Janeway. ``Oh," said Chakotay. ``Okay."The chronometer ticked down to zero. \begin{center}\rule{3cm}{0.4 pt}\end{center} \textit{Voyager}'s engines roared and the yellow planet swelled in the view screen. ``Drop cloak and engage target alpha," said Janeway. \textit{Voyager}'s cloak lifted with the ship less than a planetary diameter from the Kazon fleet. The spread of three photon torpedoes streaked away and struck \textit{Wrath }amidships port, blasting his superstructure apart and leaving the central core floating exposed in a tangle of glowing wreckage. ``Begin transmitting---" said Janeway. The remaining twelve battleships fired on \textit{Voyager} with their main batteries. Janeway had to grab her armrests to keep from getting thrown out of her chair. ``Shields down to fifty percent," said Tuvok. ``Tom, get us out of here!" said Janeway. ``Warp drive is not responding," said Paris. ``Engineering, report!" said Janeway. ``\textit{Port plasma manifold offline,}" said Carey. ``\textit{We're working on it.}" ``Work faster!" said Janeway, as \textit{Voyager} rocked with another massive shell hit. “Fire phasers!” Chakotay rushed over to the tactical station. ``Tuvok, reload torpedoes, destroy target beta. Give the rest of them something to think about." ``Captain?" said Tuvok. ``Do it!" said Janeway. Outside the ship, four photon torpedoes screamed into the front armor of the nearest Kazon battleship, blasting it into flying debris. ``Captain, it looks like some of the Kazons are running away," said Kim. ``Two, three...five, six of them are powering their warp drives." ``Let them go," said Janeway. On the view screen, phaser beams played across the hull of another Kazon battleship, burning its shields away; Tuvok followed up with a pair of torpedoes that left it scorched and drifting. ``Hail \textit{Wrath}." ``They're responding," said Kim. ``On screen!" Jal Jabin appeared on the main screen cloaked in smoke on a dark, ruined bridge. His face slicked with blood. ``Where's Razik?" said Janeway. ``He's dead." \textit{Voyager }shook again. ``One more shot and so are you," said Janeway. ``Call your fleet off or die." ``Balls," said Maj Jal Jabin. He jabbed a button on his console and vanished from the screen. \begin{center}\rule{3cm}{0.4 pt}\end{center} \noindent\textit{\textbf{Wrath}}\\Janeway's hideous albino face disappeared from Jabin's comms screen. He switched to the fleet channel. ``Dishonor and perdition to those who run! Glory and eternal life to those who fight! Destroy \textit{Voyager}!" Jal Jabin hoisted himself out of his chair and stepped over the body of the Razik. He staggered over to a special control station, pulled the body of its operator aside, entered a code on a keypad, and pressed the enter key. ``And fuck you too, old man," he said, as the first phaser blast from \textit{Voyager} burned through the control room's inner armor. \begin{center}\rule{3cm}{0.4 pt}\end{center} \noindent\textit{\textbf{Voyager}}\\The last of the hulk of \textit{Wrath} broke up into a thousand glowing pieces even as shouts of ``Glory to those who fight!" echoed across the Kazons' comms. There was an alarm from behind Janeway and a curse from Chakotay. ``Photon torpedoes offline," said Chakotay. ``Which ship is the flagship now?" said Janeway. ``No idea," said Chakotay. ``They don't need a lot of coordinating to keep shooting at us." ``Captain!" said Ensign Wildman. ``Something's happening on the planet! The Caretaker is transporting something big." ``What is it?" said Janeway, just as a massive shell hit threw her off her feet. There was a brilliant light on the viewscreen, brighter than Ocampa's sun, and a terrible, telepathic scream. Janeway curled into the fetal position, ready to die, when it fell away as rapidly as it had come. She wanted to lay on the deck for a year, but she forced herself to get back up. The shellfire had stopped. ``Report!" said Janeway. ``Captain, all the Kazons are gone." On the main viewscreen was the Caretaker, hanging serene and alone. ``What?" said Chakotay. ``Where did they---?" ``Captain!" shouted Harry Kim. The twisted wreck of \textit{Predator} smashed headlong into the Caretaker station at warp speed. There was a blast of light and debris and all the station's knife-blade appendages crumpled, leaving only the station's core. Janeway and Chakotay looked at each other. Neither had anything they could say. Ensign Wildman broke the silence. ``Captain, the Kazon ship punctured the hull. I can scan the interior. I'm detecting a class M atmosphere at standard temperature and pressure." Janeway tapped her commbadge. ``Transporter room, stand by for away team."
\end{document}